---
title: "dev_history.Rmd"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE
)

library(testthat)
```

# A chunk for package description

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
```{r description}
fusen::fill_description(
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = "Use Rmd First method to build your package. Start your package with documentation. Everything can be set from a Rmd file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
```

# Add dev_history template

```{r function}
#' Add dev_history.Rmd file that drives package development
#'
#' @param pkg Path where to save file
#' @param overwrite Whether to overwrite existing dev_history.Rmd file
#'
#' @return
#' Create a dev_history.Rmd file and return its path
#' @export
#'
#' @examples
add_dev_history <- function(pkg = ".", overwrite = FALSE) {
  pkg_path <- normalizePath(pkg)
  dev_path <- file.path(pkg_path, "dev_history.Rmd")
  if (file.exists(dev_path) & overwrite == FALSE) {
    stop("dev_history.Rmd already existed. It was not deleted.")
  } else {
    file.copy(system.file("dev-template.Rmd", package = "fusen"),
              dev_path)
  }
  
  cat('^dev_history\\.Rmd$', file = file.path(pkg_path, ".Rbuildignore"))
  dev_path
}
```

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)
browseURL(dummypackage)

# Add
add_dev_history(pkg = dummypackage, overwrite = TRUE)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

```{r tests}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)
browseURL(dummypackage)

# Add
add_dev_history(pkg = dummypackage)

test_that("add_dev_history adds dev_history.Rmd", {
  expect_true(file.exists(file.path(dummypackage, "dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".RBuildignore")))
  
  # Second time error
  expect_error(add_dev_history(pkg = dummypackage))
})

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```



# fill_description

```{r function}
#' Fill DESCRIPTION file of the package
#'
#' @param pkg Path to package
#' @param overwrite Whether to overwrite existing DESCRIPTION
#' @inheritParams usethis use_description_defaults
#'
#' @return
#' FIll DESCRIPTION file with fields. Return path to file.
#' @export
#'
#' @examples
fill_description <- function(pkg = ".", fields, overwrite = FALSE) {
  old <- setwd(pkg)
  on.exit(old)
  
  path <- normalizePath(pkg)
  
  desc_file <- path(path, "DESCRIPTION")
  
  if (file.exists(desc_file) & !isTRUE(overwrite)) {
    stop("DESCRIPTION already exists. Set overwrite = TRUE to overwrite.") 
  }
    # usethis::use_description(fields = fields)
    
    fields_new <- usethis::use_description_defaults(
      package = basename(path),
      roxygen = TRUE,
      fields = fields)
    desc <- desc::desc(text = glue::glue("{names(fields_new)}: {fields_new}"))
  
  desc$write(file = desc_file)
  desc_file
}
```

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)
browseURL(dummypackage)

fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = "Use Rmd First method to build your package. Start your package with documentation. Everything can be set from a Rmd file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

```{r tests}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = "Use Rmd First method to build your package. Start your package with documentation. Everything can be set from a Rmd file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)

test_that("fill_description adds DESCRIPTION", {
  expect_true(file.exists(file.path(dummypackage, "DESCRIPTION")))
  lines <- readLines(file.path(dummypackage, "DESCRIPTION"))
  expect_true(lines[1] == "Package: dummypackage")
  
  # Second launch error and no change
  expect_error(fill_description(
    pkg = dummypackage, fields = list(Title = "Second launch")))
  lines <- readLines(file.path(dummypackage, "DESCRIPTION"))
  expect_true(lines[1] == "Package: dummypackage")
})

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r dev, eval=FALSE}
usethis::use_mit_license("Sébastien Rochette")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

```{r function}
library(parsermd)

#' Inflate Rmd to package
#'
#' @param pkg Path to package
#' @param x Path to Rmd file to inflate
#'
#' @return
#' Package structure. Return path to current package.
#' @export
#'
#' @examples
inflate <- function(pkg = ".", rmd = "dev_history.Rmd", check = TRUE) {
  pkg_path <- normalizePath(pkg)
  rmd <- normalizePath(rmd, mustWork = FALSE)
  
  if (grepl(pkg_path, rmd)) {
    # Rmd already contains pkgpath
    rmd_path <- rmd
  } else {
    rmd_path <- file.path(pkg_path, rmd)
  }
  
  if(!file.exists(rmd_path)){
    stop(rmd, "does not exists, please use fusen::add_dev_history() to create it.")
  }
  
  # Create NAMESPACE
  namespace_file <- file.path(pkg_path, "NAMESPACE")
  if (!file.exists(namespace_file)) {
    roxygen2::roxygenise(pkg_path)
  }
  
  parsed_rmd <- parse_rmd(rmd)
  parsed_tbl <- as_tibble(parsed_rmd)

  # Get functions ----
  # Create R directory if needed
  R_dir <- file.path(pkg_path, "R")
  if (!dir.exists(R_dir)) {dir.create(R_dir)}
  
  # Check if there are functions
  rmd_fun <- parsed_tbl[!is.na(parsed_tbl$label) &
                          grepl("function", parsed_tbl$label),]
  if (nrow(rmd_fun) != 0) {
    parse_fun <- function(x) { # x <- rmd_fun[1,]
      code <- rmd_get_chunk(x)$code
      # find function name
      fun_name <- stringr::str_extract(
        code[grep("function", code)],
        "\\w*(?=(\\s*)(<-|=)(\\s*)function)"
      ) %>% 
        gsub(" ", "", .) # remove spaces
      
      # create R file with code content and fun name
      r_file <- file.path(pkg_path, "R", paste0(fun_name, ".R"))
      if (file.exists(r_file)) {warning(r_file, "has been overwritten")}
      cat(code, file = r_file, sep = "\n")
    }
    lapply(rmd_fun, parse_fun)
  }
  
  
  # Run attachment
  attachment::att_amend_desc(path = pkg_path)

  # Check
  if (isTRUE(check)) {
    devtools::check(pkg = pkg_path)
  }
}
```

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_dev_history(pkg = dummypackage, overwrite = TRUE)

inflate(pkg = dummypackage, rmd = dev_file)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

