---
title: "dev_history.Rmd for working package"
author: "Sebastien Rochette"
date: "23/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
-->

```{r description}
# --> for parse tests
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = "Use Rmarkdown First method to build your package. Start your package with documentation. Everything can be set from a Rmarkdown file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Sébastien Rochette")
```

# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->

```{r development-2}
# Set , error=TRUE for checks() if needed
# Run all in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))
# Example dataset
file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
# You will be able to read your example data file in each of your function examples and tests as follows
# For check() only, we need to shim system.file, otherwise base::system.file does not recognised load_all()
pkgload:::shim_system.file(package = "<my_package_name>")
system.file(package = "<my_package_name>")
list.files(system.file(package = "<my_package_name>"))
datafile <- system.file("nyc_squirrels_sample.csv", package = "<my_package_name>")
datafile <- pkgload:::shim_system.file("nyc_squirrels_sample.csv", package = "<my_package_name>")
here::here()
datafile
nyc_squirrels <- read.csv(datafile)
```

# Calculate the median of a vector

```{r function}
#' My median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
#' my_median(2:20)
my_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples}
my_median(1:12)
```

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```

# Calculate the mean of a vector
## Use sub-functions in the same chunk

```{r function-1}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm =na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
sub_median <- function(x, na.rm = TRUE) {
  stats::median(x, na.rm)
}
```

```{r examples-1}
my_other_median(1:12)
my_other_median(8:20)
my_other_median(20:50)
```

```{r tests-1}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

# The third median without example

```{r function-2}
#' My third median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
my_third_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```


# The fourth median without example in but one out

```{r function-3}
#' My fourth median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
my_fourth_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples-3}
my_fourth_median(1:12)
my_fourth_median(8:20)
```

# The fifth median without empty example and test

```{r function-4}
#' My fifth median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
my_fifth_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples-4}

```

```{r tests-4}

```

# The sixth median with dot in function name

```{r function-6}
#' My sixth median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
my.sixth.median_function <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples-6}
my.sixth.median_function(1:12)
my.sixth.median_function(8:20)
my.sixth.median_function(20:50)
```

```{r tests-6}
test_that("my.sixth.median_function works properly and show error if needed", {
  expect_true(my.sixth.median_function(1:12) == 6.5)
  expect_error(my.sixth.median_function("text"))
})
```

## Empty ones

```{r function-5}


```

```{r examples-5}

```

```{r tests-5}

```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

```{r}
# duplicate empty name
```

```{r}
# duplicate empty name
```


You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
