---
title: "flat_read_inflate_params.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

This vignette details the process used to be able to inflate all the flat files present in the `dev/` folder at once.

Prior to be able to inflate all the flat files, some checks are performed.

The function `pre_inflate_all_diagnosis()` performs a diagnosis to assess whether the flat files are available to be used by `inflate_all()`. 

Please note that `inflate_all()` requires the existence of a `config_fusen.yml` file. This file is not existing in versions of {fusen} prior to v0.5.0.9000.

If you are working in a project initiated with a version of {fusen} prior to v0.5.0.9000, please run `inflate()` for at least one of your flat files in order to create the `config_fusen.yml` file.

If you are already familiar to `config_fusen.yml` but were working with a dev version of {fusen} prior to v0.5.0.9001, your `config_fusen.yml` file does not contain inflate-related parameters. You will have to inflate again you flat files in order to complete `config_fusen.yml` with the `inflate()` parameters.


# pre_inflate_all_diagnosis

```{r function-pre_inflate_all_diagnosis}
#' This function evaluates whether flat files can or can not be inflated with `inflate_all()`
#'
#' Internal function used in `inflate_all()`
#'
#' @param config_yml List. Content of the fusen config_file
#' @param pkg Character. Path of the current package
#'
#' @importFrom glue glue
#' @importFrom tibble tibble
#'
#' @return
#'
pre_inflate_all_diagnosis <- function(config_yml, pkg) {
  flat_files_in_dev_folder <- list.files(file.path(pkg, "dev"))
  flat_files_in_dev_folder <- flat_files_in_dev_folder[grepl(pattern = "^flat_", x = flat_files_in_dev_folder)]

  if (length(flat_files_in_dev_folder) == 0) {
    stop("There are no flat files starting with 'flat_' in the 'dev/' directory")
  }

  flat_files_status <- lapply(flat_files_in_dev_folder, function(flat) {
    if (flat %in% names(config_yml) &&
      "inflate" %in% names(config_yml[[flat]]) &&
      config_yml[[flat]][["state"]] == "active") {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} was inflated"),
        type = "message"
      ))
    } else if (flat %in% names(config_yml) &&
      config_yml[[flat]][["state"]] != "active") {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} was not inflated because it is \"inactive or deprecated\""),
        type = "message"
      ))
    } else if (!flat %in% names(config_yml)) {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} was not inflated because it is absent from the config file. Please inflate() from the flat once"),
        type = "warning"
      ))
    } else if (flat %in% names(config_yml) &&
      is.null(config_yml[[flat]][["inflate"]])) {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} was not inflated because although present in the config file, it has no inflate() parameters. Please inflate() again from the flat with this 'fusen' version"),
        type = "stop"
      ))
    }
  })

  flat_files_status <- do.call(rbind, flat_files_status)

  files_in_config_yml_but_missing_in_dev_folder <- names(config_yml)[!names(config_yml) %in% flat_files_in_dev_folder]

  if (length(files_in_config_yml_but_missing_in_dev_folder) > 0) {
    flat_files_status <- rbind(
      flat_files_status,
      tibble(
        flat = files_in_config_yml_but_missing_in_dev_folder,
        status = glue("The file {files_in_config_yml_but_missing_in_dev_folder} was not inflated because it was not found, have you changed the name or did you move in another place ? Maybe you want to set the state as 'deprecated' in the config file"),
        type = "stop"
      )
    )
  }

  return(invisible(flat_files_status))
}
```


```{r example-pre_inflate_all_diagnosis, eval = FALSE}
#' \dontrun{
dummypackage <- tempfile("register")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <-
  suppressMessages(add_minimal(
    pkg = dummypackage,
    overwrite = TRUE,
    open = FALSE
  ))
# let's create 2 flat files
flat_file <- dev_file[grepl("flat_", dev_file)]
flat_file2 <-
  gsub(
    x = flat_file,
    pattern = "flat_minimal.Rmd",
    replacement = "flat_minimal_2.Rmd"
  )
file.copy(
  from = flat_file,
  to = flat_file2,
  overwrite = TRUE
)

# let's inflate them to have dev/config_fusen.yml
suppressMessages(
  inflate(
    pkg = dummypackage,
    flat_file = flat_file,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE
  )
)

suppressMessages(
  inflate(
    pkg = dummypackage,
    flat_file = flat_file2,
    vignette_name = "Get started2",
    check = FALSE,
    open_vignette = FALSE
  )
)

config_yml_ref <-
  yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

# all files can be inflated with inflate_all()
config_yml <- config_yml_ref
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider the first flat file is deprecated
config_yml <- config_yml_ref
config_yml[[1]][["state"]] <- "deprecated"
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider the first flat file is missing from config_fusen.yaml
config_yml <- config_yml_ref
config_yml[[1]] <- NULL
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider that the first flat file has not inflate related params in config_fusen.yaml
config_yml <- config_yml_ref
config_yml[[1]][["inflate"]] <- NULL
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider a file is in config.yml but missing from dev/
config_yml <- config_yml_ref
config_yml[["missing_file.Rmd"]] <- config_yml[[1]]
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

unlink(dummypackage, recursive = TRUE)
#' }
```


```{r tests-pre_inflate_all_diagnosis}
dummypackage <- tempfile("diag")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE))

# let's create 2 flat files
flat_file <- dev_file[grepl("flat_", dev_file)]
flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

test_that("pre_inflate_all_diagnosis works", {
  expect_true(inherits(pre_inflate_all_diagnosis, "function"))

  usethis::with_project(dummypackage, {
    # We inflate both flat files
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE
      )
    )

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started2", check = FALSE,
        open_vignette = FALSE
      )
    )

    config_yml_ref <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    # all files can be inflated with inflate_all()
    config_yml <- config_yml_ref
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd was inflated",
              "The flat file flat_minimal_2.Rmd was inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("message", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )

    #  "not inflated because "inactive or deprecated" (message) : a file is present in config_yml but its state is not 'active'
    config_yml <- config_yml_ref
    config_yml[[1]][["state"]] <- "deprecated"
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd was not inflated because it is \"inactive or deprecated\"",
              "The flat file flat_minimal_2.Rmd was inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("message", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )


    #  "not inflated because not in config file please inflate() from the flat once" (warning) : a file is missing from config_yml
    config_yml <- config_yml_ref
    config_yml[[1]] <- NULL
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd was not inflated because it is absent from the config file. Please inflate() from the flat once",
              "The flat file flat_minimal_2.Rmd was inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("warning", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )


    #  "not inflated because in config, but without parameters, please inflate() again from the flat with this new 'fusen' version" (stop) : a file is is config_yml but has not inflate parameters
    config_yml <- config_yml_ref
    config_yml[[1]][["inflate"]] <- NULL
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd was not inflated because although present in the config file, it has no inflate() parameters. Please inflate() again from the flat with this 'fusen' version",
              "The flat file flat_minimal_2.Rmd was inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("stop", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )

    # a file is in config.yml but missing from dev/
    config_yml <- config_yml_ref
    config_yml[["missing_file.Rmd"]] <- config_yml[[1]]
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c(
            "flat_minimal.Rmd", "flat_minimal_2.Rmd",
            "missing_file.Rmd"
          ),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd was inflated",
              "The flat file flat_minimal_2.Rmd was inflated",
              "The file missing_file.Rmd was not inflated because it was not found, have you changed the name or did you move in another place ? Maybe you want to set the state as 'deprecated' in the config file"
            ),
            class = c("glue", "character")
          ),
          type = c(
            "message", "message",
            "stop"
          )
        ),
        row.names = c(NA, -3L),
        class = c(
          "tbl_df", "tbl",
          "data.frame"
        )
      )
    )

    # error if we dont have any flat file in dev/
    config_yml <- config_yml_ref
    unlink(flat_file)
    unlink(flat_file2)
    expect_error(pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage))
  })
})

unlink(dummypackage, recursive = TRUE)
```



```{r function-read_inflate_params}
#' Read inflate-related parameters in config_fusen.yaml
#'
#' Internal function used in `inflate_all()`
#'
#' @param config_yml List. Content of the fusen config_file
#'
#' @return a named list with the flat files listed in config_fusen.yaml
#' and the parameters used to inflate them
#'
#' @examples
read_inflate_params <- function(config_yml) {
  config_yml <- config_yml[sapply(config_yml, function(flat) flat[["state"]] == "active")]

  flat_files_names <- names(config_yml)

  flat_files_names <- flat_files_names[!flat_files_names %in% "keep"]

  if (length(flat_files_names) == 0) {
    return(NULL)
  }

  # inflate-related parameters are at level 2 of the list
  inflate_params <- lapply(flat_files_names, function(flat) {
    config_yml[[flat]][["inflate"]]
  }) %>% setNames(flat_files_names)

  inflate_params
}
```

```{r examples-read_inflate_params, eval=FALSE}
#' \dontrun{
config_yml <- yaml::read_yaml(system.file("inflate_all/config_fusen_with_inflate_parameters.yaml", package = "fusen"))
read_inflate_params(config_yml = config_yml)
#' }
```

```{r tests-read_inflate_params}
test_that("read_inflate_params works", {
  config_fusen_not_existing <-
    system.file("inflate_all/fake.yaml", package = "fusen")
  expect_error(read_inflate_params(config_yml = config_fusen_not_existing))

  config_fusen_existing <-
    yaml::read_yaml(system.file("inflate_all/config_fusen_with_inflate_parameters.yaml",
      package = "fusen"
    ))

  inflate_params <-
    read_inflate_params(config_yml = config_fusen_existing)

  expect_equal(
    length(inflate_params),
    3
  )

  expect_equal(
    names(inflate_params),
    c(
      "flat_full.Rmd",
      "flat_new_one.Rmd",
      "flat_no_inflate_params.Rmd"
    )
  )

  expect_equal(
    inflate_params[["flat_full.Rmd"]],
    list(
      pkg = "fusentest",
      flat_file = "dev/flat_full.Rmd",
      vignette_name = "Get started",
      open_vignette = FALSE,
      check = FALSE,
      document = TRUE,
      overwrite = "ask"
    )
  )

  expect_equal(
    inflate_params[["flat_new_one.Rmd"]],
    list(
      pkg = "fusentest",
      flat_file = "dev/flat_new_one.Rmd",
      vignette_name = "new_one",
      open_vignette = FALSE,
      check = FALSE,
      document = TRUE,
      overwrite = "ask"
    )
  )
  expect_null(inflate_params[["flat_no_inflate_params.Rmd"]])

  # test whether flat files with state = "deprecated" are removed
  config_fusen_with_deprecated <-
    yaml::read_yaml(system.file(
      "inflate_all/config_fusen_with_inflate_parameters_and_some_deprecated_files.yaml",
      package = "fusen"
    ))

  inflate_params <-
    read_inflate_params(config_yml = config_fusen_with_deprecated)

  expect_equal(
    length(inflate_params),
    2
  )

  expect_equal(
    names(inflate_params),
    c("flat_new_one.Rmd", "flat_no_inflate_params.Rmd")
  )
})
```



```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_read_inflate_params.Rmd",
  vignette_name = "Inflate all your flat files",
  check = FALSE,
  overwrite = TRUE,
  open_vignette = FALSE
)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```
