---
title: "flat_get_package_structure.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Get a tree of the package structure to help developers

`get_package_structure()` is a function that helps developers understand the package structure. It reads the `dev/config_fusen.yaml` file, adds the list of resulting functions and extra description of files.  

You can know:

- The description of the flat file as issued from its Title when exists
- If the flat file is still active
- The list of R files issued from the flat file
- The list of functions inside these R files
- The list of files of tests issued from the flat file
- There is a possibility to list all functions that are called in the test files
- The vignette issued from the flat file

With `draw_the_map()`, you can draw a tree of the package structure in the console.

```{r function-get_package_structure}
#' Get structure and information of a 'fusen' built package for developers
#'
#' @param config_file Path to a source configuration file
#' to get the structure from
#' @param emoji Add emojis to the output
#' @param silent Whether to print messages
#'
#' @return A list of information about the package
#' @export
#'
#' @examples
get_package_structure <- function(
    config_file,
    emoji = TRUE,
    silent = FALSE) {
  if (missing(config_file)) {
    yaml_fusen_file_orig <- getOption(
      "fusen_config_file",
      default = "dev/config_fusen.yaml"
    )
  }

  yaml_fusen_file <- tempfile(fileext = ".yaml")
  if (!file.exists(yaml_fusen_file_orig)) {
    # Not 'fusen' package or not inflated
    file.create(yaml_fusen_file)
  } else {
    file.copy(yaml_fusen_file_orig, yaml_fusen_file)
  }

  # Add not registered files in a copy of the config file
  suppressMessages(
    register_all_to_config(
      pkg = ".",
      config_file = yaml_fusen_file
    )
  )

  yaml_fusen <- yaml::read_yaml(yaml_fusen_file)
  file.remove(yaml_fusen_file)

  # For each element, add the title of the flat file
  if (file.exists("NAMESPACE")) {
    namespace <- readLines("NAMESPACE")
    if (isFALSE(silent)) {
      cat_rule("Reading NAMESPACE file")
    }
  } else {
    namespace <- NULL
    if (isFALSE(silent)) {
      cat_rule(paste("No NAMESPACE file found there: ", getwd()))
    }
  }

  for (flat_file in names(yaml_fusen)) {
    if (isFALSE(silent)) {
      cat_rule(flat_file)
    }
    yaml_fusen[[flat_file]]$inflate <- NULL

    # Extract title from the flat Rmd file
    if (flat_file != "keep") {
      flat_lines <- readLines(yaml_fusen[[flat_file]]$path)
      yaml_begin <- which(grepl("^---", flat_lines))[1]
      yaml_end <- which(grepl("^---", flat_lines))[2]
      flat_yaml <- yaml::yaml.load(flat_lines[yaml_begin:yaml_end])
      yaml_fusen[[flat_file]] <- c(
        list(flat_title = flat_yaml$title),
        yaml_fusen[[flat_file]]
      )
    }

    # Add emoji
    if (emoji) {
      flat_state <- yaml_fusen[[flat_file]]$state
      yaml_fusen[[flat_file]]$state <-
        paste(ifelse(
          flat_state == "active",
          "\U0001f34f", "\U0001f6d1"
        ), flat_state)
    }

    # Get the list of R files with their functions
    r_files <- yaml_fusen[[flat_file]][["R"]]
    list_r_files <- list()
    for (r_file in r_files) {
      functions <- get_all_created_funs(r_file)
      # Get if function is exported from namespace
      exported <- paste0("export(", functions, ")") %in% namespace
      if (emoji) {
        functions <- paste(
          ifelse(exported,
            "\U0001f440", "\U0001f648"
          ), functions
        )
      } else {
        functions <- paste(
          ifelse(exported, "exported", "not exported"),
          functions
        )
      }

      list_r_files <- c(
        list_r_files,
        setNames(list(functions), r_file)
      )
    }

    yaml_fusen[[flat_file]][["R"]] <- list_r_files
  }

  return(yaml_fusen)
}

#' Draw a tree of the package structure in the console
#'
#' @param structure_list A list of information about the package as issued
#' from `[get_package_structure()]`
#' @param silent Whether to print messages
#'
#' @export
#' @rdname get_package_structure
#'
draw_the_tree <- function(structure_list, silent = FALSE) {
  if (missing(structure_list)) {
    structure_list <- get_package_structure(silent = silent)
  }
  # Calculate the depth of a list
  depth <- function(structure_list) {
    if (!is.list(structure_list)) {
      return(0)
    }
    if (length(structure_list) == 0) {
      return(1)
    }
    return(1 + max(sapply(structure_list, depth)))
  }

  to_tree <- function(xlist) {
    to_tree_max(xlist, maxdepth = depth(xlist))
  }

  to_tree_max <- function(xlist, maxdepth) {
    d <- depth(xlist)
    if (d > 0) {
      result <- lapply(
        seq_along(xlist),
        function(w) {
          paste0(
            "\n",
            paste(rep("  ", maxdepth - d), collapse = ""),
            "- ",
            names(xlist)[w],
            paste0(
              unlist(to_tree_max(xlist[[w]], maxdepth)),
              collapse = ""
            )
          )
        }
      )
      return(result)
    } else if (d == 0) {
      paste0(
        "\n",
        paste(
          paste0(
            paste0(rep("  ", maxdepth), collapse = ""),
            "+ ",
            xlist
          ),
          collapse = "\n"
        )
      )
    }
  }

  cat(unlist(to_tree(structure_list)), sep = "")
}
```

```{r examples-get_package_structure, eval=FALSE}
#' \dontrun{
#' # This only works inside a 'fusen' built package
#' pkg_structure <- get_package_structure()
#' draw_the_tree(pkg_structure)
#' }
#'
#' # Example with a dummy package
dummypackage <- tempfile("drawpkg.structure")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(
  add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE)
)
flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {
  # Add an extra R file with internal function
  # to list in "keep"
  dir.create("R")
  cat("extra_fun <- function() {1}\n", file = "R/my_extra_fun.R")

  # Works with classical package
  pkg_structure <- get_package_structure()
  draw_the_tree(pkg_structure)
})

usethis::with_project(dummypackage, {
  # Works with 'fusen' package
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  pkg_structure <- get_package_structure()
  draw_the_tree(pkg_structure)
})
```

```{r tests-get_package_structure}
# Test full ----
dummypackage <- tempfile("drawpkg.structure")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(
  add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE)
)
flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {
  # Add an random R file with internal function
  dir.create("R")
  cat("extra_fun <- function() {1}\n", file = "R/my_extra_fun.R")

  test_that("get_package_structure allows classical package", {
    pkg_structure <- get_package_structure()

    expect_snapshot(pkg_structure)
    expect_snapshot(draw_the_tree(pkg_structure))
  })


  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  test_that("get_package_structure allows fusen structure", {
    # Need to force edition to allow expect_snapshot
    # As we are in another directory using with_dir()
    local_edition(3)
    # Fix output conditions for this test for snapshots
    local_reproducible_output(
      width = 100,
      crayon = FALSE,
      unicode = FALSE,
      rstudio = FALSE,
      hyperlinks = FALSE,
      lang = "en",
      .env = parent.frame()
    )

    pkg_structure <- get_package_structure()

    expect_snapshot(pkg_structure)

    expect_snapshot(draw_the_tree(pkg_structure))
  })
})
```

# Get the list of functions from a R file
    
```{r function-get_all_created_funs}
#' Get all functions created in a R file
#'
#' @param file A R file
#'
#' @return A character vector of function names
#'
#' @export
get_all_created_funs <- function(file) {
  stopifnot(tools::file_ext(file) %in% c("R", "r"))
  # Get each bloc of code
  parts_parsed <- parse(file, keep.source = TRUE)
  # We cannot directly get as.character as it would
  # remove character quotes from text only lines
  # like a line with : "_example" fails
  parts <- lapply(attr(parts_parsed, "srcref"), as.character)

  all_functions <- lapply(
    seq_along(parts), function(x) {
      out <- list()
      out$code <- as.character(parts[x])
      name <- parse_fun(out)$fun_name
      return(name)
    }
  ) %>% unlist()

  all_functions_no_na <- all_functions[!is.na(all_functions)]

  return(all_functions_no_na)
}
```
  
```{r example-get_all_created_funs}
file_path <- tempfile(fileext = ".R")
cat(
  "my_fun <- function() {1}",
  "my_fun2 <- function() {2}",
  sep = "\n",
  file = file_path
)
get_all_created_funs(file_path)
```
  
```{r tests-get_all_created_funs}
test_that("get_all_created_funs works", {
  expect_true(inherits(get_all_created_funs, "function"))

  file_path <- tempfile(fileext = ".R")
  cat(
    "my_fun <- function() {1}",
    "my_fun2 <- function() {2}",
    sep = "\n",
    file = file_path
  )
  expect_equal(
    get_all_created_funs(file_path),
    c("my_fun", "my_fun2")
  )
})
```
  


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_get_package_structure.Rmd",
  vignette_name = "Draw a tree of your package files and functions",
  check = TRUE, open_vignette = TRUE
)
```

