---
title: "dev_history.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
inflate:
    state: deprecated?
---

```{r development, include=FALSE}
library(testthat)
library(tools)
```

# add_flat_template

```{r function-1}
flat_template_choices <- c(
  "full",
  "minimal_package",
  "minpkg",
  "minimal_flat",
  "minflat",
  "add",
  "additional",
  "teach",
  "teaching",
  "dev_history",
  "dev"
)

create_fusen_choices <- c("full", "minimal", "teaching", "dev_history")

#' Add flat Rmd file that drives package development
#'
#' @param template Name of the template to use. See details.
#' @param pkg Path where to save file
#' @param overwrite Whether to overwrite existing flat Rmd template file with same name
#' @param open Logical. Whether to open file after creation
#' @param dev_dir Name of directory for development Rmarkdown files. Default to "dev".
#' @param flat_name Name of the file to write in dev.
#' Use the name of the main function of your template to get chunks pre-filled with this function name.
#'
#' @importFrom tools file_path_sans_ext
#' @details
#' Choose `template` among the different templates available:
#'
#' - "full": The full template with a reproducible package that can directly be inflated.
#' It comes along with the "dev_history" template. Default.
#' - "minimal_package": Minimal template to start a new package when you already know 'fusen', along with the "dev_history" template. Note that this is called "minimal" in `create_fusen()`.
#' - "minimal_flat" or "additional": Template for a new minimal flat file only.
#' - "teaching": Template with a reproducible package, simpler than "full", but everything to
#'  teach the minimal structure of a package.
#' - "dev_history": Template with functions commonly used during package development.
#' This does not contain chunks to write your own functions.
#'
#' Abbreviated names can also be used for the different templates:
#' "add" for additional, "minflat" for minimal_flat, "minpkg" for minimal_package "teach" for teaching, "dev" for "dev_history".
#'
#' `add_additional()`, `add_minimal_flat()`, `add_dev_history()`, `add_minimal_package()`, `add_full()` are wrapper around `add_flat_template("additional")`, ...
#'
#' @rdname add_flat_template
#' @return
#' Create flat Rmd file(s) template(s) and return its (their) path
#' @export
#'
#' @examples
add_flat_template <- function(
  template = c("full", "minimal_package", "minimal_flat", "additional", "teaching", "dev_history"),
  pkg = ".",
  dev_dir = "dev",
  flat_name = NULL,
  overwrite = FALSE,
  open = TRUE
) {
  project_name <- get_pkg_name(pkg = pkg)

  if (project_name != asciify_name(project_name, to_pkg = TRUE)) {
    stop(
      "Please rename your project/directory with: `",
      asciify_name(project_name, to_pkg = TRUE),
      "` as a package name should only contain letters, numbers and dots."
    )
  }

  template <- template[1]
  template <- match.arg(template, choices = flat_template_choices)

  if (template %in% c("additional", "add")) {
    template <- "additional"
    if (is.null(flat_name)) {
      flat_name <- "additional"
    }
  } else if (template %in% c("minimal_flat", "minflat")) {
    template <- "additional"
    if (is.null(flat_name)) {
      flat_name <- "minimal"
    }
  } else if (template %in% c("minpkg", "minimal", "minimal_package", "min")) {
    template <- "minimal_package"
    if (is.null(flat_name)) {
      flat_name <- "minimal"
    }
  } else if (template %in% c("teach")) {
    template <- "teaching"
    if (is.null(flat_name)) {
      flat_name <- "teaching"
    }
  } else if (is.null(flat_name)) {
    flat_name <- template
  }


  if (!template %in% c("full", "teaching", "dev_history") &
    !flat_name %in% c("minimal", "minimal_package", "minimal_flat", "additional")) {
    fun_name <- clean_function_name(flat_name)
  } else {
    fun_name <- NA
  }
  flat_name <- paste0(
    "flat_",
    asciify_name(gsub("[.]Rmd$", "", flat_name[1])),
    ".Rmd"
  )

  pkg <- normalizePath(pkg)
  full_dev_dir <- file.path(pkg, dev_dir)
  if (!dir.exists(full_dev_dir)) {
    dir.create(full_dev_dir)
  }
  dev_file_path <- file.path(full_dev_dir, flat_name) # "dev_history.Rmd")

  # Which template ----
  if (template == "dev_history") {
    dev_file_path <- character(0)
  } else {
    template_file <- system.file(paste0("flat-template-", template, ".Rmd"), package = "fusen")

    if (file.exists(dev_file_path) & overwrite == FALSE) {
      n <- length(list.files(full_dev_dir, pattern = "^flat_.*[.]Rmd"))
      dev_file_path <- file.path(full_dev_dir, paste0(file_path_sans_ext(flat_name), "_", n + 1, ".Rmd"))
      message(
        flat_name,
        " already exists. New flat file is renamed '",
        basename(dev_file_path),
        "'. Use overwrite = TRUE, if you want to ",
        "overwrite the existing file or rename it."
      )
    }
    dev_name <- basename(dev_file_path)

    # Change lines asking for pkg name
    lines_template <- readLines(template_file)

    lines_template[grepl("<my_package_name>", lines_template)] <-
      gsub(
        "<my_package_name>",
        project_name,
        lines_template[grepl("<my_package_name>", lines_template)]
      )

    # Change flat_template file name
    # _inflate
    lines_template[grepl("dev/flat_template.Rmd", lines_template)] <-
      gsub(
        "dev/flat_template.Rmd",
        file.path(dev_dir, dev_name),
        lines_template[grepl("dev/flat_template.Rmd", lines_template)]
      )
    # _title
    lines_template[grepl("flat_template.Rmd", lines_template)] <-
      gsub(
        "flat_template.Rmd",
        dev_name,
        lines_template[grepl("flat_template.Rmd", lines_template)]
      )

    # Change my_fun to fun_name
    if (!is.na(fun_name)) {
      lines_template[grepl("my_fun", lines_template)] <-
        gsub(
          "my_fun",
          fun_name,
          lines_template[grepl("my_fun", lines_template)]
        )
    }

    cat(enc2utf8(lines_template), file = dev_file_path, sep = "\n")
  }

  # Add the-dev-history when needed ----
  if (template %in% c("full", "minimal_package", "dev_history")) {
    dev_file <- file.path(full_dev_dir, "0-dev_history.Rmd")
    if (file.exists(dev_file) & !isTRUE(overwrite)) {
      message(
        "'0-dev_history.Rmd' already exists. It was not overwritten. ",
        "Set `add_flat_template(overwrite = TRUE)` if you want to do so."
      )
    } else {
      copy <- file.copy(
        system.file("the-dev-history.Rmd", package = "fusen"),
        dev_file,
        overwrite = overwrite
      )
      if (!copy) {
        stop("'0-dev_history.Rmd' could not be created in '", full_dev_dir, "'")
      }
      dev_file_path <- c(dev_file_path, dev_file)
    }
  }

  # Add data for the full template exemple
  if (template %in% c("full")) {
    inst_dir <- file.path(pkg, "inst")
    # Create "inst/" directory
    if (!dir.exists(inst_dir)) {
      dir.create(inst_dir)
    }
    # Example dataset
    file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), inst_dir)
  }

  # .Rbuildignore ----
  # usethis::use_build_ignore(dev_dir) # Cannot be used outside project
  if (length(list.files(pkg, pattern = "[.]Rproj")) == 0) {
    ignores <- c(paste0("^", dev_dir, "$"), "^\\.here$")
  } else {
    ignores <- c(paste0("^", dev_dir, "$"))
  }

  local_file_ignore(file = file.path(pkg, ".Rbuildignore"), ignores)

  # Add a gitignore file in dev_dir ----
  # Files to ignore
  ignores <- c("*.html")
  local_file_ignore(file = file.path(full_dev_dir, ".gitignore"), ignores)

  if (length(list.files(pkg, pattern = "[.]Rproj")) == 0 &
    !any(grepl("^[.]here$", list.files(pkg, all.files = TRUE)))) {
    here::set_here(pkg)
  }
  if (isTRUE(open) & interactive()) {
    lapply(dev_file_path, usethis::edit_file)
  }

  dev_file_path
}

#' Add new lines in a file if they are different from what exists
#' @noRd
local_file_ignore <- function(file, ignores) {
  buildfile <- normalizePath(file, mustWork = FALSE)
  if (!file.exists(buildfile)) {
    existing_lines <- character(0)
  } else {
    existing_lines <- readLines(buildfile, warn = FALSE, encoding = "UTF-8")
  }
  new <- setdiff(ignores, existing_lines)
  if (length(new) != 0) {
    all <- c(existing_lines, new)
    cat(enc2utf8(all), file = buildfile, sep = "\n")
  }
}
```

```{r examples-1}
# Create a new project
dummypackage <- tempfile("dummy.package.flat")
dir.create(dummypackage)

# Add
add_flat_template(template = "teaching", pkg = dummypackage)
# Delete dummy package
unlink(dummypackage, recursive = TRUE)

# For classical use in your package
#' \dontrun{
# first time ever using 'fusen'
add_flat_template("full")

# first time in your new package
add_flat_template("minimal_package")

# add new flat file for new functions
add_flat_template("add")
add_additional()
add_minimal_flat()

# add only the dev_history file in an existing package
add_dev_history()

# add new flat template for teaching (a reduced full template)
add_flat_template("teaching")
#' }
```

```{r tests-1}
# Create a new project
dummypackage <- tempfile(pattern = "add.flat.template")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

# add_flat_template ----
test_that("add_flat_template adds flat_template.Rmd and co.", {
  dev_file_path <- expect_error(
    add_flat_template(pkg = dummypackage, open = FALSE),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_true(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))

  rbuildignore_file <- file.path(dummypackage, ".Rbuildignore")
  expect_true(file.exists(rbuildignore_file))
  rbuildignore_lines <- readLines(rbuildignore_file)
  expect_true(any(grepl("^dev$", rbuildignore_lines, fixed = TRUE)))
  expect_true(any(grepl("[.]here", rbuildignore_lines)))

  gitignore_file <- file.path(dummypackage, "dev", ".gitignore")
  expect_true(file.exists(gitignore_file))
  gitignore_lines <- readLines(gitignore_file)
  expect_equal(object = gitignore_lines, expected = "*.html")

  dev_lines <- readLines(flat_file)
  expect_equal(length(grep(pkg_name, dev_lines)), 3)

  # Second time message and new file
  expect_message(add_flat_template(pkg = dummypackage))
  expect_true(file.exists(file.path(dummypackage, "dev", "flat_full_2.Rmd")))
  # _New file has path changed in title and inflate
  lines_2 <- readLines(file.path(dummypackage, "dev", "flat_full_2.Rmd"))
  expect_length(grep(x = lines_2, pattern = "flat_full_2[.]Rmd"), 2)
})
unlink(dummypackage, recursive = TRUE)

# Test with .Rproj and no .here, it works ----
# Create a new project
dummypackage2 <- tempfile(pattern = "rproj.nohere")
dir.create(dummypackage2)
cat("", file = file.path(dummypackage2, "dummy.Rproj"))

# Add
dev_file_path <- add_flat_template(pkg = dummypackage2, open = FALSE)
flat_file <- dev_file_path[grepl("flat", dev_file_path)]

test_that("add_flat_template works with .Rproj and no .here", {
  expect_true(all(file.exists(dev_file_path)))
  expect_false(file.exists(file.path(dummypackage2, ".here")))

  rbuildignore_file <- file.path(dummypackage2, ".Rbuildignore")
  expect_true(file.exists(rbuildignore_file))
  rbuildignore_lines <- readLines(rbuildignore_file)
  expect_true(any(grepl("dev", rbuildignore_lines, fixed = TRUE)))
  expect_false(any(grepl("[.]here", rbuildignore_lines)))
})
unlink(dummypackage2, recursive = TRUE)

# Test "dev_history" template ----
dummypackage <- tempfile(pattern = "dev.history.template")
dir.create(dummypackage)
# Add
test_that("add dev_history template works", {
  withr::with_dir(dummypackage, {
    dev_file_path <- expect_error(
      add_flat_template(
        pkg = dummypackage,
        template = "dev_history",
        open = FALSE
      ),
      regexp = NA
    )

    expect_true(file.exists(dev_file_path))

    usethis::with_project(dummypackage, {
      # Extract and test the description chunk
      dev_lines <- readLines(dev_file_path)
      # Change path of project
      dev_lines <- gsub(
        "here::here()",
        # To correct for Windows path
        paste0('"', gsub("\\\\", "\\\\\\\\", dummypackage), '"'),
        dev_lines,
        fixed = TRUE
      )

      devlines_file <- tempfile(pattern = "devlines")
      cat(dev_lines, file = devlines_file, sep = "\n")
      dev_parse <- lightparser::split_to_tbl(devlines_file)
      file.remove(devlines_file)

      desc_code <- tempfile("desc")

      cat(
        unlist(
          dev_parse[which(dev_parse[["label"]] == "description"), ][["code"]]
        ),
        sep = "\n",
        file = desc_code
      )

      # Execute code
      expect_error(source(desc_code), regexp = NA)
      file.remove(desc_code)
    })
    expect_true(file.exists(file.path(dummypackage, "DESCRIPTION")))
    expect_true(file.exists(file.path(dummypackage, "LICENSE")))
    expect_true(file.exists(file.path(dummypackage, "LICENSE.md")))
  })
})

unlink(dummypackage)


# Test "dev_history" template ----
dummypackage <- tempfile(pattern = "dev.history.template.uu")
dir.create(dummypackage)
# Add
test_that("add dev_history template works with windows \\users path", {
  withr::with_dir(dummypackage, {
    dev_file_path <- expect_error(
      add_flat_template(
        pkg = dummypackage,
        template = "dev_history",
        open = FALSE
      ),
      regexp = NA
    )

    expect_true(file.exists(dev_file_path))
    # Test specific \\users path
    newdir_uu <- tempfile("aa\\Users/gzv")
    dir.create(newdir_uu, recursive = TRUE)

    usethis::with_project(dummypackage, {
      # Extract and test the description chunk
      dev_lines <- readLines(dev_file_path)
      # Change path of project
      dev_lines <- gsub(
        "here::here()",
        # To correct for Windows path
        paste0('"', gsub("\\\\", "\\\\\\\\", newdir_uu), '"'),
        dev_lines,
        # paste0('"', newdir_uu, '"'), dev_lines,
        fixed = TRUE
      )


      devlines_file <- tempfile(pattern = "devlines")
      cat(dev_lines, file = devlines_file, sep = "\n")
      dev_parse <- lightparser::split_to_tbl(devlines_file)
      file.remove(devlines_file)

      desc_code <- tempfile("desc", fileext = ".R")

      cat(
        unlist(
          dev_parse[which(dev_parse[["label"]] == "description"), ][["code"]]
        ),
        sep = "\n",
        file = desc_code
      )

      # Execute code
      expect_error(source(desc_code), regexp = NA)
    })
    # DESCRIPTION in newdir_uu as created by fill_description()
    expect_true(file.exists(file.path(newdir_uu, "DESCRIPTION")))
    # LICENSE.md in dummypackage as created by use_mit_license()
    # No LICENSE because of separation of DESCRIPTION
    # expect_true(file.exists(file.path(dummypackage, "LICENSE")))
    expect_true(file.exists(file.path(dummypackage, "LICENSE.md")))
  })
})

unlink(dummypackage)

# Add failed with malformed package name ----
# Create a new project
dummypackage3 <- tempfile(pattern = "malformed_pkg")
dir.create(dummypackage3)
cat("", file = file.path(dummypackage3, "dummy.Rproj"))

# Add
test_that("add_flat_template fails", {
  expect_error(add_flat_template(pkg = dummypackage3, open = FALSE), "package name")
})
unlink(dummypackage3, recursive = TRUE)

# More complicated example for tests
# This will render the Rmd template that is supposed to build a package
# But we need to be inside a project,
# in the correct working directory,
# with the correct here()

# Test all templates to knit ----
all_templates <- fusen:::flat_template_choices[!fusen:::flat_template_choices %in% c("dev_history", "dev")] # "dev_history"
test_that("all templates to knit and inflate a second time", {
  expect_length(all_templates, 9)
})

for (template in all_templates) {
  # template <- all_templates[1]
  main_flat_file_name <- template
  if (template %in% c(
    "minimal_package",
    "minpkg",
    "minimal_flat",
    "minflat"
  )) {
    main_flat_file_name <- "minimal"
  } else if (template == "add") {
    main_flat_file_name <- "additional"
  } else if (template == "teach") {
    main_flat_file_name <- "teaching"
  }

  dummypackage4 <- tempfile(pattern = paste0("all.templates.knit", gsub("_", ".", template)))
  dir.create(dummypackage4)

  orig.proj <- here::here()

  withr::with_dir(dummypackage4, {
    # Add template
    dev_file_path <- suppressMessages(add_flat_template(template = template, open = FALSE))
    flat_file <- dev_file_path[grepl("flat", dev_file_path)]

    lines_template <- readLines(flat_file)
    # Run description chunk to build DESCRIPTION file and make it a proper pkg
    desc_line <- grep("\\{r description", lines_template)
    if (length(desc_line) != 0) {
      lines_template[desc_line] <- "```{r description, eval=TRUE}"
    }
    # pkgload::load_all in the template cannot work in non interactive R CMD Check
    if (template == "full" & !interactive()) {
      # if (template == "full" & interactive()) {
      loadall_line <- grep("^pkgload::load_all", lines_template)
      lines_template[loadall_line] <- "# pkgload::load_all() commented"
      data_line <- grep("datafile <- system.file", lines_template)
      lines_template[data_line] <-
        glue::glue('datafile <- file.path("{normalize_path_winslash(dummypackage4)}", "inst", "nyc_squirrels_sample.csv")')
    }

    cat(enc2utf8(lines_template), file = flat_file, sep = "\n")

    # description chunk as eval=TRUE
    if (any(grepl("dev_history", dev_file_path))) {
      dev_hist_path <- dev_file_path[grepl("dev_history", dev_file_path)]
      lines_dev <- readLines(dev_hist_path)
      lines_dev[grepl("\\{r description", lines_dev)] <- "```{r description, eval=TRUE}"
      cat(enc2utf8(lines_dev), file = dev_hist_path, sep = "\n")
    }

    # Simulate as being inside project
    usethis::proj_set(dummypackage4)
    here:::do_refresh_here(dummypackage4)

    if (rmarkdown::pandoc_available("1.12.3")) {
      # knitting with dev_history should transform project as a package
      # as fill_description is eval = TRUE
      if (any(grepl("dev_history", dev_file_path))) {
        test_that(paste0("dev_history can be rendered, associated with template", template), {
          expect_error(
            rmarkdown::render(
              input = dev_hist_path,
              output_file = file.path(dummypackage4, "dev", "dev_history.html"),
              envir = new.env(),
              quiet = TRUE
            ),
            regexp = NA
          )
        })
      } else if (template %in% c(
        "additional",
        "add",
        "minimal_flat",
        "minflat"
      )) {
        fusen::fill_description(
          pkg = here::here(),
          fields = list(Title = "Dummy Package")
        )
        # Define License with use_*_license()
        usethis::use_mit_license("John Doe")
      }

      test_that(paste0("template ", template, " can be rendered"), {
        flat_to_render <- file.path(dummypackage4, "dev", paste0("flat_", main_flat_file_name, ".Rmd"))
        expect_true(file.exists(flat_to_render))

        expect_error(
          rmarkdown::render(
            input = flat_to_render,
            output_file = file.path(dummypackage4, "dev", paste0("flat_", main_flat_file_name, ".html")),
            envir = new.env(),
            quiet = TRUE
          ),
          regexp = NA
        )
      })
    }

    usethis::proj_set(NULL)
    here:::do_refresh_here(orig.proj)
  })

  test_that(paste0("template ", template, " that was run as Rmarkdown gives project as a package"), {
    expect_true(file.exists(file.path(dummypackage4, "dev", paste0("flat_", main_flat_file_name, ".Rmd"))))
    if (template %in% c("full", "minimal_package")) {
      expect_true(file.exists(file.path(dirname(flat_file), "0-dev_history.Rmd")))
    }

    if (rmarkdown::pandoc_available("1.12.3")) {
      expect_true(file.exists(file.path(dummypackage4, "DESCRIPTION")))
      expect_true(file.exists(file.path(dummypackage4, "LICENSE")))
      if (template %in% c("full")) {
        expect_true(file.exists(file.path(dummypackage4, "inst", "nyc_squirrels_sample.csv")))
      } else {
        expect_false(file.exists(file.path(dummypackage4, "inst", "nyc_squirrels_sample.csv")))
      }
      expect_true(file.exists(file.path(dummypackage4, "dev", paste0("flat_", main_flat_file_name, ".html"))))
    }
  })

  # Now try to inflate from the inflate chunk
  test_that("flat file inflates after knit from command inside", {
    flat_lines <- readLines(flat_file)

    expect_true(sum(grepl(paste0("fusen::inflate\\(flat_file = \"dev/flat_", main_flat_file_name, ".Rmd\""), flat_lines)) == 1)

    withr::with_dir(dummypackage4, {
      inflate_command <- paste0("fusen::inflate(flat_file = \"dev/flat_", main_flat_file_name, ".Rmd\", open_vignette = FALSE, check = FALSE)")
      expect_error(suppressMessages(eval(parse(text = inflate_command))), regexp = NA)
    })
  })

  # Now try to inflates a second time
  test_that("flat file inflates a second time", {
    withr::with_dir(dummypackage4, {
      inflate_command_second <- paste0("fusen::inflate(flat_file = \"dev/flat_", main_flat_file_name, ".Rmd\", open_vignette = FALSE, check = FALSE, overwrite = TRUE)")
      expect_error(suppressMessages(eval(parse(text = inflate_command_second))), regexp = NA)
    })
  })

  unlink(dummypackage4, recursive = TRUE)
} # end of loop on template knit

# Test other names modifies template ----
dummypackage <- tempfile(pattern = "other.names")
dir.create(dummypackage)
# Add
test_that("Other flat_name works", {
  # Template additional used with "add"
  dev_file_path <- expect_error(
    add_flat_template(
      template = "add",
      pkg = dummypackage,
      flat_name = "hello",
      open = FALSE
    ),
    regexp = NA
  )
  expect_true(file.exists(file.path(dummypackage, "dev/flat_hello.Rmd")))
  hello_flat <- readLines(dev_file_path)
  # 9 times hello for function name
  # 2 times hello in flat_hello.Rmd
  expect_equal(length(grep("hello", hello_flat)), 9 + 2)
  expect_equal(length(grep("flat_hello[.]Rmd", hello_flat)), 2)

  # Template minimal used with "minpkg", same name, flat changes name
  expect_message(
    add_flat_template(
      template = "minpkg",
      pkg = dummypackage,
      flat_name = "hello",
      open = FALSE
    ),
    regexp = "flat_hello.Rmd already exists."
  )
  flat_file <- file.path(dummypackage, "dev/flat_hello_2.Rmd")
  expect_true(file.exists(flat_file))
  hello_flat <- readLines(flat_file)
  # 9 times hello for function name
  # 2 times hello in flat_hello_2.Rmd
  expect_equal(length(grep("hello", hello_flat)), 9 + 2)
  expect_equal(length(grep("flat_hello_2[.]Rmd", hello_flat)), 2)

  # Try inflate to see if files get hello name
  usethis::with_project(dummypackage, {
    fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
    expect_error(
      inflate(
        pkg = dummypackage,
        flat_file = flat_file,
        vignette_name = "hello",
        check = FALSE,
        open_vignette = FALSE
      ),
      regexp = NA
    )
  })

  expect_true(file.exists(file.path(dummypackage, "R", "hello.R")))
  expect_true(file.exists(file.path(dummypackage, "tests", "testthat", "test-hello.R")))
  expect_true(file.exists(file.path(dummypackage, "vignettes", "hello.Rmd")))
  test_hello <- readLines(file.path(dummypackage, "tests", "testthat", "test-hello.R"))
  expect_true(any(grepl("hello works", test_hello)))
  vignette_hello <- readLines(file.path(dummypackage, "vignettes", "hello.Rmd"))
  expect_true(any(grepl("title: \"hello\"", vignette_hello)))
  expect_true(any(grepl("  %\\VignetteIndexEntry{hello}", vignette_hello, fixed = TRUE)))
  expect_true(any(grepl("hello()", vignette_hello)))
})
# Delete dummy package
unlink(dummypackage, recursive = TRUE)

# Test other dev_dir works ----
dummypackage <- tempfile(pattern = "devdir")
dir.create(dummypackage)
# Add
test_that("Other dev_dir works", {
  # Template additional used with "add"
  dev_file_path <- expect_error(
    add_flat_template(
      template = "add",
      pkg = dummypackage,
      flat_name = "hello",
      dev_dir = "devdir",
      open = FALSE
    ),
    regexp = NA
  )
  expect_true(file.exists(file.path(dummypackage, "devdir/flat_hello.Rmd")))
  hello_flat <- readLines(dev_file_path)

  # 9 times hello for function name
  # 2 times hello in flat_hello.Rmd
  # 1 time devdir/flat_hello.Rmd
  # O time dev/flat_hello.Rmd
  expect_equal(length(grep("hello", hello_flat)), 9 + 2)
  expect_equal(length(grep("flat_hello[.]Rmd", hello_flat)), 2)
  expect_equal(length(grep("devdir/flat_hello[.]Rmd", hello_flat)), 1)
  expect_equal(length(grep("dev/flat_hello[.]Rmd", hello_flat)), 0)
})
# Delete dummy package
unlink(dummypackage, recursive = TRUE)

# local_file_ignore works ----
test_that("local_file_ignore works", {
  tmpdirectory <- tempfile()
  dir.create(tmpdirectory)

  anyfile <- file.path(tmpdirectory, "whatever")
  local_file_ignore(file = anyfile, ignores = c("whatever", "^.other/$"))
  lines <- readLines(anyfile)
  expect_equal(
    object = lines,
    expected = c("whatever", "^.other/$")
  )

  # Add over
  local_file_ignore(file = anyfile, ignores = c("whatever", "something.else"))
  lines <- readLines(anyfile)
  expect_equal(
    object = lines,
    expected = c("whatever", "^.other/$", "something.else")
  )

  # Clean
  unlink(tmpdirectory)
})

# add_flat_template allows bad flat_name for function name ----
dummypackage <- tempfile(pattern = "bad.flat.ok")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that(
  "add_flat_template allows bad flat_name for function name with full",
  {
    dev_file_path <- expect_error(
      suppressMessages(
        add_flat_template(
          pkg = dummypackage,
          flat_name = "bad for function ! but.ok",
          open = FALSE
        )
      ),
      regexp = NA
    )
    flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

    expect_true(all(file.exists(dev_file_path)))
    expect_true(file.exists(file.path(
      dummypackage,
      "dev",
      "flat_bad-for-function-but-ok.Rmd"
    )))
    expect_true(file.exists(file.path(
      dummypackage,
      "dev",
      "0-dev_history.Rmd"
    )))
  }
)
unlink(dummypackage, recursive = TRUE)

# add_flat_template allows bad flat_name for function name ----
dummypackage <- tempfile(pattern = "bad.flat.ok.add")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_flat_template allows bad flat_name for function name with add", {
  dev_file_path <- expect_error(
    suppressMessages(
      add_additional(
        pkg = dummypackage,
        flat_name = "bad for function ! but.ok2",
        open = FALSE
      )
    ),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(
    dummypackage,
    "dev",
    "flat_bad-for-function-but-ok2.Rmd"
  )))

  dev_lines <- readLines(flat_file)
  # title x 1, function x 3, example x 2, tests x 3
  expect_equal(length(grep("bad_for_function_but_ok2", dev_lines)), 9)
})
unlink(dummypackage, recursive = TRUE)
```

## add_additional & co.

```{r function-add_additional}
#' @rdname add_flat_template
#' @export
add_additional <- function(
  pkg = ".",
  dev_dir = "dev",
  flat_name = "additional",
  overwrite = FALSE,
  open = TRUE
) {
  add_flat_template(
    template = "additional",
    pkg = pkg,
    dev_dir = dev_dir,
    flat_name = flat_name,
    overwrite = overwrite,
    open = open
  )
}

#' @rdname add_flat_template
#' @export
add_minimal_flat <- function(
  pkg = ".",
  dev_dir = "dev",
  flat_name = "minimal",
  overwrite = FALSE,
  open = TRUE
) {
  add_flat_template(
    template = "minimal_flat",
    pkg = pkg,
    dev_dir = dev_dir,
    flat_name = flat_name,
    overwrite = overwrite,
    open = open
  )
}

#' @rdname add_flat_template
#' @export
add_minimal_package <- function(
  pkg = ".",
  dev_dir = "dev",
  flat_name = "minimal",
  overwrite = FALSE,
  open = TRUE
) {
  add_flat_template(
    template = "minimal_package",
    pkg = pkg,
    dev_dir = dev_dir,
    flat_name = flat_name,
    overwrite = overwrite,
    open = open
  )
}

#' @rdname add_flat_template
#' @export
add_full <- function(
  pkg = ".",
  dev_dir = "dev",
  flat_name = "full",
  overwrite = FALSE,
  open = TRUE
) {
  add_flat_template(
    template = "full",
    pkg = pkg,
    dev_dir = dev_dir,
    flat_name = flat_name,
    overwrite = overwrite,
    open = open
  )
}

#' @rdname add_flat_template
#' @export
add_dev_history <- function(
  pkg = ".",
  dev_dir = "dev",
  overwrite = FALSE,
  open = TRUE
) {
  add_flat_template(
    template = "dev_history",
    pkg = pkg,
    dev_dir = dev_dir,
    flat_name = "fake",
    overwrite = overwrite,
    open = open
  )
}
```

```{r example-add_additional}
```

```{r tests-add_additional}
# add_full ----
dummypackage <- tempfile(pattern = "add.wrappers")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_full adds flat_full.Rmd", {
  dev_file_path <- expect_error(
    suppressMessages(add_full(pkg = dummypackage, open = FALSE)),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_true(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))

  rbuildignore_file <- file.path(dummypackage, ".Rbuildignore")
  expect_true(file.exists(rbuildignore_file))
  rbuildignore_lines <- readLines(rbuildignore_file)
  expect_true(any(grepl("^dev$", rbuildignore_lines, fixed = TRUE)))
  expect_true(any(grepl("[.]here", rbuildignore_lines)))

  dev_lines <- readLines(flat_file)
  expect_equal(length(grep(pkg_name, dev_lines)), 3)
})
unlink(dummypackage, recursive = TRUE)

# add_minimal ----
dummypackage <- tempfile(pattern = "add.wrappers")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_minimal_package adds flat_minimal.Rmd", {
  dev_file_path <- expect_error(
    suppressMessages(add_minimal_package(pkg = dummypackage, open = FALSE)),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(dummypackage, "dev", "flat_minimal.Rmd")))
  expect_true(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_false(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))

  dev_lines <- readLines(flat_file)
  expect_equal(length(grep("flat_minimal", dev_lines)), 2)
})
unlink(dummypackage, recursive = TRUE)

# add_additional ----
dummypackage <- tempfile(pattern = "add.wrappers")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_additional adds flat_additional.Rmd", {
  dev_file_path <- expect_error(
    suppressMessages(add_additional(pkg = dummypackage, open = FALSE)),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(dummypackage, "dev", "flat_additional.Rmd")))
  expect_false(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_false(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))

  dev_lines <- readLines(flat_file)
  expect_equal(length(grep("additional", dev_lines)), 2)
})
unlink(dummypackage, recursive = TRUE)

# add_minimal_flat ----
dummypackage <- tempfile(pattern = "add.wrappers")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_minimal_flat adds add_minimal_flat.Rmd", {
  dev_file_path <- expect_error(
    suppressMessages(add_minimal_flat(pkg = dummypackage, open = FALSE)),
    regexp = NA
  )
  flat_file <- dev_file_path[grepl("flat_", dev_file_path)]

  expect_true(all(file.exists(dev_file_path)))
  expect_true(file.exists(file.path(dummypackage, "dev", "flat_minimal.Rmd")))
  expect_false(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_false(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))

  dev_lines <- readLines(flat_file)
  expect_equal(length(grep("flat_minimal", dev_lines)), 2)
})
unlink(dummypackage, recursive = TRUE)

# add_dev_history ----
dummypackage <- tempfile(pattern = "add.wrappers")
dir.create(dummypackage)
pkg_name <- basename(dummypackage)

test_that("add_dev_history adds dev_history.Rmd only", {
  dev_file_path <- expect_error(
    suppressMessages(add_dev_history(pkg = dummypackage, open = FALSE)),
    regexp = NA
  )

  expect_true(all(file.exists(dev_file_path)))
  expect_false(file.exists(file.path(dummypackage, "dev", "flat_fake.Rmd")))
  expect_true(file.exists(file.path(dummypackage, "dev", "0-dev_history.Rmd")))
  expect_true(file.exists(file.path(dummypackage, ".here")))
  expect_false(file.exists(file.path(dummypackage, "inst", "nyc_squirrels_sample.csv")))
})
unlink(dummypackage, recursive = TRUE)
```


```{r development-inflate, eval=FALSE}
# # Run but keep eval=FALSE to avoid infinite loop
# # Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_create_flat.Rmd",
  check = FALSE,
  vignette_name = NA
)
```

