---
title: "flat_inflate_all.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r development, include=FALSE}
library(testthat)
library(yaml)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

The `inflate_all()` function allows the user to inflate all the flat files present in the `dev/` folder at once.

Prior to be able to inflate all the flat files, some checks are performed, to assess whether the flat files are available to be used by `inflate_all()`.

Please note that `inflate_all()` requires the existence of a `config_fusen.yml` file. This file is not existing in versions of {fusen} prior to v0.5.0.9000.

If you are working in a project initiated with a version of {fusen} prior to v0.5.0.9000, please run `inflate()` for each of the flat files you want to work with in order to create the appropriated `config_fusen.yml` file.

If you are already familiar to `config_fusen.yml` but were working with a dev version of {fusen} prior to v0.5.0.9001, your `config_fusen.yml` file does not contain inflate-related parameters. You will have to inflate again you flat files in order to complete `config_fusen.yml` with the `inflate()` parameters.

# inflate_all
    
```{r function-inflate_all}
#' Inflate all your flat files
#'
#' Inflate all the flat files stored in dev/ and starting with "flat_"
#'
#' @param pkg Path to package
#'
#' @importFrom yaml read_yaml
#'
#' @return side effect. Inflates all your flat files that can be inflated.
#'
#' @export
inflate_all <- function(pkg = ".") {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (!file.exists(config_file)) {
    stop("There is no fusen.config_file in your package. Your flat files must be inflated at least once manually before you can use `inflate_all()`. If you were using a fusen prior to v0.5.0.9000 you must inflate all your flat files manually once again.")
  }

  # current_warn_option <- getOption("warn")
  # options(warn = 1)
  # on.exit(options(warn = current_warn_option))

  config_yml <- read_yaml(config_file)

  diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = pkg)

  for (flat_file_diag in 1:nrow(diag)) {
    # do.call(
    #   diag[["type"]][flat_file_diag],
    #   list(diag[["status"]][flat_file_diag])
    # )
    params <- diag[["params"]][flat_file_diag]
    if (is.na(params)) {
      status_text <- paste0(
        diag[["type"]][flat_file_diag],
        "('", diag[["status"]][flat_file_diag], "')")
    } else {
      status_text <- paste0(
        diag[["type"]][flat_file_diag],
        "('", diag[["status"]][flat_file_diag], "', ",
        diag[["params"]][flat_file_diag],
        ")")
    }
    
    eval(parse(text = status_text))
  }
  
  inflate_params <- read_inflate_params(config_yml = config_yml)

  if (length(inflate_params) == 0) {
    message("No flat files were inflated")
  } else {
    invisible(
      lapply(inflate_params, function(flat_file) {
        # TO BE REMOVED WHEN "pkg" wont be stored anymore in config_fusen
        flat_file$pkg <- pkg
        # should we keep that?
        flat_file$overwrite <- TRUE
        suppressMessages(do.call(inflate, flat_file))
      })
    )
  }
}
```
  
```{r example-inflate_all, eval=FALSE}
#' \dontrun{
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <-
  (add_minimal(
    pkg = dummypackage,
    overwrite = TRUE,
    open = FALSE
  ))

usethis::with_project(dummypackage, {
  # if you are starting from a brand new package, inflate_all() will crash
  # it's because of the absence of a fusen config file
  # inflate_all()

  # you need to inflate manually your flat file first
  inflate(
    pkg = dummypackage,
    flat_file = flat_file,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE,
    document = TRUE,
    overwrite = "yes"
  )

  # your config file has been created
  config_yml_ref <-
    yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

  # now you can run inflate_all()
  inflate_all()

  # Let's deprecate our flat file : inflate_all() won't like it and will tell you
  config_yml_deprecated <- config_yml_ref
  config_yml_deprecated[[1]][["state"]] <- "deprecated"
  yaml::write_yaml(config_yml_deprecated, file = "dev/config_fusen.yaml")
  inflate_all()

  # If you add a new flat file, absent from config_fusen.yml, inflate_all() will warn you
  yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")
  flat_file2 <-
    gsub(
      x = flat_file,
      pattern = "flat_minimal.Rmd",
      replacement = "flat_minimal_2.Rmd"
    )
  file.copy(
    from = flat_file,
    to = flat_file2,
    overwrite = TRUE
  )
  inflate_all()
  unlink(flat_file2)

  # Let's remove the inflate parameters from config_fusen.yml
  # If you used fusen and inflate() prior to v0.5.0.9001 your config_fusen.yml does not contain
  # the inflate parameters. You must inflate it again before being able to use inflate_all()
  config_yml_no_inflate_params <- config_yml_ref
  config_yml_no_inflate_params[[1]][["inflate"]] <- NULL
  yaml::write_yaml(config_yml_no_inflate_params, file = "dev/config_fusen.yaml")
  # inflate_all() will raise an error
  inflate_all()


  # Let's add a flat file in in config_fusen.yml not present in dev/
  config_yml_file_absent_in_dev <- config_yml_ref
  config_yml_file_absent_in_dev[["missing_file.Rmd"]] <-
    config_yml_file_absent_in_dev[[1]]
  yaml::write_yaml(config_yml_file_absent_in_dev, file = "dev/config_fusen.yaml")
  # inflate_all() will raise an error
  inflate_all()
})
unlink(dummypackage, recursive = TRUE)
#' }
```
  
```{r tests-inflate_all}
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- (add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE))

# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all works", {

  expect_true(inherits(inflate_all, "function"))

  usethis::with_project(dummypackage, {

    # if no config file exists, we raise an error
    expect_error(inflate_all(), regexp = "There is no fusen[.]config_file in your package[.]")

    # we inflate the flat file
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    config_yml_ref <- yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )

    # Let's deprecate our flat file
    config_yml_deprecated <- config_yml_ref
    config_yml_deprecated[[1]][["state"]] <- "deprecated"
    yaml::write_yaml(config_yml_deprecated, file = "dev/config_fusen.yaml")

    expect_message(inflate_all(),
      regexp = glue::glue('The flat file {basename(flat_file)} is not going to be inflated because it is "inactive or deprecated"')
    )

    # Let's add a new flat file, absent from config_fusen.yml
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )
    
    if (packageVersion("attachment") >= "0.4.0") {
      expect_warning(inflate_all())
    }

    # Let's remove the inflate parameters from config_fusen.yml
    unlink(flat_file2)

    config_yml_no_inflate_params <- config_yml_ref
    config_yml_no_inflate_params[[1]][["inflate"]] <- NULL
    yaml::write_yaml(config_yml_no_inflate_params, file = "dev/config_fusen.yaml")

    expect_error(inflate_all())


    # Let's add a flat file in in config_fusen.yml not present in dev/
    config_yml_file_absent_in_dev <- config_yml_ref
    config_yml_file_absent_in_dev[["missing_file.Rmd"]] <- config_yml_file_absent_in_dev[[1]]
    yaml::write_yaml(config_yml_file_absent_in_dev, file = "dev/config_fusen.yaml")

    expect_error(inflate_all())

    # Now let's take the ability of inflate_all() to inflate all our files !
    # We start from a clean place
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )
    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_false(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_false(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_false(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    inflate_all()

    expect_true(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_true(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_true(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    # what happens if we add a function in our flat file
    flat_content <- readLines(flat_file)
    function_template <- readLines(system.file("inflate_all/fusen_chunk_template", package = "fusen"))

    writeLines(c(flat_content, function_template), con = flat_file)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c("test-my_fun.R", "test-new_fun2.R")
    )


    # let's add a second flat
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started_2", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_true(length(list.files(file.path(dummypackage, "R"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "man"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE)) == 0)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "my_fun_from_flat_file2.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "my_fun_from_flat_file2.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c(
        "test-my_fun.R",
        "test-my_fun_from_flat_file2.R",
        "test-new_fun2.R"
      )
    )

    expect_equal(
      list.files(file.path(dummypackage, "vignettes/")),
      c("get-started.Rmd", "get-started_2.Rmd")
    )


    # Let's check a other way to choose the vignette name
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = c("name" = "index"), check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    unlink(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE))
    expect_true(length(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE)) == 0)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "vignettes/")),
      c("get-started.Rmd", "index.Rmd")
    )
  })
})

unlink(dummypackage, recursive = TRUE)
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_inflate_all.Rmd",
  vignette_name = "Inflate all your flat files",
  check = FALSE,
  overwrite = TRUE,
  open_vignette = FALSE
)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```

