---
title: "flat_read_inflate_params.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(yaml)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

This vignette details the process used to be able to inflate all the flat files present in the `dev/` folder at once.

Prior to be able to inflate all the flat files, some checks are performed.

The function `pre_inflate_all_diagnosis()` performs a diagnosis to assess whether the flat files are available to be used by `inflate_all()`. 

Please note that `inflate_all()` requires the existence of a `config_fusen.yml` file. This file is not existing in versions of {fusen} prior to v0.5.0.9000.

If you are working in a project initiated with a version of {fusen} prior to v0.5.0.9000, please run `inflate()` for at least one of your flat files in order to create the `config_fusen.yml` file.

If you are already familiar to `config_fusen.yml` but were working with a dev version of {fusen} prior to v0.5.0.9001, your `config_fusen.yml` file does not contain inflate-related parameters. You will have to inflate again you flat files in order to complete `config_fusen.yml` with the `inflate()` parameters.


# pre_inflate_all_diagnosis

```{r function-pre_inflate_all_diagnosis}
#' This function evaluates whether flat files can or can not be inflated with `inflate_all()`
#'
#' Internal function used in `inflate_all()`
#'
#' @param config_yml List. Content of the fusen config_file
#' @param pkg Character. Path of the current package
#'
#' @importFrom glue glue
#' @importFrom tibble tibble
#'
#' @return a tibble with the ability to each flat file to be inflated by inflate_all()
#' @noRd
pre_inflate_all_diagnosis <- function(config_yml, pkg) {
  flat_files_in_dev_folder <- list.files(file.path(pkg, "dev"))
  flat_files_in_dev_folder <- flat_files_in_dev_folder[grepl(pattern = "^flat_", x = flat_files_in_dev_folder)]

  if (length(flat_files_in_dev_folder) == 0) {
    stop("There are no flat files starting with 'flat_' in the 'dev/' directory")
  }

  flat_files_status <- lapply(flat_files_in_dev_folder, function(flat) {
    if (flat %in% names(config_yml) &&
      "inflate" %in% names(config_yml[[flat]]) &&
      config_yml[[flat]][["state"]] == "active") {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} is going to be inflated"),
        type = "message"
      ))
    } else if (flat %in% names(config_yml) &&
      config_yml[[flat]][["state"]] != "active") {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} is not going to be inflated because it is \"inactive or deprecated\""),
        type = "message"
      ))
    } else if (!flat %in% names(config_yml)) {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} is not going to be inflated because it is absent from the config file. Please inflate() from the flat once"),
        type = "warning"
      ))
    } else if (flat %in% names(config_yml) &&
      is.null(config_yml[[flat]][["inflate"]])) {
      return(tibble(
        flat = flat,
        status = glue("The flat file {flat} is not going to be inflated because although present in the config file, it has no inflate() parameters. Please inflate() again from the flat with this 'fusen' version"),
        type = "stop"
      ))
    }
  })

  flat_files_status <- do.call(rbind, flat_files_status)

  files_in_config_yml_but_missing_in_dev_folder <- names(config_yml)[!names(config_yml) %in% flat_files_in_dev_folder]

  if (length(files_in_config_yml_but_missing_in_dev_folder) > 0) {
    flat_files_status <- rbind(
      flat_files_status,
      tibble(
        flat = files_in_config_yml_but_missing_in_dev_folder,
        status = glue("The file {files_in_config_yml_but_missing_in_dev_folder} is not going to be inflated because it was not found, have you changed the name or did you move in another place ? Maybe you want to set the state as 'deprecated' in the config file"),
        type = "stop"
      )
    )
  }

  return(invisible(flat_files_status))
}
```


```{r example-pre_inflate_all_diagnosis, eval = FALSE}
#' \dontrun{
dummypackage <- tempfile("register")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <-
  suppressMessages(add_minimal(
    pkg = dummypackage,
    overwrite = TRUE,
    open = FALSE
  ))
# let's create 2 flat files
flat_file <- dev_file[grepl("flat_", dev_file)]
flat_file2 <-
  gsub(
    x = flat_file,
    pattern = "flat_minimal.Rmd",
    replacement = "flat_minimal_2.Rmd"
  )
file.copy(
  from = flat_file,
  to = flat_file2,
  overwrite = TRUE
)

# let's inflate them to have dev/config_fusen.yml
suppressMessages(
  inflate(
    pkg = dummypackage,
    flat_file = flat_file,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE
  )
)

suppressMessages(
  inflate(
    pkg = dummypackage,
    flat_file = flat_file2,
    vignette_name = "Get started2",
    check = FALSE,
    open_vignette = FALSE
  )
)

config_yml_ref <-
  yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

# all files can be inflated with inflate_all()
config_yml <- config_yml_ref
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider the first flat file is deprecated
config_yml <- config_yml_ref
config_yml[[1]][["state"]] <- "deprecated"
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider the first flat file is missing from config_fusen.yaml
config_yml <- config_yml_ref
config_yml[[1]] <- NULL
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider that the first flat file has not inflate related params in config_fusen.yaml
config_yml <- config_yml_ref
config_yml[[1]][["inflate"]] <- NULL
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

# let's consider a file is in config.yml but missing from dev/
config_yml <- config_yml_ref
config_yml[["missing_file.Rmd"]] <- config_yml[[1]]
diag <-
  pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)
print(diag)

unlink(dummypackage, recursive = TRUE)
#' }
```


```{r tests-pre_inflate_all_diagnosis}
dummypackage <- tempfile("diag")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE))

# let's create 2 flat files
flat_file <- dev_file[grepl("flat_", dev_file)]
flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

test_that("pre_inflate_all_diagnosis works", {
  expect_true(inherits(pre_inflate_all_diagnosis, "function"))

  usethis::with_project(dummypackage, {
    # We inflate both flat files
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE
      )
    )

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started2", check = FALSE,
        open_vignette = FALSE
      )
    )

    config_yml_ref <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    # all files can be inflated with inflate_all()
    config_yml <- config_yml_ref
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd is going to be inflated",
              "The flat file flat_minimal_2.Rmd is going to be inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("message", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )

    #  "not inflated because "inactive or deprecated" (message) : a file is present in config_yml but its state is not 'active'
    config_yml <- config_yml_ref
    config_yml[[1]][["state"]] <- "deprecated"
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd is not going to be inflated because it is \"inactive or deprecated\"",
              "The flat file flat_minimal_2.Rmd is going to be inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("message", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )


    #  "not inflated because not in config file please inflate() from the flat once" (warning) : a file is missing from config_yml
    config_yml <- config_yml_ref
    config_yml[[1]] <- NULL
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd is not going to be inflated because it is absent from the config file. Please inflate() from the flat once",
              "The flat file flat_minimal_2.Rmd is going to be inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("warning", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )


    #  "not inflated because in config, but without parameters, please inflate() again from the flat with this new 'fusen' version" (stop) : a file is is config_yml but has not inflate parameters
    config_yml <- config_yml_ref
    config_yml[[1]][["inflate"]] <- NULL
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c("flat_minimal.Rmd", "flat_minimal_2.Rmd"),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd is not going to be inflated because although present in the config file, it has no inflate() parameters. Please inflate() again from the flat with this 'fusen' version",
              "The flat file flat_minimal_2.Rmd is going to be inflated"
            ),
            class = c(
              "glue",
              "character"
            )
          ),
          type = c("stop", "message")
        ),
        row.names = c(NA, -2L),
        class = c("tbl_df", "tbl", "data.frame")
      )
    )

    # a file is in config.yml but missing from dev/
    config_yml <- config_yml_ref
    config_yml[["missing_file.Rmd"]] <- config_yml[[1]]
    diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage)

    expect_equal(
      diag,
      structure(
        list(
          flat = c(
            "flat_minimal.Rmd", "flat_minimal_2.Rmd",
            "missing_file.Rmd"
          ),
          status = structure(
            c(
              "The flat file flat_minimal.Rmd is going to be inflated",
              "The flat file flat_minimal_2.Rmd is going to be inflated",
              "The file missing_file.Rmd is not going to be inflated because it was not found, have you changed the name or did you move in another place ? Maybe you want to set the state as 'deprecated' in the config file"
            ),
            class = c("glue", "character")
          ),
          type = c(
            "message", "message",
            "stop"
          )
        ),
        row.names = c(NA, -3L),
        class = c(
          "tbl_df", "tbl",
          "data.frame"
        )
      )
    )

    # error if we dont have any flat file in dev/
    config_yml <- config_yml_ref
    unlink(flat_file)
    unlink(flat_file2)
    expect_error(pre_inflate_all_diagnosis(config_yml = config_yml, pkg = dummypackage))
  })
})

unlink(dummypackage, recursive = TRUE)
```

# read_inflate_params

```{r function-read_inflate_params}
#' Read inflate-related parameters in config_fusen.yaml
#'
#' Internal function used in `inflate_all()`
#'
#' @param config_yml List. Content of the fusen config_file
#'
#' @return a named list with the flat files listed in config_fusen.yaml
#' and the parameters used to inflate them
#' @noRd
#' @examples
read_inflate_params <- function(config_yml) {
  config_yml <- config_yml[sapply(config_yml, function(flat) flat[["state"]] == "active")]

  flat_files_names <- names(config_yml)

  flat_files_names <- flat_files_names[!flat_files_names %in% "keep"]

  if (length(flat_files_names) == 0) {
    return(NULL)
  }

  # inflate-related parameters are at level 2 of the list
  inflate_params <- lapply(flat_files_names, function(flat) {
    config_yml[[flat]][["inflate"]]
  }) %>% setNames(flat_files_names)

  inflate_params
}
```

```{r examples-read_inflate_params, eval=FALSE}
#' \dontrun{
config_yml <- yaml::read_yaml(system.file("inflate_all/config_fusen_with_inflate_parameters.yaml", package = "fusen"))
read_inflate_params(config_yml = config_yml)
#' }
```

```{r tests-read_inflate_params}
test_that("read_inflate_params works", {
  config_fusen_not_existing <-
    system.file("inflate_all/fake.yaml", package = "fusen")
  expect_error(read_inflate_params(config_yml = config_fusen_not_existing))

  config_fusen_existing <-
    yaml::read_yaml(system.file("inflate_all/config_fusen_with_inflate_parameters.yaml",
      package = "fusen"
    ))

  inflate_params <-
    read_inflate_params(config_yml = config_fusen_existing)

  expect_equal(
    length(inflate_params),
    3
  )

  expect_equal(
    names(inflate_params),
    c(
      "flat_full.Rmd",
      "flat_new_one.Rmd",
      "flat_no_inflate_params.Rmd"
    )
  )

  expect_equal(
    inflate_params[["flat_full.Rmd"]],
    list(
      pkg = "fusentest",
      flat_file = "dev/flat_full.Rmd",
      vignette_name = "Get started",
      open_vignette = FALSE,
      check = FALSE,
      document = TRUE,
      overwrite = "ask"
    )
  )

  expect_equal(
    inflate_params[["flat_new_one.Rmd"]],
    list(
      pkg = "fusentest",
      flat_file = "dev/flat_new_one.Rmd",
      vignette_name = "new_one",
      open_vignette = FALSE,
      check = FALSE,
      document = TRUE,
      overwrite = "ask"
    )
  )
  expect_null(inflate_params[["flat_no_inflate_params.Rmd"]])

  # test whether flat files with state = "deprecated" are removed
  config_fusen_with_deprecated <-
    yaml::read_yaml(system.file(
      "inflate_all/config_fusen_with_inflate_parameters_and_some_deprecated_files.yaml",
      package = "fusen"
    ))

  inflate_params <-
    read_inflate_params(config_yml = config_fusen_with_deprecated)

  expect_equal(
    length(inflate_params),
    2
  )

  expect_equal(
    names(inflate_params),
    c("flat_new_one.Rmd", "flat_no_inflate_params.Rmd")
  )
})
```

# inflate_all
    
```{r function-inflate_all}
#' Title
#'
#' Description
#'
#' @importFrom yaml read_yaml
#'
#' @return side effect. Inflates all your flat files that can be inflated.
#'
#' @export
inflate_all <- function(pkg = ".") {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (!file.exists(config_file)) {
    stop("There is fusen.config_file in your package. If you were using a fusen prior to v0.5.0.9000 you must inflate your flat files manually once again. Otherwise, your flat files must be inflated once before you can use inflate_all()")
  }

  config_yml <- read_yaml(config_file)

  diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = pkg)

  for (flat_file_diag in 1:nrow(diag)) {
    do.call(
      diag[["type"]][flat_file_diag],
      list(diag[["status"]][flat_file_diag])
    )
  }

  inflate_params <- read_inflate_params(config_yml = config_yml)

  if (length(inflate_params) == 0) {
    message("No flat files were inflated")
  } else {
    invisible(
      lapply(inflate_params, function(flat_file) {
        # TO BE REMOVED WHEN "pkg" wont be stored anymore in config_fusen
        flat_file$pkg <- pkg
        # should we keep that?
        flat_file$overwrite <- TRUE
        suppressMessages(do.call(inflate, flat_file))
      })
    )
  }
}
```
  
```{r example-inflate_all, eval=FALSE}
#' \dontrun{
inflate_all()
#' }
```
  
```{r tests-inflate_all}
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("diag")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- (add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE))

# let's create 2 flat files
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all works", {
  expect_true(inherits(inflate_all, "function"))

  usethis::with_project(dummypackage, {
    options(warn = 1L)

    # if no config file exists, we raise an error
    expect_error(inflate_all())

    # we inflate the flat file
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    config_yml_ref <- yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )

    # Let's deprecate our flat file
    config_yml_deprecated <- config_yml_ref
    config_yml_deprecated[[1]][["state"]] <- "deprecated"
    yaml::write_yaml(config_yml_deprecated, file = "dev/config_fusen.yaml")

    expect_message(inflate_all(),
      regexp = glue::glue('The flat file {basename(flat_file)} is not going to be inflated because it is "inactive or deprecated"')
    )

    # Let's add a new flat file, absent from config_fusen.yml
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )
    expect_warning(inflate_all())

    # Let's remove the inflate parameters from config_fusen.yml
    unlink(flat_file2)

    config_yml_no_inflate_params <- config_yml_ref
    config_yml_no_inflate_params[[1]][["inflate"]] <- NULL
    yaml::write_yaml(config_yml_no_inflate_params, file = "dev/config_fusen.yaml")

    expect_error(inflate_all())


    # Let's add a flat file in in config_fusen.yml not present in dev/
    config_yml_file_absent_in_dev <- config_yml_ref
    config_yml_file_absent_in_dev[["missing_file.Rmd"]] <- config_yml_file_absent_in_dev[[1]]
    yaml::write_yaml(config_yml_file_absent_in_dev, file = "dev/config_fusen.yaml")

    expect_error(inflate_all())

    # Now let's take the ability of inflate_all() to inflate all our files !
    # We start from a clean place
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )
    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_false(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_false(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_false(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    inflate_all()

    expect_true(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_true(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_true(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    # what happens if we add a function in our flat file
    flat_content <- readLines(flat_file)
    function_template <- readLines(system.file("inflate_all/fusen_chunk_template", package = "fusen"))

    writeLines(c(flat_content, function_template), con = flat_file)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c("test-my_fun.R", "test-new_fun2.R")
    )


    # let's add a second flat
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started_2", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_true(length(list.files(file.path(dummypackage, "R"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "man"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE)) == 0)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "my_fun_from_flat_file2.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "my_fun_from_flat_file2.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c(
        "test-my_fun.R",
        "test-my_fun_from_flat_file2.R",
        "test-new_fun2.R"
      )
    )

    expect_equal(
      list.files(file.path(dummypackage, "vignettes/")),
      c("get-started.Rmd", "get-started_2.Rmd")
    )


    # Let's check a other way to choose the vignette name
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = c("name" = "index"), check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    unlink(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE))
    expect_true(length(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE)) == 0)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "vignettes/")),
      c("get-started.Rmd", "index.Rmd")
    )
  })
})

unlink(dummypackage, recursive = TRUE)
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_read_inflate_params.Rmd",
  vignette_name = "Inflate all your flat files",
  check = FALSE,
  overwrite = TRUE,
  open_vignette = FALSE
)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```
