---
title: "flat_init_share_on_github.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

**You write R scripts and you would like to share them with other users, in a sustainable and maintainable way. You already know how to write a notebook (Rmarkdown or Quarto) and share its HTML output, but you do not like to present the outputs along with how to use the functions in the same web page.**

# Initiate GitHub to share your work on a website

- Create a new project with {fusen} using git
```{r}
#| echo: false
#| eval: false
path_project <- "your/path/where/to/start/your/project/project_name"
fusen::create_fusen(path = path_project, template = "minimal", with_git = TRUE, open = TRUE)
```

- Follow the "dev/0-dev_history.Rmd" to describe your project
  + At least, you will have to fill the `fusen::fill_description()` function with your identity as below
```{r}
#| eval: false
# Describe your project
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Share Your Project Following Good Development Practices From a Rmarkdown File",
    Description = "Use Rmarkdown First method. Strengthen your work with documentation and tests. Everything can be set from a Rmarkdown file in your project.",
    `Authors@R` = c(
      person("John", "Doe", email = "john@email.me", role = c("aut", "cre"), comment = c(ORCID = "0000-0000-0000-0000"))
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("John Doe")
```

- Open the "dev/flat_full.Rmd"
  + This is the skeleton to follow if you want a properly documented and tested work
    + Write what the code is supposed to do in plain markdown
    + Separate the `function` from the `example` and `test` chunks
    + Create new sections below in your flat template with the Addin > add {fusen} chunk
- Then `inflate()` the flat template to build the proper structure of the project
    + Sections will be transferred in the correct places to get a proper package
    + A set of checks will be run to verify that your work is properly documented and tested
```{r}
#| eval: false
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```

- Share your work on a website using GitHub
  + You may need to run `usethis::create_github_token()`, then `gitcreds::gitcreds_set()` before, if you do not have a registered GitHub token yet.
  + You will be asked multiple times if you want to commit, you can say "yes" each time.

```{r function-init_share_on_github}
#' Initiate GitHub to share your work on a website
#'
#' This uses {pkgdown} to share the documentation of the package through GitHub Actions.
#' You may need to run `usethis::create_github_token()`, then `gitcreds::gitcreds_set()` before.
#'
#' @return The URL of the website created
#' @export
#'
#' @examples
init_share_on_github <- function() {
  pkg <- "."
  
  # Init git if not already initiated
  repo <- tryCatch(gert::git_find(pkg), error = function(e) NULL)
  if (!is.null(repo)) {
    to_init <- is.na(gert::git_info(pkg)[["head"]])
  } else {
    to_init <- TRUE
  }
  if (to_init) {
    sure <- paste0("git is not initiated yet\n",
                   "Do you want to init and commit the current state? (y/n)\n")
    do_it <- readline(sure) == "y"
    if (do_it) {
      cli::cat_rule("Init Git Repository with first commit")
      gert::git_init(path = pkg)
      gert::git_add(".")
      gert::git_commit_all(message = "chore: Init repository")
      if (requireNamespace("rstudioapi") && rstudioapi::isAvailable()) {
        message("After the procedure, you'll want to restart your RStudio session")
      }
    } else {
      stop("Please Init you git repository using `usethis::use_git()`")
    }
  }

  # Init GitHub connexion
  cli::cat_rule("Init GitHub Connexion")
  info_git <- gert::git_remote_list()
  if (nrow(info_git) == 0) {
    usethis::use_github()
  } else if (grepl("github", info_git[info_git$name == "origin", "url"])) {
    message("Your repository is already connected to a remote GitHub repository: ",
            info_git[info_git$name == "origin", "url"])
  } else {
    stop("Your repository is not connected to a GitHub repository: ", info_git[info_git$name == "origin", "url"])
  }
  
  msg <- character(0)
  
  # Add a DESCRIPTION if not exists
  if (!file.exists("DESCRIPTION")) {
    cli::cat_rule("Add DESCRIPTION")
    fill_description(pkg = pkg)
    msg <- c(msg, "You need to fill your DESCRIPTION file. See `?fusen::fill_description`.")
  }
  
  # Add a NEWS if not exists
  if (!file.exists("NEWS.md")) {
    cli::cat_rule("Add NEWS")
    usethis::use_news_md()
  }
  
  # Add a Readme if not exists
  if (!file.exists("README.Rmd")) {
    cli::cat_rule("Add Readme")
    usethis::use_readme_rmd()
  }
  
  # Add GitHub Actions with pkgdown
  cli::cat_rule("Init GitHub Actions")
  usethis::use_github_action_check_standard()
  usethis::use_github_action("pkgdown")
  usethis::use_github_action("test-coverage")
  
  # Get info for website
  github_url <- gert::git_remote_info()$url
  github_url_no_git <- gsub("[.]git$", "", github_url)
  username <- gsub("https://github.com/(.*)/.*$", "\\1", github_url_no_git)
  projname <- gsub(paste0("https://github.com/", username, "/(.*)$"), "\\1", github_url_no_git)
  url_pages <- paste0("https://", username, ".github.io/", projname)
    
  # Knit the Readme file
  cli::cat_rule("Update and Knit the Readme file")
  readme_lines <- readLines("README.Rmd")
  add_line <- grep("## Example", readme_lines)[1]
  readme_lines[add_line] <- paste0(
    "## Documentation\n\n",
    "Full documentation website on: ", url_pages,
    "\n\n",
    readme_lines[add_line]
  )
  cat(readme_lines, file = "README.Rmd", sep = "\n")
  knitr::knit("README.Rmd")
  msg <- c(msg, "You will want to update your README.Rmd file. And then `knit()` it.")
  
  # Push to the repository
  cli::cat_rule("Push to GitHub and wait for publication")
  gert::git_add(".")
  gert::git_commit_all(message = "chore: Init Actions and website")
  gert::git_push()
  
  # Message website
  cli::cat_rule("Make sure GitHub is set for your website publication")
  url_setting_pages <- paste0(github_url_no_git, '/settings/pages')
  url_actions <- paste0(github_url_no_git, '/actions/workflows/pkgdown.yaml')
  # usethis::ui_todo(
  # cli::cli_warn(
  cat(
    cli::cli_text("1 - Wait for the 'pkgdown' Actions 'chore: Init Actions and website' to finish on: {.url {url_actions}}."),
    
    cli::cli_text("2 - Once the 'gh-pages' branch is created, you need to tell GitHub to follow it."),
    cli::cli_text("Go to: {.url  {url_setting_pages}} and choose 'gh-pages' in the 'Branch' drop-down menu, instead of 'None'."),
    cli::cli_text("You may need to wait for it to be created by GitHub Actions."),
    
    # browseURL(paste0(github_url_no_git, "/settings/pages"))
    cli::cli_text("3 - In a few seconds, you'll be able to see your project website at: {.url {url_pages}}"),
    cli::cli_text("Now it's time to continue your project: fill the flat file, inflate, push to GitHub."),
    cli::cli_text("> Infos: ", paste(msg, collapse = " - ")),
    {if (!dir.exists("R")) cli::cli_text("> Note: The Action 'R-CMD-check' may fail as you do not have any function in your package yet. Inflate your flat file with a function once, and it should be good.")},
    {if (!dir.exists("tests")) cli::cli_text("> Note: The Action 'test-coverage' may fail as you do not have any test in your package yet. Inflate your flat file with a unit test once, and it should be good.")}
  )
  
  return(url_pages)
}
```

```{r examples-init_share_on_github, eval=FALSE}
#' \dontrun{
init_share_on_github()
#' }
```

_In a few minutes, you'll be able to see and share your project website._  
You won't have to run this command line again. 
Each time you push new commits to the main branch on GitHub, your website will be updated thanks to GitHub Actions.

```{r tests-init_share_on_github}
test_that("init_share_on_github works", {
  
  skip_if_not(interactive())
  
  if (Sys.getenv("FUSEN_TEST_PUBLISH", unset = "FALSE") == "TRUE") {
    # Only create the project if specifically asked by maintainers
    path_project <- file.path(tempdir(), paste0("fusen.github.", packageVersion("fusen"))) 
    # path_project <- tempfile("fusen.github.proj")
    the_devs <- create_fusen(path = path_project, template = "minimal", with_git = TRUE, open = FALSE)
    the_flat <- the_devs[grep("flat", the_devs)]
    # Follow the "dev/0-dev_history.Rmd"
    usethis::with_project(path_project, {
      fill_description(
        pkg = path_project,
        fields = list(
          Title = "Share Your Project Following Good Development Practices From a Rmarkdown File",
          Description = "Use Rmarkdown First method. Strengthen your work with documentation and tests. Everything can be set from a Rmarkdown file in your project.",
          `Authors@R` = c(
            person("John", "Doe", email = "john@email.me", role = c("aut", "cre"), comment = c(ORCID = "0000-0000-0000-0000"))
          )
        )
      )
      # Define License with use_*_license()
      usethis::use_mit_license("John Doe")
      
      # Inflate ?
      # inflate(flat_file = the_flat, vignette_name = "Get started", open_vignette = FALSE)
    })
    
    usethis::with_project(path_project, {
      # Share on GitHub
      website_url <- init_share_on_github()
    }) # End of with_project
  
    do_it <- readline("Does pkgdown website exists after following instructions? (y/n)") == "y"
    expect_true(do_it)
  }
  unlink(path_project, recursive = TRUE)
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_init_share_on_github.Rmd", vignette_name = "Share on a GitHub website", overwrite = TRUE, check = FALSE)

rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```

