---
title: "flat_df_to_config.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

This vignette shows tools that are used internally to {fusen} to keep track of all files created during the `inflate()` process. 
They are exported for users who start using {fusen} >= 0.5, in a package built without {fusen}, or with earlier versions of {fusen}.  

The recommended process for a migration is:  

- Run `check_not_registered_files()` on your package
- Open the "dev/config_not_registered.csv" file
  + The csv contains all existing "R/", "tests/" and "vignettes/" files
  + If you used earlier version of {fusen}, the csv may list the flat file of origin
- Clean or modify the csv file
  + Let `origin = "keep"` for files to keep, that are not coming from a flat file
- Run `df_to_config()`


## Protect existing R, tests and vignettes files

`df_to_config()` allows to add your own list of files that you want to `keep` in your package, despite not beeing created with a flat file.  
This is important if you started to develop without {fusen}, and start using a flat file from now on, so that {fusen} does not delete your existing files.

```{r function-df_to_config, filename="clean_fusen_files"}
#' Add a tibble of files and types to the 'fusen' config file
#' @param df_files A dataframe with 'type' and 'path' columns
#' or a csv file path as issued from `[check_not_registered_files()]`
#' or nothing (and it will take the csv file in "dev/")
#' @param flat_file_path Character. Usually `"keep"` or the name of the origin flat file, although inflating the flat file should have the same result.
#' @param force Logical. Whether to force writing the configuration file even with potential errors.
#'
#' @importFrom stats setNames
#'
#' @return Config file path.
#' Side effect: create a yaml config file.
#'
#' @details
#' - Only types: "R", "test", "vignette" are accepted.
#' - All `path` should exist.
#' - Change path to config file with `options(fusen.config_file = "dev/config_fusen.yaml")`
#'
df_to_config <- function(df_files, flat_file_path = "keep", force = FALSE) {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  # User entry verifications
  if (missing(df_files)) {
    df_files <- file.path(dirname(config_file), "config_not_registered.csv")
  }

  if (!is.data.frame(df_files) && file.exists(df_files)) {
    df_files <- read.csv(df_files)
  } else if (!is.data.frame(df_files) && !file.exists(df_files)) {
    stop("'", df_files, "' does not exist. You can run `check_not_registered_files()` before.")
  }

  # Then if is.data.frame(df_files)
  if (!all(c("type", "path") %in% names(df_files))) {
    stop("df_files should contains two columns named: 'type' and 'path'")
  }

  if (!"origin" %in% names(df_files)) {
    df_files[["origin"]] <- flat_file_path
  } else {
    # check origin exists
    df_files_origin <- df_files[["origin"]]
    df_files_origin <- df_files_origin[df_files_origin != "keep"]
    all_exists <- file.exists(df_files_origin)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'origin' in df_files do not exist:",
        paste(
          paste0(
            "row ", which(!all_exists), ": ",
            df_files[["origin"]][!all_exists]
          ),
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli::cli_alert_warning(
          paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  }

  if (!all(grepl("^R$|^r$|^test$|^tests$|^vignette$|^vignettes$", df_files[["type"]]))) {
    stop("Only types 'R', 'test' or 'vignette' are allowed")
  }
  all_exists <- file.exists(df_files[["path"]])
  if (!all(all_exists)) {
    msg <- paste(
      "Some 'path' in df_files do not exist:",
      paste(
        paste0(
          "row ", which(!all_exists), "- ",
          df_files[["type"]][!all_exists], ": ",
          df_files[["path"]][!all_exists]
        ),
        collapse = ", "
      )
    )

    if (isTRUE(force)) {
      cli::cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  df_files$path <- normalizePath(df_files$path)
  df_files$origin <- normalizePath(df_files$origin)

  if (any(duplicated(df_files$path))) {
    msg <- paste("Some paths appear multiple times in df_files. Please remove duplicated rows: ", paste(unique(df_files$path[duplicated(df_files$path)]), collapse = ", "))

    if (isTRUE(force)) {
      cli::cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  if (file.exists(config_file)) {
    complete_yaml <- yaml::read_yaml(config_file)

    yaml_paths <- get_list_paths(complete_yaml)
    all_exists <- file.exists(yaml_paths)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'path' in config_file do not exist:",
        paste(
          yaml_paths[!all_exists],
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli::cli_alert_warning(
          paste(msg, "However, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  } else {
    complete_yaml <- list()
  }

  each_flat_file_path <- unique(df_files[["origin"]])
  all_groups_list <- lapply(each_flat_file_path, function(x) update_one_group_yaml(df_files, complete_yaml, x)) %>%
    setNames(basename(each_flat_file_path))

  all_modified <- names(complete_yaml)[names(complete_yaml) %in% names(all_groups_list)]

  if (length(all_modified) != 0) {
    cli::cli_alert_info(
      paste0(
        "Some files group already existed and were overwritten: ",
        paste(all_modified, collapse = ", ")
      )
    )
    complete_yaml[all_modified] <- NULL
  }

  # Combine with complete_yaml
  complete_yaml <- c(complete_yaml, all_groups_list)
  complete_yaml <- complete_yaml[sort(names(complete_yaml))]

  # Get duplicated paths after update
  yaml_paths <- unlist(complete_yaml)

  if (any(duplicated(yaml_paths))) {
    which_file <- files_list_to_vector(
      lapply(complete_yaml, files_list_to_vector)
    )

    if (isTRUE(force)) {
      cli::cli_alert_warning("Some paths appear multiple times in the config file. The yaml was forced with `force = TRUE`. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"))
    } else {
      stop("Some paths would appear multiple times in the future config file. The yaml has not been created. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"), "\nOr use `force = TRUE`")
    }
  }

  yaml::write_yaml(complete_yaml, file = config_file)

  return(config_file)
}

#' Extract name of file along with type to inform the user
#' @param list_of_files A named list of files
#' @noRd
files_list_to_vector <- function(list_of_files) {
  lapply(seq_along(list_of_files), function(x) {
    if (length(list_of_files[[x]]) != 0) {
      paste(names(list_of_files[x]), list_of_files[[x]], sep = ": ")
    }
  }) %>% unlist()
}

#' Update one group in the complete yaml as list
#' @param complete_yaml The list as output of config_yaml file
#' @param flat_file_path The group to update
#' @noRd
update_one_group_yaml <- function(df_files, complete_yaml, flat_file_path) {
  all_keep_before <- complete_yaml[[basename(flat_file_path)]]

  this_group_list <- list(
    path = flat_file_path,
    R = c(df_files$path[grepl("^R$|^r$", df_files$type)]),
    tests = c(df_files$path[grepl("^test$|^tests$", df_files$type)]),
    vignettes = c(df_files$path[grepl("^vignette$|^vignettes$", df_files$type)])
  )

  # All these will be deleted

  # Those removed
  those_removed <- setdiff(
    all_keep_before,
    this_group_list
  )
  those_removed_vec <- files_list_to_vector(those_removed)
  those_added <- setdiff(
    this_group_list,
    all_keep_before
  )
  those_added_vec <- files_list_to_vector(those_added)

  if (!is.null(those_removed_vec) || length(those_removed_vec) != 0) {
    silent <- lapply(paste(those_removed_vec, "was removed from the config file"), cli::cli_alert_warning)
  }
  if (!is.null(those_added_vec) || length(those_added_vec) != 0) {
    silent <- lapply(paste(those_added_vec, "was added to the config file"), cli::cli_alert_success)
  }

  return(this_group_list)
}
```

```{r examples-df_to_config, eval=FALSE}
# Add your own list of files to "keep",
# if they are not in a flat file.
# Otherwise, they may be deleted with your next `inflate()`
my_files_to_protect <- tibble::tribble(
  ~type, ~path,
  "R", "R/zaza.R",
  "R", "R/zozo.R",
  "test", "tests/testthat/test-zaza.R",
  "vignette", "vignettes/my-zaza-vignette.Rmd"
)

# \dontrun{
df_to_config(my_files_to_protect)
# }
```

```{r tests-df_to_config}
# Test df_to_config with custom config file path ----
config_file_path <- tempfile(fileext = ".yaml")

test_that("df_to_config fails when appropriate", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    all_files <- tibble::tribble(
      ~type, ~files,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files, flat_file_path = "keep"),
      "df_files should contains two columns named: 'type' and 'path'"
    )

    all_files <- tibble::tribble(
      ~type, ~path,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files),
      "Some files in df_files do not exist:  R: zaza.R, R: zozo.R, test: test-zaza.R"
    )
  })
})

# Create files, even empty
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R")))

test_that("df_to_config works", {
  withr::with_options(list(fusen.config_file = config_file_path), {

    # Use full path
    all_files <- tibble::tribble(
      ~type, ~path,
      "R", file.path(dir_tmp, "zaza.R"),
      "R", file.path(dir_tmp, "zozo.R"),
      "test", file.path(dir_tmp, "test-zaza.R")
    )

    expect_message(config_file_out <- df_to_config(all_files))
  })

  expect_equal(config_file_out, config_file_path)
  all_keep <- yaml::read_yaml(config_file_out)
  expect_equal(names(all_keep), "keep")
  expect_equal(names(all_keep$keep), c("path", "R", "tests", "vignettes"))
  expect_equal(all_keep$keep$path, c("keep"))
  expect_equal(basename(all_keep$keep$R), c("zaza.R", "zozo.R"))
  expect_equal(basename(all_keep$keep$tests), c("test-zaza.R"))
  expect_equal(all_keep$keep$vignettes, list())
})

# Second pass
all_files <- tibble::tribble(
  ~type, ~path,
  "r", file.path(dir_tmp, "tata.R"),
  "R", file.path(dir_tmp, "toto.R"),
  "tests", file.path(dir_tmp, "test-tata.R"),
  "vignettes", file.path(dir_tmp, "tata_vignette.Rmd")
)

file.create(file.path(dir_tmp, c("tata.R", "toto.R", "test-tata.R", "tata_vignette.Rmd")))

withr::with_options(list(fusen.config_file = config_file_path), {
  # debugonce(df_to_config)
  expect_message(
    config_file <- df_to_config(all_files),
    regexp = "Some files group already existed and were overwritten: keep"
  ) # "keep" is default
})

# rstudioapi::navigateToFile(config_file)
```

## List files that are not registered in config
    
{fusen} now registers all files created during `inflate()`. 
This allows to clean the packages directories in case some functions do not exist anymore and were renamed.  
However, this also requires to register all existing files if you started your package without {fusen} or with an earlier version of {fusen}.  
`check_not_registered_files()` shows files that are not already registered in the yaml config file. The output is consistent with what is needed for `df_to_config()` to register them if wanted.  
Note that `check_not_registered_files()` will try to guess the source flat template, if you used {fusen} >= 0.4 before.

```{r function-check_not_registered_files, filename="clean_fusen_files"}
#' Show in a table files that are not already registered in the yaml config file
#'
#' If user start their package without 'fusen' or with version < 0.4, they need to create the config file, with already existing functions.
#'
#' @param path Path to package to check for not registered files
#' @param guess Logical. Guess if the file was inflated by a specific flat file
#' @param to_csv Logical. Whether to store along the config file, the outputs in a csv for the user to clean it manually
#' @return Path to csv file if `to_csv` is TRUE. `dput()` of the dataframe otherwise.
#'
#' @export
check_not_registered_files <- function(path = ".", guess = TRUE, to_csv = TRUE) {
  path <- normalizePath(path)

  all_r <- list.files(file.path(path, "R"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_test <- list.files(file.path(path, "tests", "testthat"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_vignette <- list.files(file.path(path, "vignettes"), pattern = "[.]Rmd$|[.]rmd$", full.names = TRUE)

  res <- data.frame(
    type = c(
      rep("R", length(all_r)),
      rep("test", length(all_test)),
      rep("vignette", length(all_vignette))
    ),
    path = c(
      all_r, all_test, all_vignette
    )
  )

  if (nrow(res) == 0) {
    message("There are no files in the package. Did you inflate it once?")
    return(NULL)
  }

  # TODO Are they in the config file already ?
  # Read config file, and remove those already there
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (file.exists(config_file)) {
    config_list <- yaml::read_yaml(config_file)
    config_list_path <- get_list_paths(config_list)
    res_existing <- res[res$path %in% config_list_path, ]
    res_new <- res[!res$path %in% config_list_path, ]
  } else {
    res_existing <- res[FALSE, ]
    res_new <- res
  }

  if (nrow(res_new) == 0) {
    cli::cli_alert_info("There are no unregistered files")
    return(NULL)
  }

  # Guess those not in config_file
  # All files without path, are changed for "keep"
  if (isTRUE(guess)) {
    # List all files
    res_new$origin <- unlist(lapply(res_new$path, guess_flat_origin))
  } else {
    res_new$origin <- "keep"
  }

  csv_file <- file.path(dirname(config_file), "config_not_registered.csv")
  # Save for manual modification
  if (isTRUE(to_csv)) {
    write.csv(res_new, csv_file, row.names = FALSE)
    cli::cli_alert_info(paste(
      "Wrote not registered files in: ", csv_file,
      "\nKeep only those necessary and run `df_to_config()` on the csv file."
    ))

    return(csv_file)
  } else {
    # return a `dput()` to allow to add to `df_to_config()`
    # dput()
    return(dput(res_new))
  }
}

#' Guess flat file of origin of a script
#'
#' @param path Path of the script to test
guess_flat_origin <- function(path) {
  lines <- readLines(path)

  guess_path <- sub(
    ".* from\\s*/(.+[.].{1}md).*", "\\1",
    lines[grep("(G|g)enerated by \\{fusen\\} from", lines)][1]
  )

  guess_path <- normalizePath(guess_path, mustWork = FALSE)
  if (file.exists(guess_path)) {
    return(guess_path)
  } else {
    return("No existing source path found. Write 'keep', the full path to the flat file source., or delete this line.")
  }
}

#' Get all paths from a config list
#' @param config_list List as read from config.yaml file
#' @noRd
get_list_paths <- function(config_list) {
  unlist(lapply(config_list, function(x) {
    x$path <- NULL
    x
  }))
}
```
  
```{r example-check_not_registered_files, eval=FALSE}
#' \dontrun{
# Run this on the current package in development
out_csv <- check_not_registered_files()
out_csv
#' }
```

```{r example2-check_not_registered_files, eval=TRUE}
# Or you can try on the reproducible example
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
suppressMessages(
  inflate(
    pkg = dummypackage, flat_file = flat_file,
    vignette_name = "Get started", check = FALSE,
    open_vignette = FALSE
  )
)
# Add a not registered file to the package
cat("# test R file", file = file.path(dummypackage, "R", "to_keep.R"))
  
# Use the fonction to check the list of files
out_csv <- check_not_registered_files(dummypackage)
out_csv
# Modify manually the list of files in the csv created
# Then read the file to add to the config file
content_csv <- read.csv(out_csv)
out_config <- df_to_config(df_files = out_csv)
out_config
# Open the out_config file to see what's going on
```


```{r tests-check_not_registered_files}
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {
  test_that("check_not_registered_files returns message if empty", {
    expect_true(inherits(check_not_registered_files, "function"))

    # debugonce(check_not_registered_files)
    expect_message(check_not_registered_files(), "There are no files in the package")
  })

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  guessed_path <- guess_flat_origin(file.path(dummypackage, "R", "my_median.R"))
  expect_equal(guessed_path, file.path(dummypackage, "dev", "flat_full.Rmd"))

  guessed_path <- guess_flat_origin(file.path(dummypackage, "dev", "0-dev_history.Rmd"))
  expect_true(grepl("No existing source path found", guessed_path))

  expect_message(out_csv <- check_not_registered_files(),
    regexp = "Wrote not registered files in:  dev/config_not_registered.csv"
  )

  content_csv <- read.csv(out_csv)
  expect_true(all(names(content_csv) %in% c("type", "path", "origin")))
  expect_equal(content_csv[["type"]], c("R", "R", "test", "test", "vignette"))

  # Include it in df_to_config()
  out_config <- df_to_config(df_files = out_csv)
  out_config_content <- yaml::read_yaml(out_config)
  expect_true(names(out_config_content) == "flat_full.Rmd")
  expect_equal(
    names(out_config_content[["flat_full.Rmd"]]),
    c("path", "R", "tests", "vignettes")
  )
  # rstudioapi::navigateToFile(out_config)

  # Test add a R file manually and include in "keep" after `check_not_registered_files()`
  cat("# test R file", file = file.path(dummypackage, "R", "to_keep.R"))

  out_csv <- check_not_registered_files()
  content_csv <- read.csv(out_csv)
  expect_true(
    grepl(
      "No existing source path found",
      content_csv[grepl("to_keep.R", content_csv[, "path"]), "origin"]
    )
  )

  # Add in the yaml file with `df_to_config()`
  keep_to_add_to_config <- content_csv[grepl("to_keep.R", content_csv[, "path"]), ]
  keep_to_add_to_config$origin <- "keep"

  out_config <- df_to_config(keep_to_add_to_config)
  # rstudioapi::navigateToFile(out_config)
  out_config_content <- yaml::read_yaml(out_config)
  expect_true(grepl("to_keep[.]R", out_config_content$keep$R))

  expect_message(
    out_csv <- check_not_registered_files(),
    "There are no unregistered files"
  )
  expect_true(is.null(out_csv))

  # Add  same file in the yaml file with `df_to_config()` using different origin (existing one, but duplicate R file)
  keep_to_add_to_config$origin <- "dev/flat_full.Rmd"

  expect_error(
    df_to_config(keep_to_add_to_config),
    "Some paths would appear multiple times in the future config file."
  )

  # Add  same file in the yaml file with `df_to_config()` using different origin (not existing)
  keep_to_add_to_config$origin <- "dev/flat_dont_exists.Rmd"

  expect_error(
    df_to_config(keep_to_add_to_config),
    "Some 'origin' in df_files do not exist: row 1: dev/flat_dont_exists.Rmd"
  )
})
```
  
# clean_fusen_files
    
```{r function-clean_fusen_files, filename="clean_fusen_files"}
#' Title
#'
#' Description
#'
#' @return
#'
#' @export
clean_fusen_files <- function() {

}
```
  
```{r example-clean_fusen_files}
clean_fusen_files()
```
  
```{r tests-clean_fusen_files}

# Test full ----
# Change options(fusen.config_file = "dev/config_fusen.yaml")
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

# Detect all files created ----
usethis::with_project(dummypackage, {
  browser()

  # Create empty config file

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  debugonce(inflate)
})
```
  

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_clean_fusen_files.Rmd", vignette_name = "Clean {fusen} files", check = FALSE)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```
