---
title: "flat_inflate_all.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r development, include=FALSE}
library(testthat)
library(yaml)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Inflate all your flat files at once

The `inflate_all()` function allows the user to inflate all the flat files available in the "dev/" directory at once.
This requires to inflate each new flat file individually at least once in order to register the inflate parameters.

Prior to be able to inflate all the flat files, some checks are performed, to assess whether the flat files are available to be used by `inflate_all()`.

Indeed, `inflate_all()` requires the existence of a complete {fusen} configuration file: "dev/config_fusen.yaml". This file exists only from versions of {fusen} upper than v0.5.0:

- If you are working in a project initiated with a version of {fusen} prior to v0.5.0, please manually run `inflate()` for each of the flat files you want to work with, in order to create the appropriate "dev/config_fusen.yaml" file.

- If you are already familiar with "dev/config_fusen.yaml" but were working with a dev version of {fusen} prior to v0.6.0, your "dev/config_fusen.yaml" file does not contain inflate-related parameters. You will have to inflate again you flat files in order to complete the configuration file with the proper `inflate()` parameters.

There is a wrapper named `inflate_all_no_check()` that will prevent running `check()`. This is a short version of `inflate_all(check = FALSE)`.

```{r function-inflate_all}
#' Inflate all your flat files
#'
#' Inflate all the flat files stored in "dev/" and starting with "flat_"
#'
#' @param pkg Path to package
#' @param clean Logical. Whether to help detect unregistered files.
#' @inheritParams inflate
#'
#' @importFrom yaml read_yaml
#' @importFrom cli cat_rule
#' @importFrom devtools check
#'
#' @return side effect. Inflates all your flat files that can be inflated.
#' 
#' @details This requires to [inflate()] all flat files individually at least once, so that their specific inflate configurations are stored.  
#' 
#' This also requires to register all R, tests and vignettes files of your package, even if not created with an inflate. Run [inflate_all()] once and read the messages. The first time, you will probably need to run [register_all_to_config()] if your package is not new.
#'
#' @seealso
#'   [inflate()] for the options of a single file inflate,
#'   [check_not_registered_files()] for the list of files not already associated with a flat file in the config file,
#'   [register_all_to_config()] for automatically registering all files already present in the project before the first `inflate_all()`
#'
#' @export
inflate_all <- function(pkg = ".", document = TRUE, check = TRUE, open_vignette = FALSE, overwrite = TRUE, clean = TRUE, ...) {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (!file.exists(config_file)) {
    stop("There is no fusen.config_file in your package. Your flat files must be inflated at least once manually before you can use `inflate_all()`. If you were using a fusen prior to v0.5.0.9000 you must inflate all your flat files manually once again.")
  }

  config_yml <- read_yaml(config_file)

  diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = pkg)
  # Run stop first only
  pre_inflate_all_diagnosis_eval(diag, type_stop = TRUE)
  # If message or warnings about flat files, show at the end of the process
  # => Is going to be
  pre_inflate_all_diagnosis_eval(diag, type_stop = FALSE)

  inflate_params <- read_inflate_params(config_yml = config_yml)

  if (length(inflate_params) == 0) {
    message("No flat files were inflated")
  } else {
    apply_inflate <- function(inflate_params, pkg, overwrite, open_vignette) {
      config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")
      # Change config option temporary, to be able to modify it on the fly
      config_file_tmp <- tempfile(pattern = "tempconfig")
      on.exit(file.remove(config_file_tmp))
      file.copy(config_file, to = config_file_tmp)
      options("fusen.config_file" = config_file_tmp)
      on.exit(options("fusen.config_file" = config_file))

      invisible(
        lapply(inflate_params, function(flat_file) {
          flat_file$pkg <- pkg
          flat_file$overwrite <- overwrite
          flat_file$open_vignette <- open_vignette
          flat_file$document <- FALSE
          flat_file$check <- FALSE
          suppressMessages(do.call(inflate, flat_file))
        })
      )
    }

    apply_inflate(inflate_params, pkg = pkg, overwrite = overwrite, open_vignette = open_vignette)

    # Document and check package
    document_and_check_pkg(
      pkg = pkg,
      check = check,
      document = document,
      ...
    )
  }
  
  if (isTRUE(clean)) {
    cli::cat_rule("check not registered files")
    invisible(check_not_registered_files(path = pkg))
  }
  invisible(pkg)
}

#' @rdname inflate_all
#' @export
inflate_all_no_check <- function(pkg = ".", document = TRUE, open_vignette = FALSE, overwrite = TRUE, clean = TRUE, ...) {
  inflate_all(pkg = pkg, document = document, check = FALSE, open_vignette = open_vignette, overwrite = overwrite, clean = clean, ...)
}
```
  
```{r example-inflate_all, eval=FALSE}
#' \dontrun{
# Usually, in the current package run inflate_all() directly
# These functions change the current user workspace
inflate_all()
# Or inflate_all_no_check() to prevent checks to run
inflate_all_no_check()
#' }

# You can also inflate_all flats of another package as follows
# Example with a dummy package with a flat file
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
flat_files <- add_minimal_package(
  pkg = dummypackage,
  overwrite = TRUE,
  open = FALSE
)
flat_file <- flat_files[grep("flat", basename(flat_files))]
# Inflate the flat file once
usethis::with_project(dummypackage, {
  # if you are starting from a brand new package, inflate_all() will crash
  # it's because of the absence of a fusen config file
  #
  # inflate_all() # will crash

  # Add licence
  usethis::use_mit_license("John Doe")

  # you need to inflate manually your flat file first
  inflate(
    pkg = dummypackage,
    flat_file = flat_file,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE,
    document = TRUE,
    overwrite = "yes"
  )

  # your config file has been created
  config_yml_ref <-
    yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))
})

# Next time, you can run inflate_all() directly
usethis::with_project(dummypackage, {
  # now you can run inflate_all()
  inflate_all(check = FALSE, document = TRUE)
})

# Clean the temporary directory
unlink(dummypackage, recursive = TRUE)
```
  
```{r tests-inflate_all}
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_minimal_package(pkg = dummypackage, overwrite = TRUE, open = FALSE)

# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all is a function", {
  expect_true(inherits(inflate_all, "function"))
})

usethis::with_project(dummypackage, {
  # Add licence
  usethis::use_mit_license("John Doe")

  test_that("error if no config file exists", {
    # if no config file exists, we raise an error
    expect_error(inflate_all(), regexp = "There is no fusen[.]config_file in your package[.]")
  })

  # we inflate the flat file
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE, document = TRUE,
      overwrite = "yes"
    )
  )
  config_yml_ref <- yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

  test_that("inflate_all says which is going to be inflated", {
    expect_message(inflate_all(check = FALSE),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )
  })

  test_that("deprecated is detected and not inflated", {
    # Let's deprecate our flat file
    config_yml_deprecated <- config_yml_ref
    config_yml_deprecated[["flat_minimal.Rmd"]][["state"]] <- "deprecated"
    config_yml_deprecated[["flat_minimal.Rmd"]][["R"]] <- ""
    write_yaml_verbatim(config_yml_deprecated, file = "dev/config_fusen.yaml")

    # And remove R file to verify it is not rebuilt
    fun_file <- file.path("R", "my_fun.R")
    expect_true(file.exists(fun_file))
    file.remove(fun_file)

    expect_message(inflate_all(check = FALSE),
      regexp = glue::glue("The flat file {basename(flat_file)} is not going to be inflated because it is in state 'inactive or deprecated'")
    )

    expect_false(file.exists(fun_file))
  })

  test_that("new flat file, absent from config_fusen.yml works", {
    # Let's add a new flat file, absent from config_fusen.yml
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

    expect_message(inflate_all(check = FALSE),
      regexp = glue::glue("The flat file flat_minimal_2.Rmd is not going to be inflated because it is absent from the config file")
    )

    unlink(flat_file2)
  })

  test_that("error when remove params", {
    # Let's remove the inflate parameters from config_fusen.yml
    config_yml_no_inflate_params <- config_yml_ref
    config_yml_no_inflate_params[["flat_minimal.Rmd"]][["inflate"]] <- NULL
    write_yaml_verbatim(config_yml_no_inflate_params, file = "dev/config_fusen.yaml")

    expect_error(inflate_all(check = FALSE), regexp = "The flat file flat_minimal[.]Rmd is not going to be inflated because although present in the config file, it has no inflate\\(\\) parameters")
  })

  test_that("flat file in config_fusen.yml not present in dev", {
    # Let's add a flat file in config_fusen.yml not present in dev/
    config_yml_file_absent_in_dev <- config_yml_ref
    config_yml_file_absent_in_dev[["missing_file.Rmd"]] <- config_yml_file_absent_in_dev[["flat_minimal.Rmd"]]
    config_yml_file_absent_in_dev[["missing_file.Rmd"]][["path"]] <- "dev/missing_file.Rmd"
    write_yaml_verbatim(config_yml_file_absent_in_dev, file = "dev/config_fusen.yaml")

    expect_error(inflate_all(check = FALSE), regexp = "The file missing_file[.]Rmd is not going to be inflated because it was not found")
  })

  test_that("inflate all really inflates all", {
    # Now let's take the ability of inflate_all() to inflate all our files !
    # We start from a clean place
    write_yaml_verbatim(config_yml_ref, file = "dev/config_fusen.yaml")

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )
    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_false(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_false(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_false(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    inflate_all(check = FALSE)

    expect_true(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_true(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_true(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))
  })

  test_that("add a function in our flat file works", {
    # what happens if we add a function in our flat file
    flat_content <- readLines(flat_file)
    function_template <- readLines(system.file("inflate_all/fusen_chunk_template", package = "fusen"))

    writeLines(c(flat_content, function_template), con = flat_file)

    inflate_all(check = FALSE)

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c("test-my_fun.R", "test-new_fun2.R")
    )
  })

  test_that("A second flat file works", {
    # let's add a second flat
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started_2", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_true(length(list.files(file.path(dummypackage, "R"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "man"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE)) == 0)

    inflate_all(check = FALSE)

    expect_true(all(
      list.files(file.path(dummypackage, "R/")) %in% c("my_fun.R", "my_fun_from_flat_file2.R", "new_fun2.R")
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "man/")) %in% c("my_fun.Rd", "my_fun_from_flat_file2.Rd", "new_fun2.Rd")
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "tests/testthat")) %in% c(
        "test-my_fun.R",
        "test-my_fun_from_flat_file2.R",
        "test-new_fun2.R"
      )
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "vignettes/")) %in% c("get-started.Rmd", "get-started_2.Rmd")
    ))

    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))
    unlink(flat_file2)
  })

  test_that("inflate_all deals with vignette name", {
    write_yaml_verbatim(config_yml_ref, file = "dev/config_fusen.yaml")

    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    # Let's check a other way to choose the vignette name
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = c("name" = "index"), check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    unlink(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE))
    expect_true(length(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE)) == 0)

    inflate_all(check = FALSE)

    expect_true(all(list.files(file.path(
      dummypackage, "vignettes/"
    )) %in% c("get-started.Rmd", "index.Rmd")))
  })
})

unlink(dummypackage, recursive = TRUE)

# with no files named flat_ works ----

# You can also inflate_all flats of another package as follows
# Example with a dummy package with a flat file
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
flat_files <- add_minimal_package(
  pkg = dummypackage,
  overwrite = TRUE,
  open = FALSE
)
flat_file <- flat_files[grep("flat", basename(flat_files))]
# Change flat name
flat_file_newname <- gsub("flat_minimal[.]Rmd", "test_minimal.Rmd", flat_file)
file.rename(flat_file, flat_file_newname)

# Inflate the flat file once
usethis::with_project(dummypackage, {
  # Add licence
  usethis::use_mit_license("John Doe")

  # you need to inflate manually your flat file first
  inflate(
    pkg = dummypackage,
    flat_file = flat_file_newname,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE,
    document = TRUE,
    overwrite = "yes"
  )

  # your config file has been created
  config_yml_ref <-
    yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

  test_that("inflate_all with no files named flat_ works", {
    # now you can run inflate_all()
    expect_message(
      inflate_all(check = FALSE, document = TRUE),
      regexp = "The flat file test_minimal.Rmd is going to be inflated"
    )

    # Delete R file and see if it comes back
    the_file <- file.path("R", "my_fun.R")
    file.remove(the_file)
    expect_false(file.exists(the_file))

    inflate_all(check = FALSE, document = TRUE)
    expect_true(file.exists(the_file))
  })
})

# Clean the temporary directory
unlink(dummypackage, recursive = TRUE)

# Test inflate_all_no_check vs inflate_all with check ----
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_minimal_package(pkg = dummypackage, overwrite = TRUE, open = FALSE))

# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all_no_check is a function", {
  expect_true(inherits(inflate_all_no_check, "function"))
})

usethis::with_project(dummypackage, {
  # Add licence
  usethis::use_mit_license("John Doe")

  suppressMessages(
    inflate(
      pkg = dummypackage,
      flat_file = flat_file,
      vignette_name = "toto",
      check = FALSE,
      open_vignette = FALSE,
      document = TRUE,
      overwrite = "yes"
    )
  )

  test_that("when check = FALSE we ensure no check has been performed", {
    # no check
    utils::capture.output(inflate_all_no_check(),
      file = file.path(dummypackage, "dev/inflate_all_nocheck.txt")
    )

    expect_false(any(grepl(
      pattern = "R CMD check",
      x = readLines(file.path(
        dummypackage, "dev/inflate_all_nocheck.txt"
      ))
    )))
  })

  test_that("rmdcheck does not raise errors on the created package", {
    check_out <- rcmdcheck::rcmdcheck(dummypackage,
      quiet = TRUE,
      args = c("--no-manual")
    )
    expect_true(length(check_out[["errors"]]) == 0)
  })

  # run check on interactive mode only
  test_that("inflate_all with check = TRUE works", {
    skip_if_not(interactive())
    suppressMessages(inflate_all(
      check = TRUE,
      quiet = TRUE,
      args = c("--no-manual", "--no-build-vignettes"),
      check_dir = file.path(dummypackage, "dev/")
    ))
    check_lines <- readLines(file.path(dummypackage, "dev/", paste0(basename(dummypackage), ".Rcheck"), "00check.log"))
    expect_equal(check_lines[length(check_lines)], "Status: OK")
  })
})

unlink(dummypackage, recursive = TRUE)

# Test inflate_all detects unregistered files ----
dummypackage <- tempfile("inflateall.unregistered")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_minimal_package(pkg = dummypackage, overwrite = TRUE, open = FALSE))

flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {
  # Add licence
  suppressMessages(usethis::use_mit_license("John Doe"))

  suppressMessages(
    inflate(
      pkg = dummypackage,
      flat_file = flat_file,
      vignette_name = "toto",
      check = FALSE,
      open_vignette = FALSE,
      document = TRUE,
      overwrite = "yes"
    )
  )

  test_that("inflate_all detects unregistered files", {
    # Create an unregistered file
    cat("# unregistered file in R\n", 
        file = file.path(dummypackage, "R", "unregistered_r.R"))
    cat("# unregistered file in test\n", 
        file = file.path(dummypackage, "tests", "testthat", "test-unregistered_r.R"))
    
    expect_message(
      inflate_all_no_check(),
      regexp = "There are unregistered files in your package."
    )
    csv_file <- file.path("dev", "config_not_registered.csv")
    expect_true(file.exists(csv_file))
    
    csv_content <- read.csv(csv_file)
    csv_content <- csv_content[order(csv_content[["path"]]),]
    
    csv_content_expected <- structure(list(
      type = c("R", "test"),
      path = c("R/unregistered_r.R", 
               "tests/testthat/test-unregistered_r.R"), 
      origin = c("No existing source path found. Write 'keep', the full path to the flat file source, or delete this line.", 
                 "No existing source path found. Write 'keep', the full path to the flat file source, or delete this line."
      )), 
      row.names = 1:2,
      class = "data.frame")
    csv_content_expected <- csv_content_expected[order(csv_content_expected[["path"]]),]
    
    expect_equal(csv_content, csv_content_expected)
    
  })
  
  test_that("inflate_all is silent after files registered", {

    # register everything
    register_all_to_config()
        
    expect_message(
      inflate_all_no_check(),
      regexp = "There are no unregistered files"
    )
  })
  
  test_that("inflate_all is does not check registered if FALSE", {
    output <- capture.output(inflate_all_no_check(clean = FALSE))
    expect_false(any(grepl("registered", output)))
  })
  
})
unlink(dummypackage, recursive = TRUE)

```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_inflate_all.Rmd",
  vignette_name = "Inflate all your flat files",
  check = TRUE, # args = c("--no-manual", "--no-tests"),
  overwrite = TRUE,
  open_vignette = FALSE
)
# rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```

