---
title: "flat_df_to_config.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

## {fusen} registers all files created with a flat file

From {fusen} >=0.5, a "config_fusen.yaml" file registers all files created from a specific "flat" file as soon as you inflate it.
Hence, you can keep track on where to find the source of your functions and tests.
One of its major functionnality is to help you clean your package files in case you decide to change a function name, delete a function or change a vignette name.

To make this work properly, you will have to register all files that were not created from a flat file. `add_files_to_config()` will help you do so (See below: "Register some specific files, even with regex").  

If you use this version of {fusen} in an existing project, you will want to register all existing files to avoid a too strong clean up: `register_all_to_config()` will help you do so (See below: "How to migrate from previous {fusen} versions?").

## {fusen} helps you clean your old functions and tests files

{fusen} inflates your flat files to script files with pre-defined names stored in the correct place, so that you do not have to think about it. If you do not change the default behavior, scripts names are created from the name of each function created.  
Until version 0.4, if you decided to change the name of your function, or a function was obsolete, you had to clean it all manually.  
This time is over with {fusen} version >0.5!  
Now, {fusen} keeps track of files created with an `inflate()`, in a yaml configuration file. It also allows you to register all extra files that you decide are legitimate. 
Hence, {fusen} will be able to clean all files that are not necessary anymore in your package.


To make this work properly, all R, test and vignettes files will need to be registered in the "dev/config_fusen.yaml" file.  
{fusen} will try to guess the source flat file of each script. This will only be possible if you used {fusen} >= 0.4 before. Otherwise, you may want to follow the detailed process below.

## Delete files not anymore linked to a flat file

TODO - clean_fusen_files

### Register some specific files, even with regex

You may not want to register each new file that does not come during an inflate process. For instance, with {golem}, there are module (`^mod_*`) files, which need to be protected. You can add this regular expression directly in the yaml file with `add_files_to_config(c("R" = "^mod_*"))` 

## Deprecate flat files after inflate

If your practice of {fusen} is to inflate it once, and then continue development in the R, test and vignette files directly, then you may want to properly deprecated the flat file.   
We recommend to use `deprecate_flat_file()` to clean your script files (remove "do not edit"), update the config file and move the flat file in a "dev/dev_history" directory.

TODO

## How to migrate from previous {fusen} versions?

This vignette shows tools that are used internally to {fusen} to keep track of all files created during the `inflate()` process. 
They are visible to users as soon as they start using {fusen} >= 0.5, even if the package was built without {fusen}, or with an earlier version of {fusen}.  

The recommended process for a migration is:  

- Run `register_all_to_config()` in your current package to create the "dev/config_fusen.yaml" that registers all your existing files. 
 + You will note a "keep" section, which lists all files for which the source was not guessed. You can clean it up if you want.
- You're good to go with the new version of {fusen}

### You can take this opportunity to clean your repository

If you used earlier versions of {fusen}, it is possible that you have some remaining ".R" or test files. 
You may want to detect which scripts are linked to a flat file. 
If you are more familiar with ".csv" file than with the ".yaml" file above, or if you want a quick edit of multiple sources, you can run these intermediate steps:

- Run `check_not_registered_files()` on your package
- Open the "dev/config_not_registered.csv" file
  + The csv contains all existing "R/", "tests/" and "vignettes/" files
  + If you used earlier version of {fusen}, the csv may list the flat file of origin
- Clean or modify the csv file
  + Let `origin = "keep"` for files to keep, that are not coming from a flat file
- Run `df_to_config()`
- You're good to go with the new version of {fusen}



## The details of each function linked to config

You can continue reading if you are interesting in the functioning of these config file manipulations.

### Keep it all, I am sure of the current state

If all files of the current state are legitimate, then, you can register everything in the config file.

Run `register_all_to_config()` in your current package to create the "dev/config_fusen.yaml" that registers all your files. You will note a "keep" section, which lists all files for which the source was not guessed.

```{r function-register_all_to_config}
#' Include all existing package files in the config file
#'
#' Helps transition from non-fusen packages
#'
#' @param pkg Path to the package from which to add file to configuration file
#' @inheritParams df_to_config
#' @return Path to configuration file
#'
#' @export
register_all_to_config <- function(pkg = ".", clean = FALSE) {
  # Use the fonction to check the list of files
  out_df <- check_not_registered_files(pkg, to_csv = FALSE)

  if (is.null(out_df)) {
    message("There is no file to register or everything was already registered")
    return(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))
  }

  w.keep <- grep("No existing source path found", out_df[["origin"]])
  out_df[["origin"]][w.keep] <- "keep"
  out_config <- df_to_config(df_files = out_df, clean = clean)
  # rstudioapi::navigateToFile(file.path(pkg, "dev", "config_fusen.yaml"))
  return(invisible(out_config))
}
```

```{r example-register_all_to_config-1, eval=FALSE}
#' \dontrun{
# Usually run this one inside the current project
# Note: running this will write "dev/config_fusen.yaml" in your working directory
register_all_to_config()
#' }
```

<!-- Use eval=FALSE because inflate cannot work inside a Rmd vignette -->

```{r example-register_all_to_config-2, eval=FALSE}
# Or you can try on the reproducible example
dummypackage <- tempfile("register")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage, {
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )
  out_path <- register_all_to_config(dummypackage)

  # Look at the output
  yaml::read_yaml(out_path)
})
```

```{r tests-register_all_to_config}
# Or you can try on the reproducible example
dummypackage <- tempfile("register")
dir.create(dummypackage)
dir.create(file.path(dummypackage, "fusentest"))
dummypackage_fixed <- file.path(dummypackage, "fusentest")
# unlink(dummypackage, recursive = TRUE)
# {fusen} steps
fill_description(pkg = dummypackage_fixed, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage_fixed, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage_fixed, {
  suppressMessages(
    inflate(
      pkg = dummypackage_fixed, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )
})
# Add a not registered file to the package
cat("# test R file", file = file.path(dummypackage_fixed, "R", "to_keep.R"))


test_that("register_all_to_config can be run twice", {
  expect_true(inherits(register_all_to_config, "function"))

  usethis::with_project(dummypackage_fixed, {
    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )
    expect_equal(out_path, file.path("dev", "config_fusen.yaml"))

    # What happens if everything is already registered? ----
    expect_message(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = "There is no file to register"
    )

    expect_equal(out_path, file.path("dev", "config_fusen.yaml"))

    # Add a new file to register from a new flat file ----
    add_flat_template(template = "add", flat_name = "new_one", open = FALSE)
    # Without vignette first
    inflate(pkg = dummypackage_fixed, flat_file = "dev/flat_new_one.Rmd", vignette_name = NA, check = FALSE, open_vignette = FALSE)

    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )

    # With vignette then
    inflate(pkg = dummypackage_fixed, flat_file = "dev/flat_new_one.Rmd", vignette_name = "new_one", check = FALSE, open_vignette = FALSE)

    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )
  })

  # yaml::read_yaml(out_path)
})

test_that("config file is correctly built after half register", {
  out_actual <- yaml::read_yaml(file.path(dummypackage_fixed, "dev", "config_fusen.yaml"))
  # To update
  # file.copy(file.path(dummypackage_fixed, "dev", "config_fusen.yaml"), here::here("tests/testthat/config_fusen_register.yaml"), overwrite = TRUE)
  if (file.exists("config_fusen_register.yaml")) {
    out_expected <- yaml::read_yaml("config_fusen_register.yaml")
  } else {
    # during dev in root directory
    out_expected <- yaml::read_yaml(here::here("tests/testthat/config_fusen_register.yaml"))
  }

  expect_equal(out_actual, out_expected)
})

unlink(dummypackage, recursive = TRUE)
```


### Protect existing R, tests and vignettes files

`df_to_config()` allows to add your own list of files that you want to `keep` in your package, despite not being created with a flat file.  
This is important if you started to develop without {fusen}, and start using a flat file from now on, so that {fusen} does not delete your existing files.

```{r function-df_to_config, filename="clean_fusen_files"}
#' Add a tibble of files and types to the 'fusen' config file
#' @param df_files A dataframe with 'type' and 'path' columns
#' or a csv file path as issued from `[check_not_registered_files()]`
#' or nothing (and it will take the csv file in "dev/")
#' @param flat_file_path Character. Usually `"keep"` or the name of the origin flat file, although inflating the flat file should have the same result.
#' @param state Character. Whether if the flat file is `active` or `deprecated`.
#' @param force Logical. Whether to force writing the configuration file even is some files do not exist.
#' @param clean Logical. Delete list associated a specific flat file before updating the whole list. Default is set to TRUE during `inflate()` of a specific flat fil, as the list should only contain files created during the inflate. This parameter is set to FALSE with `register_to_config()` so that it can be run twice on the package when migrating from an old version of {fusen}. This could be set to FALSE with a direct use of `df_to_config()` too.
#' @param inflate_parameters list of parameters passed through a call to `inflate()`

#' @importFrom stats setNames
#' @importFrom utils read.csv
#'
#' @return Config file path.
#' Side effect: create a yaml config file.
#' @export
#'
#' @details
#' - Only types: "R", "test", "vignette" are accepted.
#' - All `path` should exist.
#' - Change path to config file with `options(fusen.config_file = "dev/config_fusen.yaml")`
#'
df_to_config <- function(df_files,
                         flat_file_path = "keep",
                         state = c("active", "deprecated"),
                         force = FALSE,
                         clean = TRUE,
                         inflate_parameters = NULL) {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")
  state <- match.arg(state, several.ok = FALSE)

  # User entry verifications
  if (missing(df_files)) {
    df_files <- file.path(dirname(config_file), "config_not_registered.csv")
  }

  if (!is.data.frame(df_files) && file.exists(df_files)) {
    df_files <- read.csv(df_files, stringsAsFactors = FALSE)
  } else if (!is.data.frame(df_files) && !file.exists(df_files)) {
    stop("'", df_files, "' does not exist. You can run `check_not_registered_files()` before.")
  }

  # Then if is.data.frame(df_files)
  if (!all(c("type", "path") %in% names(df_files))) {
    stop("df_files should contains two columns named: 'type' and 'path'")
  }



  if (!"origin" %in% names(df_files)) {
    df_files[["origin"]] <- flat_file_path
  } else {
    # check origin exists
    df_files_origin <- df_files[["origin"]]
    df_files_origin <- df_files_origin[df_files_origin != "keep"]
    all_exists <- file.exists(df_files_origin)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'origin' in df_files do not exist:",
        paste(
          paste0(
            "row ", which(!all_exists), ": ",
            df_files[["origin"]][!all_exists]
          ),
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli::cli_alert_warning(
          paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  }

  if (!all(grepl("^R$|^r$|^test$|^tests$|^vignette$|^vignettes$", df_files[["type"]]))) {
    stop("Only types 'R', 'test' or 'vignette' are allowed")
  }
  all_exists <- file.exists(df_files[["path"]])
  if (!all(all_exists)) {
    msg <- paste(
      "Some 'path' in df_files do not exist:",
      paste(
        paste0(
          "row ", which(!all_exists), "- ",
          df_files[["type"]][!all_exists], ": ",
          df_files[["path"]][!all_exists]
        ),
        collapse = ", "
      )
    )

    if (isTRUE(force)) {
      cli::cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  if (!is.null(inflate_parameters) & flat_file_path == "keep") {
    stop("The purpose of using \"keep\" is to store files created without inflate(). Therefore it is not allowed to provide inflate_parameters")
  }

  # Remove common part between config_file and all path
  # to get relative paths to project

  # TODO - When path does not exists, normalizePath does not correctly
  # use path.expand.
  # All path should exists. It is tested above.
  df_files$path <- gsub(
    paste0(normalize_path_winslash("."), "/"),
    "",
    normalize_path_winslash(df_files$path, mustWork = TRUE)
  )

  # All origin path should exist, if not "keep"
  df_files$origin[df_files$origin != "keep"] <- gsub(
    paste0(normalize_path_winslash("."), "/"),
    "",
    normalize_path_winslash(df_files$origin[df_files$origin != "keep"], mustWork = TRUE)
  )


  if (any(duplicated(df_files$path))) {
    msg <- paste("Some paths appear multiple times in df_files. Please remove duplicated rows: ", paste(unique(df_files$path[duplicated(df_files$path)]), collapse = ", "))

    if (isTRUE(force)) {
      cli::cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  if (file.exists(config_file)) {
    complete_yaml <- yaml::read_yaml(config_file)

    yaml_paths <- get_list_paths(complete_yaml)
    yaml_paths <- yaml_paths[!grepl("inflate\\.", names(yaml_paths))]
    all_exists <- file.exists(yaml_paths)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'path' in config_file do not exist:",
        paste(
          yaml_paths[!all_exists],
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli::cli_alert_warning(
          paste(msg, "However, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  } else {
    complete_yaml <- list()
  }

  each_flat_file_path <- unique(df_files[["origin"]])
  if (length(state) != length(each_flat_file_path)) {
    state <- rep(state, length.out = length(each_flat_file_path))
  }
  all_groups_list <- lapply(
    seq_along(each_flat_file_path),
    function(x) {
      update_one_group_yaml(
        df_files, complete_yaml,
        each_flat_file_path[x],
        state = state[x],
        clean = clean,
        inflate_parameters = inflate_parameters
      )
    }
  ) %>%
    setNames(basename(each_flat_file_path))

  all_modified <- names(complete_yaml)[names(complete_yaml) %in% names(all_groups_list)]

  if (length(all_modified) != 0) {
    cli::cli_alert_info(
      paste0(
        "Some files group already existed and were overwritten: ",
        paste(all_modified, collapse = ", ")
      )
    )
    complete_yaml[all_modified] <- NULL
  }

  # Combine with complete_yaml
  complete_yaml <- c(complete_yaml, all_groups_list)
  complete_yaml <- complete_yaml[sort(names(complete_yaml))]

  # Get duplicated paths after update
  yaml_paths <- unlist(complete_yaml)
  # Except info on state
  yaml_paths <- yaml_paths[!grepl("[.]state$", names(yaml_paths))]
  yaml_paths <- yaml_paths[!grepl("inflate\\.", names(yaml_paths))]

  if (any(duplicated(yaml_paths))) {
    which_file <- files_list_to_vector(
      lapply(complete_yaml, files_list_to_vector)
    )

    if (isTRUE(force)) {
      cli::cli_alert_warning("Some paths appear multiple times in the config file. The yaml was forced with `force = TRUE`. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"))
    } else {
      stop("Some paths would appear multiple times in the future config file. The yaml has not been created. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"), "\nOr use `force = TRUE`")
    }
  }

  yaml::write_yaml(complete_yaml, file = config_file)

  return(config_file)
}

#' Extract name of file along with type to inform the user
#' @param list_of_files A named list of files
#' @noRd
files_list_to_vector <- function(list_of_files) {
  lapply(seq_along(list_of_files), function(x) {
    if (length(list_of_files[[x]]) != 0) {
      paste(names(list_of_files[x]), list_of_files[[x]], sep = ": ")
    }
  }) %>% unlist()
}

#' Update one group in the complete yaml as list
#' @param complete_yaml The list as output of config_yaml file
#' @param flat_file_path The group to update
#' @param state Character. "active" or "deprecated"
#' @param clean Logical. See `df_to_config()`. Delete list associated a specific flat file before updating the whole list. Default is set to TRUE during `inflate()` of a specific flat fil, as the list should only contain files created during the inflate. This parameter is set to FALSE with `register_to_config()` so that it can be run twice on the package when migrating from an old version of {fusen}. This could be set to FALSE with a direct use of `df_to_config()` too.
#' @param inflate_parameters list of parameters passed to the `inflate()` call
#' @noRd
update_one_group_yaml <- function(df_files,
                                  complete_yaml,
                                  flat_file_path,
                                  state = c("active", "deprecated"),
                                  clean = TRUE,
                                  inflate_parameters = NULL) {
  state <- match.arg(state, several.ok = FALSE)
  all_keep_before <- complete_yaml[[basename(flat_file_path)]]

  # Only files from df_files will be listed
  df_files_filtered <- df_files[df_files[["origin"]] == flat_file_path, ]

  # All already in the list will be deleted except if clean is FALSE
  if (isTRUE(clean)) {
    this_group_list <- list(
      path = flat_file_path,
      state = state,
      R = c(df_files_filtered[["path"]][
        grepl("^R$|^r$", df_files_filtered[["type"]])
      ]),
      tests = c(df_files_filtered[["path"]][
        grepl("^test$|^tests$", df_files_filtered[["type"]])
      ]),
      vignettes = c(df_files_filtered[["path"]][
        grepl("^vignette$|^vignettes$", df_files_filtered[["type"]])
      ])
    )
  } else {
    this_group_list <- list(
      path = flat_file_path,
      state = state,
      R = c(
        # new ones
        df_files_filtered[["path"]][
          grepl("^R$|^r$", df_files_filtered[["type"]])
        ],
        # previous ones
        unlist(all_keep_before[["R"]])
      ),
      tests = c(
        # new ones
        df_files_filtered[["path"]][
          grepl("^test$|^tests$", df_files_filtered[["type"]])
        ],
        # previous ones
        unlist(all_keep_before[["tests"]])
      ),
      vignettes = c(
        # new ones
        df_files_filtered[["path"]][grepl("^vignette$|^vignettes$", df_files_filtered[["type"]])],
        # previous ones
        unlist(all_keep_before[["vignettes"]])
      )
    )
  }

  if (!is.null(inflate_parameters)) this_group_list <- c(this_group_list, list(inflate = inflate_parameters))

  # Those removed
  those_removed <- setdiff(
    all_keep_before,
    this_group_list
  )
  those_removed_vec <- files_list_to_vector(those_removed)
  those_added <- setdiff(
    this_group_list,
    all_keep_before
  )
  those_added_vec <- files_list_to_vector(those_added)

  if (!is.null(those_removed_vec) || length(those_removed_vec) != 0) {
    silent <- lapply(paste(those_removed_vec, "was removed from the config file"), cli::cli_alert_warning)
  }
  if (!is.null(those_added_vec) || length(those_added_vec) != 0) {
    silent <- lapply(paste(those_added_vec, "was added to the config file"), cli::cli_alert_success)
  }

  return(this_group_list)
}
```

```{r examples-df_to_config, eval=FALSE}
# Add your own list of files to "keep",
# if they are not in a flat file.
# Otherwise, they may be deleted with your next `inflate()`
my_files_to_protect <- tibble::tribble(
  ~type, ~path,
  "R", "R/zaza.R",
  "R", "R/zozo.R",
  "test", "tests/testthat/test-zaza.R",
  "vignette", "vignettes/my-zaza-vignette.Rmd"
)

#' \dontrun{
df_to_config(my_files_to_protect)
#' }

# Provide a list of `inflate()` parameters if you wish them
# to be added in the dev/config_fusen.yaml file

#' \dontrun{
my_files_to_protect <- structure(
  list(
    type = c("R", "test", "vignette"),
    path = c(
      file.path(dummypackage, "R", "my_fun.R"),
      file.path(dummypackage, "tests/testthat", "test-my_fun.R"),
      "vignettes/minimal.Rmd"
    )
  ),
  row.names = c(NA, -3L),
  class = c("tbl_df", "tbl", "data.frame")
)

relative_flat_file <- "dev/flat_minimal.Rmd"

config_file <- df_to_config(
  df_files = my_files_to_protect,
  flat_file_path = relative_flat_file,
  clean = TRUE,
  state = "active",
  force = TRUE,
  inflate_parameters = list(
    flat_file = "dev/flat_minimal.Rmd",
    vignette_name = "My new vignette",
    open_vignette = FALSE,
    check = FALSE,
    document = TRUE,
    overwrite = "yes"
  )
)
#' }
```

```{r tests-df_to_config}
# Test df_to_config with custom config file path ----
config_file_path <- tempfile(fileext = ".yaml")

test_that("df_to_config fails when appropriate", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    all_files <- tibble::tribble(
      ~type, ~files,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files, flat_file_path = "keep"),
      "df_files should contains two columns named: 'type' and 'path'"
    )

    all_files <- tibble::tribble(
      ~type, ~path,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files),
      "Some 'path' in df_files do not exist: row 1- R: zaza.R, row 2- R: zozo.R, row 3- test: test-zaza.R"
    )
  })
})


# Create files, even empty
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R", "toto.Rmd")))

test_that("df_to_config works", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      # Use full path

      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R"
      )

      expect_message(config_file_out <- df_to_config(all_files))
    })

    expect_equal(config_file_out, config_file_path)
    all_keep <- yaml::read_yaml(config_file_out)
    expect_equal(names(all_keep), "keep")
    expect_equal(names(all_keep$keep), c("path", "state", "R", "tests", "vignettes"))
    expect_equal(all_keep$keep$path, c("keep"))
    expect_equal(all_keep$keep$state, c("active"))
    expect_equal(all_keep$keep$R, c("zaza.R", "zozo.R"))
    expect_equal(all_keep$keep$tests, c("test-zaza.R"))
    expect_equal(all_keep$keep$vignettes, list())
  })
})

# Second pass
all_files <- tibble::tribble(
  ~type, ~path,
  "r", "tata.R",
  "R", "toto.R",
  "tests", "test-tata.R",
  "vignettes", "tata_vignette.Rmd"
)

file.create(file.path(dir_tmp, c("tata.R", "toto.R", "test-tata.R", "tata_vignette.Rmd")))

test_that("df_to_config works after 2nd run", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      expect_message(
        config_file <- df_to_config(all_files),
        regexp = "Some files group already existed and were overwritten: keep"
      ) # "keep" is default
    })
  })
})

unlink(dir_tmp, recursive = TRUE)
file.remove(config_file_path)

# Create files, even empty ----
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R")))
dir.create(file.path(dir_tmp, "vignettes"))
file.create(file.path(dir_tmp, "vignettes", "my-vignette.Rmd"))

test_that("df_to_config works with files having no content", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    withr::with_dir(dir_tmp, {
      # Use relative path
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R",
        "vignette", file.path("vignettes", "my-vignette.Rmd")
      )

      expect_message(config_file_out <- df_to_config(all_files))
    })

    expect_equal(config_file_out, config_file_path)
    all_keep <- yaml::read_yaml(config_file_out)
    expect_equal(names(all_keep), "keep")
    expect_equal(names(all_keep$keep), c("path", "state", "R", "tests", "vignettes"))
    expect_equal(all_keep$keep$path, c("keep"))
    expect_equal(all_keep$keep$state, c("active"))
    # Relative path
    expect_equal(all_keep$keep$R, c("zaza.R", "zozo.R"))
    expect_equal(all_keep$keep$tests, c("test-zaza.R"))
    expect_equal(all_keep$keep$vignettes, c("vignettes/my-vignette.Rmd"))
  })
})

# Remove one file to see if it is detected ----
file.remove(file.path(dir_tmp, c("zaza.R")))
test_that("df_to_config works with files having no content", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    withr::with_dir(dir_tmp, {
      # Use relative path
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R",
        "vignette", file.path("vignettes", "my-vignette.Rmd")
      )

      expect_error(config_file_out <- df_to_config(all_files),
        regexp = "zaza.R"
      )
    })
  })
})

unlink(dir_tmp, recursive = TRUE)
file.remove(config_file_path)

# Test df_to_config with inflate parameters and flat_file_path = "keep"
config_file_path <- tempfile(fileext = ".yaml")
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R")))

test_that("df_to_config does not work with inflate_parameters and flat_file_path = \"keep\"", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R"
      )

      expect_error(
        df_to_config(all_files,
          inflate_parameters = list(
            flat_file = "dev/my_flat.Rmd",
            vignette_name = "My new vignette",
            open_vignette = FALSE,
            check = FALSE,
            document = TRUE,
            overwrite = "yes"
          )
        )
      )
    })
  })
})

unlink(dir_tmp, recursive = TRUE)

# df to config with inflate_parameters
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("dftoconfig")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- (add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE))
# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

dir.create(file.path(dummypackage, "R"))
file.create(file.path(dummypackage, "R", "my_fun.R"))

dir.create(file.path(dummypackage, "tests"))
dir.create(file.path(dummypackage, "tests/testthat"))
file.create(file.path(dummypackage, "tests/testthat", "test-my_fun.R"))

dir.create(file.path(dummypackage, "vignettes"))
file.create(file.path(dummypackage, "vignettes", "minimal.Rmd"))

test_that("df_to_config works with inflate parameters", {
  usethis::with_project(dummypackage, {
    all_files <- structure(list(
      type = c("R", "test", "vignette"),
      path = c(
        file.path(dummypackage, "R", "my_fun.R"),
        file.path(dummypackage, "tests/testthat", "test-my_fun.R"),
        "vignettes/minimal.Rmd"
      )
    ), row.names = c(NA, -3L), class = c("tbl_df", "tbl", "data.frame"))

    relative_flat_file <- "dev/flat_minimal.Rmd"

    config_file <- df_to_config(
      df_files = all_files,
      flat_file_path = relative_flat_file,
      clean = TRUE,
      state = "active",
      force = TRUE,
      inflate_parameters = list(
        flat_file = "dev/flat_minimal.Rmd",
        vignette_name = "My new vignette",
        open_vignette = FALSE,
        check = FALSE,
        document = TRUE,
        overwrite = "yes"
      )
    )

    config_file_content <- yaml::read_yaml(config_file)

    expect_equal(
      config_file_content[[basename(flat_file)]][["inflate"]],
      list(
        flat_file = "dev/flat_minimal.Rmd",
        vignette_name = "My new vignette",
        open_vignette = FALSE,
        check = FALSE,
        document = TRUE,
        overwrite = "yes"
      )
    )
  })
})
unlink(dummypackage, recursive = TRUE)

# Verify df_to_config was run during ìnflate()
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate parameters are put into config_fusen.yaml", {
  # Inflate once
  usethis::with_project(dummypackage, {
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE,
        extra_param = "toto"
      )
    )

    config_yml <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["vignette_name"]],
      "Get started"
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["check"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["open_vignette"]]
    )

    expect_true(
      config_yml[[basename(flat_file)]][["inflate"]][["document"]]
    )

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["overwrite"]],
      "ask"
    )


    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["extra_param"]],
      "toto"
    )

    # Let's inflate a second time with different parameters

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started again", check = FALSE,
        open_vignette = FALSE, overwrite = "yes",
        extra_param = "tutu", document = FALSE
      )
    )

    config_yml <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["vignette_name"]],
      "Get started again"
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["check"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["open_vignette"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["document"]]
    )

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["overwrite"]],
      "yes"
    )


    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["extra_param"]],
      "tutu"
    )
  })
})

unlink(dummypackage, recursive = TRUE)
# rstudioapi::navigateToFile(config_file)
```

## List files that are not registered in config

{fusen} now registers all files created during `inflate()`. 
This allows to clean the packages directories in case some functions do not exist anymore and were renamed.  
However, this also requires to register all existing files if you started your package without {fusen} or with an earlier version of {fusen}.  
`check_not_registered_files()` shows files that are not already registered in the yaml config file. The output is consistent with what is needed for `df_to_config()` to register them if wanted.  
Note that `check_not_registered_files()` will try to guess the source flat template, if you used {fusen} >= 0.4 before.

```{r function-check_not_registered_files, filename="clean_fusen_files"}
#' Show in a table files that are not already registered in the yaml config file
#'
#' If user start their package without 'fusen' or with version < 0.4, they need to create the config file, with already existing functions.
#'
#' @param path Path to package to check for not registered files
#' @param guess Logical. Guess if the file was inflated by a specific flat file
#' @param to_csv Logical. Whether to store along the config file, the outputs in a csv for the user to clean it manually
#' @return Path to csv file if `to_csv` is TRUE. `dput()` of the dataframe otherwise.
#' @importFrom utils write.csv
#'
#' @export
check_not_registered_files <- function(path = ".", guess = TRUE, to_csv = TRUE) {
  path <- normalizePath(path, winslash = "/")

  all_r <- list.files(file.path(path, "R"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_test <- list.files(file.path(path, "tests", "testthat"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_vignette <- list.files(file.path(path, "vignettes"), pattern = "[.]Rmd$|[.]rmd$", full.names = TRUE)

  res <- data.frame(
    type = c(
      rep("R", length(all_r)),
      rep("test", length(all_test)),
      rep("vignette", length(all_vignette))
    ),
    path = c(
      all_r, all_test, all_vignette
    ),
    stringsAsFactors = FALSE
  )

  if (nrow(res) == 0) {
    message("There are no files in the package. Did you inflate it once?")
    return(NULL)
  }

  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (file.exists(config_file)) {
    # Read config file, and remove those already there
    config_list <- yaml::read_yaml(config_file)
    config_list_path <- normalizePath(get_list_paths(config_list), mustWork = FALSE, winslash = "/")
    res_existing <- res[res$path %in% config_list_path, ]
    res_new <- res[!res$path %in% config_list_path, ]
  } else {
    res_existing <- res[FALSE, ]
    res_new <- res
  }

  if (nrow(res_new) == 0) {
    cli::cli_alert_info("There are no unregistered files")
    return(NULL)
  }

  # Guess those not in config_file
  # All files without path, are changed for "keep"
  if (isTRUE(guess)) {
    # List all files
    res_new$origin <- unlist(lapply(res_new$path, guess_flat_origin))
  } else {
    res_new$origin <- "keep"
  }

  # TODO go back to relative path
  res_new$path <- gsub(paste0(getwd(), "/"), "", normalize_path_winslash(res_new$path, mustWork = TRUE))

  # config_file may not exist already
  csv_file <- file.path(
    gsub(paste0(getwd(), "/"), "", dirname(normalize_path_winslash(config_file, mustWork = FALSE))), "config_not_registered.csv"
  )

  # Save for manual modification
  if (isTRUE(to_csv)) {
    write.csv(res_new, csv_file, row.names = FALSE)
    cli::cli_alert_info(paste(
      "Wrote not registered files in: ", csv_file,
      "\nKeep only those necessary and run `df_to_config()` on the csv file."
    ))

    return(csv_file)
  } else {
    # return a `dput()` to allow to add to `df_to_config()`
    # dput()
    return(dput(res_new))
  }
}

#' Guess flat file of origin of a script
#'
#' @param path Path of the script to test
#' @noRd
guess_flat_origin <- function(path) {
  lines <- readLines(path)

  guess_path <- sub(
    ".* from\\s*(/){0,1}(.+[.].{1}md).*", "\\2",
    lines[grep("(G|g)enerated by \\{fusen\\} from", lines)][1]
  )

  guess_path <- normalizePath(guess_path, mustWork = FALSE, winslash = "/")
  if (file.exists(guess_path)) {
    guess_path <- gsub(paste0(getwd(), "/"), "", normalizePath(guess_path, mustWork = FALSE, winslash = "/"))
    return(guess_path)
  } else {
    return("No existing source path found. Write 'keep', the full path to the flat file source, or delete this line.")
  }
}

#' Get all paths from a config list, except some
#' @param config_list List as read from config.yaml file
#' @noRd
get_list_paths <- function(config_list) {
  unlist(lapply(config_list, function(x) {
    if (x$path == "keep") x$path <- NULL
    x$state <- NULL
    x
  }))
}
```

```{r example-check_not_registered_files, eval=FALSE}
#' \dontrun{
# Run this on the current package in development
out_csv <- check_not_registered_files()
out_csv
#' }
```

<!-- Use eval=FALSE because inflate cannot work inside a Rmd vignette -->

```{r example2-check_not_registered_files, eval=FALSE}
# Or you can try on the reproducible example
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage, {
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  # Add a not registered file to the package
  cat("# test R file", file = file.path(dummypackage, "R", "to_keep.R"))

  # Use the fonction to check the list of files
  out_csv <- check_not_registered_files(dummypackage)
  out_csv
  # Open the csv to modify manually the list of files in the csv created
  # Indeed, the "to_keep.R" file will be registered as
  # "No existing source path found."
  # Manually change this line with "keep"
  content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
  # Here I change the line to simulate what you manually did above
  content_csv[content_csv[["path"]] == "R/to_keep.R", "origin"] <- "keep"
  write.csv(content_csv, out_csv)
  out_config <- df_to_config(
    df_files = out_csv
  )
  out_config
  # Open the out_config file to see what's going on
  yaml::read_yaml(out_config)
})
unlink(dummypackage, recursive = TRUE)
```


```{r tests-check_not_registered_files}
dummypackage <- tempfile("registered")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {
  test_that("check_not_registered_files returns message if empty", {
    expect_true(inherits(check_not_registered_files, "function"))

    # debugonce(check_not_registered_files)
    expect_message(check_not_registered_files(), "There are no files in the package")
  })

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  test_that("guess_flat_origin works", {
    guessed_path <- guess_flat_origin(file.path(dummypackage, "R", "my_median.R"))
    # Relative path
    expect_equal(guessed_path, file.path("dev", "flat_full.Rmd"))

    guessed_path <- guess_flat_origin(file.path(dummypackage, "dev", "0-dev_history.Rmd"))
    expect_true(grepl("No existing source path found", guessed_path))
  })

  test_that("check_not_registered_files works", {
    # All files were registered during inflate
    expect_true(file.exists(file.path(dummypackage, "dev", "config_fusen.yaml")))
    expect_message(out_csv <- check_not_registered_files(),
      regexp = "There are no unregistered files"
    )

    # Delete config file to check if al sub-functions work
    file.remove(file.path(dummypackage, "dev", "config_fusen.yaml"))
    expect_message(out_csv <- check_not_registered_files(),
      regexp = "Wrote not registered files in:  dev/config_not_registered.csv"
    )

    content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
    expect_true(all(names(content_csv) %in% c("type", "path", "origin")))
    expect_equal(content_csv[["type"]], c("R", "R", "test", "test", "vignette"))
    # Relative path
    expect_equal(
      content_csv[["path"]],
      c(
        "R/my_median.R",
        "R/my_other_median.R",
        "tests/testthat/test-my_median.R",
        "tests/testthat/test-my_other_median.R",
        "vignettes/get-started.Rmd"
      )
    )
  })

  test_that("guess_flat_origin output works with df_to_config", {
    out_csv <- "dev/config_not_registered.csv"
    # Include it in df_to_config()

    out_config <- df_to_config(
      df_files = out_csv
    )
    out_config_content <- yaml::read_yaml(out_config)
    expect_true(names(out_config_content) == "flat_full.Rmd")
    expect_equal(
      names(out_config_content[["flat_full.Rmd"]]),
      c("path", "state", "R", "tests", "vignettes")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["R"]],
      c("R/my_median.R", "R/my_other_median.R")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["tests"]],
      c("tests/testthat/test-my_median.R", "tests/testthat/test-my_other_median.R")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["vignettes"]],
      c("vignettes/get-started.Rmd")
    )

    # rstudioapi::navigateToFile(out_config)
  })

  # Test add a R file manually and include in "keep" after `check_not_registered_files()`
  cat("# test R file", file = file.path(dummypackage, "R", "to_keep.R"))

  test_that("check_not_registered_files can help manually fill config", {
    expect_message(out_csv <- check_not_registered_files(), "Wrote not registered files")
    content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
    expect_true(
      grepl(
        "No existing source path found",
        content_csv[grepl("to_keep.R", content_csv[, "path"]), "origin"]
      )
    )

    # Add in the yaml file with `df_to_config()`
    keep_to_add_to_config <- content_csv[grepl("to_keep.R", content_csv[, "path"]), ]
    keep_to_add_to_config$origin <- "keep"

    out_config <- df_to_config(keep_to_add_to_config)
    # rstudioapi::navigateToFile(out_config)
    out_config_content <- yaml::read_yaml(out_config)
    expect_equal(out_config_content$keep$R, "R/to_keep.R")

    expect_message(
      out_csv <- check_not_registered_files(),
      "There are no unregistered files"
    )
    expect_true(is.null(out_csv))

    # Add same file in the yaml file with `df_to_config()` using different origin (existing one, but duplicate R file) ----

    keep_to_add_to_config$origin <- "dev/flat_full.Rmd"

    expect_error(
      df_to_config(keep_to_add_to_config),
      "Some paths would appear multiple times in the future config file."
    )

    # Add same file in the yaml file with `df_to_config()` using different origin (not existing) ----

    keep_to_add_to_config$origin <- "dev/flat_dont_exists.Rmd"

    expect_error(
      df_to_config(keep_to_add_to_config),
      "Some 'origin' in df_files do not exist: row 1: dev/flat_dont_exists.Rmd"
    )
  })
})
```

# clean_fusen_files

TODO

```{r function-clean_fusen_files, filename="clean_fusen_files"}
#' Title
#'
#' Description
#'
#' @return Used for side effect. Delete unregistered files.
#'
#' @export
clean_fusen_files <- function() {
  message("This does nothing for now")
}
```


```{r example-clean_fusen_files}
clean_fusen_files()
```


```{r tests-clean_fusen_files}
# Test full ----
# Change options(fusen.config_file = "dev/config_fusen.yaml")
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

# Detect all files created ----
usethis::with_project(dummypackage, {
  # Create empty config file

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  # debugonce(inflate)
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_clean_fusen_files.Rmd", vignette_name = "Clean fusen files", check = FALSE, overwrite = TRUE, open_vignette = FALSE)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```
