---
title: "flat_inflate_all.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r development, include=FALSE}
library(testthat)
library(yaml)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

The `inflate_all()` function allows the user to inflate all the flat files present in the `dev/` folder at once.

Prior to be able to inflate all the flat files, some checks are performed, to assess whether the flat files are available to be used by `inflate_all()`.

Please note that `inflate_all()` requires the existence of a `config_fusen.yml` file. This file is not existing in versions of {fusen} prior to v0.5.0.9000.

If you are working in a project initiated with a version of {fusen} prior to v0.5.0.9000, please run `inflate()` for each of the flat files you want to work with in order to create the appropriated `config_fusen.yml` file.

If you are already familiar to `config_fusen.yml` but were working with a dev version of {fusen} prior to v0.5.0.9001, your `config_fusen.yml` file does not contain inflate-related parameters. You will have to inflate again you flat files in order to complete `config_fusen.yml` with the `inflate()` parameters.

# inflate_all
    
```{r function-inflate_all}
#' Inflate all your flat files
#'
#' Inflate all the flat files stored in dev/ and starting with "flat_"
#'
#' @param pkg Path to package
#' @inheritParams inflate
#'
#' @importFrom yaml read_yaml
#' @importFrom cli cat_rule
#' @importFrom rcmdcheck rcmdcheck
#'
#' @return side effect. Inflates all your flat files that can be inflated.
#'
#' @export
inflate_all <- function(pkg = ".", document = TRUE, check = TRUE, overwrite = TRUE, ...) {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (!file.exists(config_file)) {
    stop("There is no fusen.config_file in your package. Your flat files must be inflated at least once manually before you can use `inflate_all()`. If you were using a fusen prior to v0.5.0.9000 you must inflate all your flat files manually once again.")
  }

  config_yml <- read_yaml(config_file)

  diag <- pre_inflate_all_diagnosis(config_yml = config_yml, pkg = pkg)
  # Run stop first only
  pre_inflate_all_diagnosis_eval(diag, type_stop = TRUE)
  # If message or warnings about flat files, show at the end of the process
  # => Is going to be
  pre_inflate_all_diagnosis_eval(diag, type_stop = FALSE)

  inflate_params <- read_inflate_params(config_yml = config_yml)

  if (length(inflate_params) == 0) {
    message("No flat files were inflated")
  } else {
    apply_inflate <- function(inflate_params, overwrite) {
      config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")
      # Change config option temporary, to be able to modify it on the fly
      config_file_tmp <- tempfile(pattern = "tempconfig")
      on.exit(file.remove(config_file_tmp))
      file.copy(config_file, to = config_file_tmp)
      options("fusen.config_file" = config_file_tmp)
      on.exit(options("fusen.config_file" = config_file))

      invisible(
        lapply(inflate_params, function(flat_file) {
          flat_file$pkg <- pkg
          flat_file$overwrite <- overwrite
          flat_file$document <- FALSE
          flat_file$check <- FALSE
          suppressMessages(do.call(inflate, flat_file))
        })
      )
    }

    apply_inflate(inflate_params, overwrite)

    # Attachment + check like in inflate()
    # Run attachment
    if (isTRUE(document)) {
      attachment::att_amend_desc(path = pkg)
    }

    # Check
    if (isTRUE(check)) {
      cat_rule("Launching check()")
      res <- rcmdcheck(
        path = pkg,
        ...
      )
    }
  }
  pkg
}

#' @rdname inflate_all
#' @export
inflate_all_no_check <- function(pkg = ".", document = TRUE, overwrite = TRUE, ...) {
  inflate_all(pkg = pkg, document = document, check = FALSE, overwrite = overwrite, ...)
}
```
  
```{r example-inflate_all, eval=FALSE}
#' \dontrun{
# Usually, in the current package run inflate_all() directly
# This function has an impact on the current user workspace
inflate_all()
#' }

# You can also inflate_all flats of another package as follows
# A dummy package with a flat file
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
flat_files <- add_minimal(
  pkg = dummypackage,
  overwrite = TRUE,
  open = FALSE
)
flat_file <- flat_files[grep("flat", basename(flat_files))]
# Inflate the flat file once
usethis::with_project(dummypackage, {
  # if you are starting from a brand new package, inflate_all() will crash
  # it's because of the absence of a fusen config file
  # inflate_all()

  # Add licence
  usethis::use_mit_license("John Doe")

  # you need to inflate manually your flat file first
  inflate(
    pkg = dummypackage,
    flat_file = flat_file,
    vignette_name = "Get started",
    check = FALSE,
    open_vignette = FALSE,
    document = TRUE,
    overwrite = "yes"
  )

  # your config file has been created
  config_yml_ref <-
    yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))
})

# Next time, you can run inflate_all() directly
usethis::with_project(dummypackage, {
  # now you can run inflate_all()
  inflate_all(check = TRUE, document = TRUE)
})

# Clean the temporary directory
unlink(dummypackage, recursive = TRUE)
```
  
```{r tests-inflate_all}
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE)

# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all is a function", {
  expect_true(inherits(inflate_all, "function"))
})

usethis::with_project(dummypackage, {
  # Add licence
  usethis::use_mit_license("John Doe")

  test_that("error if no config file exists", {
    # if no config file exists, we raise an error
    expect_error(inflate_all(), regexp = "There is no fusen[.]config_file in your package[.]")
  })

  # we inflate the flat file
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE, document = TRUE,
      overwrite = "yes"
    )
  )
  config_yml_ref <- yaml::read_yaml(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))

  test_that("inflate_all says which is going to be inflated", {
    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is going to be inflated")
    )
  })

  test_that("deprecated is detected and not inflated", {
    # Let's deprecate our flat file
    config_yml_deprecated <- config_yml_ref
    config_yml_deprecated[[1]][["state"]] <- "deprecated"
    config_yml_deprecated[[1]][["R"]] <- ""
    yaml::write_yaml(config_yml_deprecated, file = "dev/config_fusen.yaml")

    # And remove R file to verify it is not rebuilt
    fun_file <- file.path("R", "my_fun.R")
    expect_true(file.exists(fun_file))
    file.remove(fun_file)

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file {basename(flat_file)} is not going to be inflated because it is 'inactive or deprecated'")
    )

    expect_false(file.exists(fun_file))
  })

  test_that("new flat file, absent from config_fusen.yml works", {
    # Let's add a new flat file, absent from config_fusen.yml
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)

    expect_message(inflate_all(),
      regexp = glue::glue("The flat file flat_minimal_2.Rmd is not going to be inflated because it is absent from the config file")
    )

    if (packageVersion("attachment") >= "0.4.0") {
      expect_warning(inflate_all())
    }

    unlink(flat_file2)
  })

  test_that("error when remove params", {
    # Let's remove the inflate parameters from config_fusen.yml
    config_yml_no_inflate_params <- config_yml_ref
    config_yml_no_inflate_params[[1]][["inflate"]] <- NULL
    yaml::write_yaml(config_yml_no_inflate_params, file = "dev/config_fusen.yaml")

    expect_error(inflate_all(), regexp = "The flat file flat_minimal[.]Rmd is not going to be inflated because although present in the config file, it has no inflate\\(\\) parameters")
  })

  test_that("flat file in in config_fusen.yml not present in dev", {
    # Let's add a flat file in in config_fusen.yml not present in dev/
    config_yml_file_absent_in_dev <- config_yml_ref
    config_yml_file_absent_in_dev[["missing_file.Rmd"]] <- config_yml_file_absent_in_dev[[1]]
    yaml::write_yaml(config_yml_file_absent_in_dev, file = "dev/config_fusen.yaml")

    expect_error(inflate_all(), regexp = "The file missing_file[.]Rmd is not going to be inflated because it was not found")
  })

  test_that("inflate all really inflates all", {
    # Now let's take the ability of inflate_all() to inflate all our files !
    # We start from a clean place
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )
    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_false(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_false(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_false(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))

    inflate_all()

    expect_true(file.exists(file.path(dummypackage, "R", "my_fun.R")))
    expect_true(file.exists(file.path(dummypackage, "man", "my_fun.Rd")))
    expect_true(file.exists(file.path(dummypackage, "tests/testthat", "test-my_fun.R")))
  })

  test_that("add a function in our flat file works", {
    # what happens if we add a function in our flat file
    flat_content <- readLines(flat_file)
    function_template <- readLines(system.file("inflate_all/fusen_chunk_template", package = "fusen"))

    writeLines(c(flat_content, function_template), con = flat_file)

    inflate_all()

    expect_equal(
      list.files(file.path(dummypackage, "R/")),
      c("my_fun.R", "new_fun2.R")
    )

    expect_equal(
      list.files(file.path(dummypackage, "man/")),
      c("my_fun.Rd", "new_fun2.Rd")
    )

    expect_equal(
      list.files(file.path(dummypackage, "tests/testthat")),
      c("test-my_fun.R", "test-new_fun2.R")
    )
  })

  test_that("A second flat file works", {
    # let's add a second flat
    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = "Get started_2", check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    # we delete the files created by inflate
    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))

    expect_true(length(list.files(file.path(dummypackage, "R"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "man"), full.names = TRUE)) == 0)
    expect_true(length(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE)) == 0)

    inflate_all()

    expect_true(all(
      list.files(file.path(dummypackage, "R/")) %in% c("my_fun.R", "my_fun_from_flat_file2.R", "new_fun2.R")
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "man/")) %in% c("my_fun.Rd", "my_fun_from_flat_file2.Rd", "new_fun2.Rd")
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "tests/testthat")) %in% c(
        "test-my_fun.R",
        "test-my_fun_from_flat_file2.R",
        "test-new_fun2.R"
      )
    ))

    expect_true(all(
      list.files(file.path(dummypackage, "vignettes/")) %in% c("get-started.Rmd", "get-started_2.Rmd")
    ))

    unlink(list.files(file.path(dummypackage, "R"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "man"), full.names = TRUE))
    unlink(list.files(file.path(dummypackage, "tests/testthat"), full.names = TRUE))
    unlink(flat_file2)
  })

  test_that("inflate_all deals with vignette name", {
    yaml::write_yaml(config_yml_ref, file = "dev/config_fusen.yaml")

    flat_file2 <- gsub(x = flat_file, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    file.copy(from = flat_file, to = flat_file2, overwrite = TRUE)
    # let's change the function name in the flat_file2
    flat_file2_content <- readLines(flat_file2)
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "my_fun", replacement = "my_fun_from_flat_file2")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "flat_minimal.Rmd", replacement = "flat_minimal_2.Rmd")
    flat_file2_content <- gsub(x = flat_file2_content, pattern = "Minimal", replacement = "Minimal_2")
    writeLines(text = flat_file2_content, con = flat_file2)

    # Let's check a other way to choose the vignette name
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file2,
        vignette_name = c("name" = "index"), check = FALSE,
        open_vignette = FALSE, document = TRUE,
        overwrite = "yes"
      )
    )

    unlink(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE))
    expect_true(length(list.files(file.path(dummypackage, "vignettes"), full.names = TRUE)) == 0)

    inflate_all()

    expect_true(all(list.files(file.path(
      dummypackage, "vignettes/"
    )) %in% c("get-started.Rmd", "index.Rmd")))
  })
})

unlink(dummypackage, recursive = TRUE)

# TODO
# Test inflate_all_no_check
dummypackage <- tempfile("inflateall")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_minimal(pkg = dummypackage, overwrite = TRUE, open = FALSE)

# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate_all_no_check is a function", {
  expect_true(inherits(inflate_all_no_check, "function"))
})

usethis::with_project(dummypackage, {
  # Add licence
  usethis::use_mit_license("John Doe")

  suppressMessages(
    inflate(
      pkg = dummypackage,
      flat_file = flat_file,
      vignette_name = "toto",
      check = FALSE,
      open_vignette = FALSE,
      document = TRUE,
      overwrite = "yes"
    )
  )
  # check
  utils::capture.output(inflate_all(),
    file = file.path(dummypackage, "dev/inflate_all_check.txt")
  )
  # no check
  utils::capture.output(inflate_all_no_check(),
    file = file.path(dummypackage, "dev/inflate_all_nocheck.txt")
  )

  expect_true(any(grepl(
    pattern = "R CMD check",
    x = readLines(file.path(
      dummypackage, "dev/inflate_all_check.txt"
    ))
  )))

  expect_false(any(grepl(
    pattern = "R CMD check",
    x = readLines(file.path(
      dummypackage, "dev/inflate_all_nocheck.txt"
    ))
  )))
})

unlink(dummypackage, recursive = TRUE)
```

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_inflate_all.Rmd",
  vignette_name = "Inflate all your flat files",
  check = FALSE,
  overwrite = TRUE,
  open_vignette = FALSE
)
rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```

