---
title: "addins"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-1}
# Load already included functions
pkgload::load_all(export_all = FALSE)
```

# Add fusen chunk

```{r function, filename="build_fusen_chunks"}
#' Add 'fusen' chunks
#'
#' Create 'fusen' chunks inside your Rmd
#'
#' @param function_name Name of the function to create.
#'     If NULL (the  default), the user will be prompted to enter it.
#' @param export Should the function be exported?
#'     Default is `getOption("fusen.export.functions")`. If NULL, the
#'     user will be prompted to enter it.
#'
#' @export
#'
#' @return A list with the context and the content, invisibly.
#'
#' @examples
#' \dontrun{
#' add_fusen_chunks("this", export = TRUE)
#' }
add_fusen_chunks <- function(function_name = NULL,
                             export = getOption("fusen.export.functions")) {
  if (
    requireNamespace("rstudioapi") &&
      rstudioapi::isAvailable() &&
      rstudioapi::hasFun("getSourceEditorContext") &&
      rstudioapi::hasFun("insertText")
  ) {
    # This will allow to interactively have the function name
    if (is.null(function_name)) {
      if (rstudioapi::hasFun("showPrompt")) {
        function_name <- rstudioapi::showPrompt("{fusen}", "Enter the function name")
        if (is.null(function_name)) {
          return(NULL)
        }
      } else {
        function_name <- readline("Enter the function name: ")
      }
    }

    if (is.null(export)) {
      if (rstudioapi::hasFun("showQuestion")) {
        export <- rstudioapi::showQuestion("{fusen}", "Should the function be exported?", ok = "yes", cancel = "no")
      } else {
        export <- readline("Should the function be exported? (y/n) ") == "y"
      }
    }

    curr_editor <- rstudioapi::getSourceEditorContext()
    if (!grepl("\\.Rmd$", curr_editor$path)) {
      stop("fusen chunks can only be added inside a Rmd file.")
    }

    s <- curr_editor$selection

    # What happens if the user has selected something in the Rmd?
    # Throw an error
    if (nchar(s[[1L]]$text) != 0L) {
      stop("fusen chunks can't be inserted on top of selected text.")
    }

    chunks <- build_fusen_chunks(
      function_name,
      export
    )

    rstudioapi::insertText(
      location = s[[1L]]$range$start,
      text = chunks
    )

    return(
      invisible(
        list(
          context = curr_editor,
          chunk_text = chunks
        )
      )
    )
  }
}
```

```{r tests}
# No tests for addins
```

```{r function-2, filename="build_fusen_chunks"}
#' Build fusen chunks
#'
#' Internal tool to build the chunk text
#'
#' @param function_name Name of the function to build the chunk text with
#'
#' @noRd
build_fusen_chunks <- function(function_name, export = TRUE) {
  cleaned_function_name <- clean_function_name(function_name)

  if (function_name != cleaned_function_name) {
    message(
      "Your function name was cleaned: `", function_name, "` is now `", cleaned_function_name,
      "` as a function name should only contain letters, numbers and underscores."
    )
    function_name <- cleaned_function_name
  }


  paste(
    sep = "\n",
    sprintf("# %s", function_name),
    "    ",
    sprintf("```{r function-%s}", function_name),
    "#' Title",
    "#' ",
    "#' Description",
    "#' ",
    "#' @return",
    "#' ",
    {
      if (export) {
        "#' @export"
      } else {
        "#' @noRd"
      }
    },
    sprintf("%s <- function(){", function_name),
    "    ",
    "}",
    "```",
    "  ",
    sprintf("```{r example-%s}", function_name),
    sprintf("%s()", function_name),
    "```",
    "  ",
    sprintf("```{r tests-%s}", function_name),
    sprintf("test_that(\"%s works\", {", function_name),
    sprintf("  expect_true(inherits(%s, \"function\")) ", function_name),
    "})",
    "```",
    "  "
  )
}
```

```{r example-2}
cat(build_fusen_chunks("pouet"))
```

```{r test-2}
test_that("build_fusen_chunks works properly", {
  res <- build_fusen_chunks("pouet")
  expect_true(
    grepl("^# pouet", res)
  )
  expect_true(
    grepl("function-pouet", res)
  )
  expect_true(
    grepl("example-pouet", res)
  )
  expect_true(
    grepl("function-pouet", res)
  )
  expect_true(
    grepl("tests-pouet", res)
  )
  expect_true(
    grepl("Title", res)
  )
  expect_true(
    grepl("Description", res)
  )
  expect_true(
    grepl("@return", res)
  )
  expect_true(
    grepl("@export", res)
  )
  res <- build_fusen_chunks("pouet", FALSE)
  expect_true(
    grepl("@noRd", res)
  )
})

# function names are clean ----
test_that("build_fusen_chunks cleans functions names", {
  expect_message(
    res <- build_fusen_chunks("1po @uet ()"),
    regexp = "Your function name was cleaned:"
  )
  expect_true(
    grepl("^# po_uet", res)
  )
  expect_true(
    grepl("function-po_uet}", res)
  )
  expect_true(
    grepl("example-po_uet}", res)
  )
  expect_true(
    grepl("tests-po_uet}", res)
  )
  expect_true(
    grepl("Title", res)
  )
  expect_true(
    grepl("Description", res)
  )
  expect_true(
    grepl("@return", res)
  )
  expect_true(
    grepl("@export", res)
  )
  expect_message(
    res <- build_fusen_chunks("1po @uet ()", FALSE),
    regexp = "Your function name was cleaned:"
  )
  expect_true(
    grepl("@noRd", res)
  )
})

# Create a new package, add set of chunks with export and check ----
dummydir <- tempfile(pattern = "chunk.export.")
dir.create(dummydir)
path_foosen <- file.path(dummydir, "foosen")

test_that("build_fusen_chunks add lines with export as expected", {
  withr::with_dir(dummydir, {
    dev_file <- create_fusen(path_foosen, template = "minimal", open = FALSE)
    fill_description(pkg = path_foosen, fields = list(Title = "Dummy Package"))
    path_dev_history <- dev_file[grepl("flat", dev_file)]
    dev_lines_orig <- readLines(path_dev_history)

    # If interactive in RStudio
    if (
      requireNamespace("rstudioapi") &&
        rstudioapi::isAvailable() &&
        rstudioapi::hasFun("navigateToFile") &&
        rstudioapi::hasFun("documentSave") # &&
      # rstudioapi::hasFun("documentClose")
    ) {
      print("Test with RStudio")
      # current position
      curr_editor <- rstudioapi::getSourceEditorContext()
      curr_position <- curr_editor$selection[[1L]]$range$start
      # Change file
      rstudioapi::navigateToFile(path_dev_history, line = 40)
      Sys.sleep(1)
      open_editor <- rstudioapi::getSourceEditorContext()
      id <- open_editor$id
      # the_open_path <- rstudioapi::documentPath(id)
      # if (basename(the_open_path) != basename(path_dev_history)) {
      #   stop("Open the file was short to get the correct Id of the opened file")
      # }
      # add chunks
      add_fusen_chunks(function_name = "zaza", export = TRUE)
      rstudioapi::documentSave(id)
      if (rstudioapi::hasFun("documentClose")) {
        rstudioapi::documentClose(id)
      }
      # # Back to current position
      rstudioapi::navigateToFile(curr_editor$path, line = curr_position[1])
    } else {
      print("test without interactive")
      dev_lines <- readLines(path_dev_history)
      dev_lines[40] <- build_fusen_chunks("zaza", export = TRUE)
      cat(dev_lines, sep = "\n", file = path_dev_history)
    }

    dev_lines_new <- readLines(path_dev_history)
    expect_equal(length(dev_lines_new), length(dev_lines_orig) + 24)
    expect_equal(dev_lines_new[40], "# zaza")
    expect_equal(dev_lines_new[42], "```{r function-zaza}")
    expect_equal(dev_lines_new[49], "#' @export")
    expect_equal(dev_lines_new[55], "```{r example-zaza}")
    expect_equal(dev_lines_new[56], "zaza()")
    expect_equal(dev_lines_new[59], "```{r tests-zaza}")

    unlink(path_foosen, recursive = TRUE)
  })
})

# Create a new package, add set of chunks with noRd and check ----
dummydir <- tempfile(pattern = "chunk.noRd.")
dir.create(dummydir)
path_foosen <- file.path(dummydir, "foosen")

test_that("build_fusen_chunks add lines with noRd as expected", {
  withr::with_dir(dummydir, {
    dev_file <- create_fusen(path_foosen, template = "minimal", open = FALSE)
    fill_description(pkg = path_foosen, fields = list(Title = "Dummy Package"))
    path_dev_history <- dev_file[grepl("flat", dev_file)]
    dev_lines_orig <- readLines(path_dev_history)

    # If interactive in RStudio
    if (
      requireNamespace("rstudioapi") &&
        rstudioapi::isAvailable() &&
        rstudioapi::hasFun("navigateToFile") &&
        rstudioapi::hasFun("documentSave") # &&
      # rstudioapi::hasFun("documentClose")
    ) {
      print("Test with RStudio")
      # current position
      curr_editor <- rstudioapi::getSourceEditorContext()
      curr_position <- curr_editor$selection[[1L]]$range$start
      # Change file
      rstudioapi::navigateToFile(path_dev_history, line = 40)
      Sys.sleep(1)
      open_editor <- rstudioapi::getSourceEditorContext()
      id <- open_editor$id
      # the_open_path <- rstudioapi::documentPath(id)
      # if (basename(the_open_path) != basename(path_dev_history)) {
      #   stop("Open the file was short to get the correct Id of the opened file")
      # }
      # add chunks
      add_fusen_chunks(function_name = "zaza", export = FALSE)
      rstudioapi::documentSave(id)
      if (rstudioapi::hasFun("documentClose")) {
        rstudioapi::documentClose(id)
      }
      # # Back to current position
      rstudioapi::navigateToFile(curr_editor$path, line = curr_position[1])
    } else {
      print("test without interactive")
      dev_lines <- readLines(path_dev_history)
      dev_lines[40] <- build_fusen_chunks("zaza", export = FALSE)
      cat(dev_lines, sep = "\n", file = path_dev_history)
    }

    dev_lines_new <- readLines(path_dev_history)
    expect_equal(length(dev_lines_new), length(dev_lines_orig) + 24)
    expect_equal(dev_lines_new[40], "# zaza")
    expect_equal(dev_lines_new[42], "```{r function-zaza}")
    expect_equal(dev_lines_new[49], "#' @noRd")
    expect_equal(dev_lines_new[55], "```{r example-zaza}")
    expect_equal(dev_lines_new[56], "zaza()")
    expect_equal(dev_lines_new[59], "```{r tests-zaza}")
    unlink(path_foosen, recursive = TRUE)
  })
})
```


```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(
  flat_file = "dev/flat_addins.Rmd",
  vignette_name = NA,
  check = FALSE
)
```
