---
title: "flat_init_share_on_github.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

**You write R scripts and you would like to share them with other users, in a sustainable and maintainable way. You already know how to write a notebook (Rmarkdown or Quarto) and share its HTML output, but you do not like to present the outputs along with how to use the functions in the same web page.**

If you plan on sharing your package on GitHub, `fusen::init_share_on_github()` creates all necessary files in your project and send them on your GitHub account to create the website of the package documentation. 
Then, you can focus on the content.  
Follow the steps below and you'll see your public website documentation in no time!

# Initiate your package and share it on GitHub

- Create a new project with {fusen} using git
```{r}
#| echo: false
#| eval: false
path_project <- "your/path/where/to/start/your/project/project_name"
fusen::create_fusen(path = path_project, template = "minimal", with_git = TRUE, open = TRUE)
```

- Follow the "dev/0-dev_history.Rmd" to describe your project
  + At least, you will have to fill the `fusen::fill_description()` function with your identity as below
```{r}
#| eval: false
# Describe your project
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Share Your Project Following Good Development Practices From a Rmarkdown File",
    Description = "Use Rmarkdown First method. Strengthen your work with documentation and tests. Everything can be set from a Rmarkdown file in your project.",
    `Authors@R` = c(
      person("John", "Doe", email = "john@email.me", role = c("aut", "cre"), comment = c(ORCID = "0000-0000-0000-0000"))
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("John Doe")
```

- Open the "dev/flat_full.Rmd"
  + This is the skeleton to follow if you want a properly documented and tested work
    + Write what the code is supposed to do in plain markdown
    + Separate the `function` from the `example` and `test` chunks
    + Create new sections below in your flat template with the Addin > add {fusen} chunk
- Then `inflate()` the flat template to build the proper structure of the project
    + Sections will be transferred in the correct places to get a proper package
    + A set of checks will be run to verify that your work is properly documented and tested
```{r}
#| eval: false
fusen::inflate(flat_file = "dev/flat_full.Rmd", vignette_name = "Get started")
```

- Share your work on a website using GitHub
  + You may need to run `usethis::create_github_token()`, then `gitcreds::gitcreds_set()` before, if you do not have a registered GitHub token yet.
  + You will be asked multiple times if you want to commit, you can say "yes" each time.

```{r function-init_share_on_github}
#' Initiate GitHub to share your package on a website
#'
#' This uses {pkgdown} to share the documentation of the package through GitHub Actions.
#' You may need to run `usethis::create_github_token()`, then `gitcreds::gitcreds_set()` before.
#'
#' @param ask Logical. `TRUE` (default) to ask the user to apply the instructions each time needed,
#' or `FALSE` if the user already know what to do.
#' @inheritParams usethis::use_github
#'
#' @details
#'
#' `init_share_on_github()` runs multiple steps to be able to share a proper package on GitHub:
#'
#' - Start versionning with git if not already
#' - Connect to your GitHub account
#' - Create a minimal DESCRIPTION file if missing
#'   + You will have to update its content with your information after deployment
#' - Add NEWS file to present modifications of your releases
#' - Add README.Rmd and knit it to README.md to quickly present the aim and the use of your package
#' - Init continuous integration (CI)
#'   + Check the package on Linux, Windows and MacOS
#'   + Calculate code coverage. Note that you may need to connect to <https://about.codecov.io/> to see the results of the code coverage.
#' - Init continuous deployment (CD) of the {pkgdown} website documentation
#' - Commit and push to GitHub
#' - List remaining manual steps to make the website public
#'
#' Read `vignette("share-on-a-github-website", package = "fusen")`
#'
#' @return The URL of the website created
#' @export
#'
#' @examples
init_share_on_github <- function(ask = TRUE, organisation = NULL) {
  pkg <- "."

  if (!requireNamespace("gert", quietly = TRUE)) {
    stop("Please install the {gert} package to be able to share on GitHub as you will need to use git and commit.")
  }
  if (!requireNamespace("knitr", quietly = TRUE)) {
    stop("Please install the {knitr} package to be able to share on GitHub as you will need to knit your README.")
  }

  # Init git if not already initiated
  repo <- tryCatch(gert::git_find(pkg), error = function(e) NULL)
  if (!is.null(repo)) {
    to_init <- is.na(gert::git_info(pkg)[["head"]])
  } else {
    to_init <- TRUE
  }
  if (to_init) {
    if (isTRUE(ask)) {
      sure <- paste0(
        "git is not initiated yet\n",
        "Do you want to init and commit the current state? (y/n)\n"
      )
      do_it <- readline(sure) == "y"
    } else {
      do_it <- TRUE
    }
    if (do_it) {
      cli::cat_rule("Init Git Repository with first commit")
      gert::git_init(path = pkg)
      gert::git_add(".")
      gert::git_commit_all(message = "chore: Init repository")
      if (requireNamespace("rstudioapi") && rstudioapi::isAvailable()) {
        message("After the procedure, you'll want to restart your RStudio session")
      }
    } else {
      stop("Please Init you git repository using `usethis::use_git()`")
    }
  }

  # Init GitHub connexion
  cli::cat_rule("Init GitHub Connexion")
  info_git <- gert::git_remote_list()
  if (nrow(info_git) == 0) {
    if (isTRUE(ask)) {
      sure <- paste0(
        "You may be redirected on GitHub. \nDo not forget to come back here, ok? (y/n)\n"
      )
      do_it <- readline(sure) == "y"
    } else {
      dont_do_it <- FALSE
    }
    if (do_it) {
      usethis::use_github(organisation = organisation)
    } else {
      cli::cli_text(
        cli::cli_alert_info(
          "You decided to stop the procedure. \nYour package was not send to {.url https://github.com}",
          "\nYou can run again {.fn fusen::init_share_on_github} to finish the procedure if you want."
        )
      )
      return(NULL)
    }
  } else if (grepl("github", info_git[info_git$name == "origin", "url"])) {
    message(
      "Your repository is already connected to a remote GitHub repository: ",
      info_git[info_git$name == "origin", "url"]
    )
  } else {
    stop("Your repository is not connected to a GitHub repository: ", info_git[info_git$name == "origin", "url"])
  }

  msg <- character(0)

  # Add a DESCRIPTION if not exists
  if (!file.exists("DESCRIPTION")) {
    cli::cat_rule("Add DESCRIPTION")
    fill_description(pkg = pkg)
    msg <- c(msg, "You need to fill your DESCRIPTION file. See `?fusen::fill_description`.")
  }

  # Add a NEWS if not exists
  if (!file.exists("NEWS.md")) {
    cli::cat_rule("Add NEWS")
    usethis::use_news_md()
  }

  # Add a Readme if not exists
  if (!file.exists("README.Rmd")) {
    cli::cat_rule("Add Readme")
    usethis::use_readme_rmd()
  }

  # Add GitHub Actions with pkgdown
  cli::cat_rule("Init GitHub Actions")
  usethis::use_github_action("check-standard")
  usethis::use_github_action("pkgdown")
  usethis::use_github_action("test-coverage")
  usethis::use_coverage(type = "codecov")

  # Get info for website
  github_url <- gert::git_remote_info()$url
  github_url_no_git <- gsub("[.]git$", "", github_url)
  username <- gsub("https://github.com/(.*)/.*$", "\\1", github_url_no_git)
  projname <- gsub(paste0("https://github.com/", username, "/(.*)$"), "\\1", github_url_no_git)
  url_pages <- paste0("https://", username, ".github.io/", projname)

  # Knit the Readme file
  cli::cat_rule("Update and Knit the Readme file")
  readme_lines <- readLines("README.Rmd")
  add_line <- grep("## Example", readme_lines)[1]
  readme_lines[add_line] <- paste0(
    "## Documentation\n\n",
    "Full documentation website on: ", url_pages,
    "\n\n",
    readme_lines[add_line]
  )
  cat(readme_lines, file = "README.Rmd", sep = "\n")
  knitr::knit("README.Rmd")
  msg <- c(msg, "You will want to update your README.Rmd file. And then `knit()` it.")

  # Push to the repository
  cli::cat_rule("Push to GitHub and wait for publication")
  gert::git_add(".")
  gert::git_commit_all(message = "chore: Init Actions and website")
  gert::git_push()

  # Message website
  cli::cat_rule("Make sure GitHub is set for your website publication")
  url_setting_pages <- paste0(github_url_no_git, "/settings/pages")
  url_actions <- paste0(github_url_no_git, "/actions/workflows/pkgdown.yaml")

  cli::cli_text(
    cli::cli_alert_info(
      "You need to wait for the 'pkgdown' Actions to finish",
      "\nYou know the action is finished if there is a green check box near 'chore: Init Actions and website' on this web page: {.url {url_actions}}."
    )
  )

  if (isTRUE(ask)) {
    sure <- paste0(
      "Say 'yes' when the 'chore: Init Actions and website' action is done and green? (y/n)\n"
    )
    do_it <- readline(sure) == "y"
  } else {
    do_it <- TRUE
  }
  if (isFALSE(do_it)) {
    message("Wait a little more for it to finish or try to guess the problems if it failed...")
  }

  if (isTRUE(ask)) {
    sure <- paste0(
      "You will need to follow a list of operations before you can continue development",
      "\nPlease read them carefully if you want to have access to your documentation website",
      "\nSay 'yes' to continue\n"
    )
    do_it <- readline(sure) == "y"
  }
  if (isTRUE(do_it)) {
    message("You did not write 'yes', but the to-do list will still appear!")
  }

  # usethis::ui_todo(
  # cli::cli_warn(
  cat(
    cli::cli_text("Let's go for the instructions to finish the process:"),
    cli::cli_text("\n1 - Wait for the 'pkgdown' Actions 'chore: Init Actions and website' to finish on: {.url {url_actions}}. This action will create a new branch on GitHub, named 'gh-pages'"),
    cli::cli_text("\n2 - Once the 'gh-pages' branch is created, you need to tell GitHub to follow it."),
    cli::cli_text("Go to: {.url  {url_setting_pages}} and choose 'gh-pages' in the 'Branch' drop-down menu, instead of 'None'. Click 'Save'."),
    cli::cli_text("If the branch is not there, wait a minute and refresh the page."),

    # browseURL(paste0(github_url_no_git, "/settings/pages"))
    cli::cli_text("\n3 - Wait another minute and you'll be able to see your project website at: {.url {url_pages}}"),
    cli::cli_text("Now it's time to continue your project: fill the flat file, inflate, push to GitHub."),
    cli::cli_text("\n> Infos: ", paste(msg, collapse = " \n- ")),
    {
      if (!dir.exists("R")) cli::cli_text("\n> Note: The Action 'R-CMD-check' may fail as you do not have any function in your package yet. Inflate your flat file with a function once, and it should be good.")
    },
    {
      if (!dir.exists("tests")) cli::cli_text("\n> Note: The Action 'test-coverage' may fail as you do not have any test in your package yet. Inflate your flat file with a unit test once, and it should be good.")
    },
    {
      if (isTRUE(ask)) cli::cli_text("\n\nThe next time you run this function, you can set `init_share_on_github(ask = TRUE)`, to not see all the intermediate questions.")
    }
  )

  return(url_pages)
}
```

```{r examples-init_share_on_github, eval=FALSE}
#' \dontrun{
#' # This modifies the current directory and send it on GitHub
init_share_on_github()
#' }
```

_In a few minutes, you'll be able to see and share your project website._  
You won't have to run this command line again. 
Each time you push new commits to the main branch on GitHub, your website will be updated thanks to GitHub Actions.

```{r tests-init_share_on_github}
test_that("init_share_on_github works", {
  skip_if_not(interactive())

  if (Sys.getenv("FUSEN_TEST_PUBLISH", unset = "FALSE") == "TRUE") {
    # Only create the project if specifically asked by maintainers
    path_project <- file.path(tempdir(), paste0("fusen.github.", packageVersion("fusen")))
    # path_project <- tempfile("fusen.github.proj")
    the_devs <- create_fusen(path = path_project, template = "teaching", with_git = TRUE, open = FALSE)
    the_flat <- the_devs[grep("flat", the_devs)]
    # Follow the "dev/0-dev_history.Rmd"
    usethis::with_project(path_project, {
      fill_description(
        pkg = path_project,
        fields = list(
          Title = "Share Your Project Following Good Development Practices From a Rmarkdown File",
          Description = "Use Rmarkdown First method. Strengthen your work with documentation and tests. Everything can be set from a Rmarkdown file in your project.",
          `Authors@R` = c(
            person("John", "Doe", email = "john@email.me", role = c("aut", "cre"), comment = c(ORCID = "0000-0000-0000-0000"))
          )
        )
      )
      # Define License with use_*_license()
      usethis::use_mit_license("John Doe")

      # Inflate ?
      inflate(flat_file = the_flat, vignette_name = "Get started", open_vignette = FALSE)
    })

    usethis::with_project(path_project, {
      # Share on GitHub
      website_url <- init_share_on_github()
    }) # End of with_project

    do_it <- readline("Does pkgdown website exists after following instructions? (y/n)") == "y"
    expect_true(do_it)

    # Clean state
    unlink(path_project, recursive = TRUE)
  }
})
```

# What happens behind the scene ?

`init_share_on_github()` runs multiple steps to be able to share a proper package on GitHub:

- Start versionning with git if not already
- Connect to your GitHub account
- Create a minimal DESCRIPTION file if missing
  + You will have to update its content with your information after deployment
- Add NEWS file to present modifications of your releases
- Add README.Rmd and knit it to README.md to quickly present the aim and the use of your package
- Init continuous integration (CI)
  + Check the package on Linux, Windows and MacOS
  + Calculate code coverage
- Init continuous deployment (CD) of the {pkgdown} website documentation
- Commit and push to GitHub
- List remaining manual steps to make the website public

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_init_share_on_github.Rmd", vignette_name = "Share on a GitHub website", overwrite = TRUE, check = FALSE)
```

