---
title: "flat_clean_fusen_files.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

This will help you clean your package files in case you decide to change a function name, delete a function or change a vignette name.

## {fusen} helps you clean your old functions and tests files

{fusen} inflates your flat files to script files with pre-defined names stored in the correct place, so that you do not have to think about it. If you do not change the default behavior, scripts names are created from the name of each function created.  
Until version 0.4, if you decided to change the name of your function, or a function was obsolete, you had to clean it all manually.  
This time is over with {fusen} version >0.6!  
Now, {fusen} keeps track of files created with an `inflate()`, in a yaml configuration file. It also allows you to register all extra files that you decide are legitimate. 
Hence, {fusen} will be able to clean all files that are not necessary anymore in your package.


To make this work properly, all R, test and vignettes files will need to be registered in the "dev/config_fusen.yaml" file.  
{fusen} will try to guess the source flat file of each script. This will only be possible if you used {fusen} >= 0.4 before. Otherwise, you may want to follow the detailed process below.

## Delete files not anymore linked to a flat file

TODO - clean_fusen_files

```{r function-clean_fusen_files, filename="clean_fusen_files"}
#' Title
#'
#' Description
#'
#' @return Used for side effect. Delete unregistered files.
#'
#' @export
clean_fusen_files <- function() {
  message("This does nothing for now")
}
```


```{r example-clean_fusen_files}
clean_fusen_files()
```


```{r tests-clean_fusen_files}
# Test full ----
# Change options(fusen.config_file = "dev/config_fusen.yaml")
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

# Detect all files created ----
usethis::with_project(dummypackage, {
  # Create empty config file

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  # debugonce(inflate)
})
```

## Deprecate flat files after inflate

If your practice of {fusen} is to inflate it once, and then continue development in the R, test and vignette files directly, then you may want to properly deprecated the flat file.   

<!-- In this case, we recommend to store your flat file in a sub-directory named "dev/dev_history/" as this will be the default behavior in a future release. Then, you can change your flat file to `state: deprecated` in the "dev/config_fusen.yaml". -->

<!--
We recommend to use `deprecate_flat_file()` to clean your script files (remove "do not edit"), update the config file and move the flat file in a "dev/dev_history" directory.

TODO
-->

```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_clean_fusen_files.Rmd", vignette_name = "Go further")
```

