---
title: "flat_df_to_config.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
inflate_state: active
---

```{r development, include=FALSE}
library(testthat)
```

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

## {fusen} registers all files created with a flat file

From {fusen} >=0.5, a "dev/config_fusen.yaml" file registers all files created from a specific "flat" file as soon as you inflate it.
Hence, you can keep track on where to find the source of your functions and tests.
In a future release, this will help you clean your package files in case you decide to change a function name, delete a function or change a vignette name.

<!--
To make this work properly, you will have to register all files that were not created from a flat file. `add_files_to_config()` will help you do so (See below: "Register some specific files, even with regex").  
-->

If you use this version of {fusen} in an existing project, you will want to register all existing files to avoid a too strong clean up: `register_all_to_config()` will help you do so (See below: "How to migrate from previous {fusen} versions?").


<!--
### Register some specific files, even with regex

You may not want to register each new file that does not come during an inflate process. For instance, with {golem}, there are module (`^mod_*`) files, which need to be protected. You can add this regular expression directly in the yaml file with `add_files_to_config(c("R" = "^mod_*"))` 
--> 


## How to migrate from previous {fusen} versions?

This vignette shows tools that are used internally to {fusen} to keep track of all files created during the `inflate()` process. 
They are visible to users as soon as they start using {fusen} >= 0.5, even if the package was built without {fusen}, or with an earlier version of {fusen}.  

The recommended process for a migration is:  

- Run `register_all_to_config()` in your current package to create the "dev/config_fusen.yaml" that registers all your existing files. 
 + You will note a "keep" section, which lists all files for which the source was not guessed. You can clean it up if you want.
- You're good to go with the new version of {fusen}

### You can take this opportunity to clean your repository

If you used earlier versions of {fusen}, it is possible that you have some remaining ".R" or test files. 
You may want to detect which scripts are linked to a flat file. 
If you are more familiar with ".csv" file than with the ".yaml" file above, or if you want a quick edit of multiple sources, you can run these intermediate steps:

- Run `check_not_registered_files()` on your package
- Open the "dev/config_not_registered.csv" file
  + The csv contains all existing "R/", "tests/" and "vignettes/" files
  + If you used earlier version of {fusen}, the csv may list the flat file of origin
- Clean or modify the csv file
  + Let `origin = "keep"` for files to keep, that are not coming from a flat file
- Run `df_to_config()`
- You're good to go with the new version of {fusen}

## Deprecate flat files after inflate

If your practice of {fusen} is to inflate it once, and then continue development in the R, test and vignette files directly, then you may want to properly deprecated the flat file.   

In this case, we recommend to store your flat file in a sub-directory named "dev/dev_history/" as this will be the default behavior in a future release. Then, you can change your flat file to `state: deprecated` in the "dev/config_fusen.yaml".

## The details of each function linked to config

You can continue reading if you are interesting in the functioning of these config file manipulations. Otherwise, you're good to go !

### Keep it all, I am sure of the current state

If all files of the current state are legitimate, then, you can register everything in the config file.

Run `register_all_to_config()` in your current package to create the "dev/config_fusen.yaml" that registers all your files. You will note a "keep" section, which lists all files for which the source was not guessed.

```{r function-register_all_to_config}
#' Include all existing package files in the config file
#'
#' Helps transition from non-fusen packages or made with earlier version
#'
#' @param pkg Path to the package from which to add file to configuration file
#' @inheritParams df_to_config
#' @return Path to configuration file
#' 
#' @seealso
#'   [check_not_registered_files()] for the list of files not already associated with a flat file in the config file,
#'
#' @export
register_all_to_config <- function(pkg = ".", clean = FALSE) {
  # Use the fonction to check the list of files
  out_df <- check_not_registered_files(pkg, to_csv = FALSE)

  if (is.null(out_df)) {
    message("There is no file to register or everything was already registered")
    return(getOption("fusen.config_file", default = "dev/config_fusen.yaml"))
  }

  w.keep <- grep("No existing source path found", out_df[["origin"]])
  out_df[["origin"]][w.keep] <- "keep"
  out_config <- df_to_config(df_files = out_df, clean = clean)
  # rstudioapi::navigateToFile(file.path(pkg, "dev", "config_fusen.yaml"))
  return(invisible(out_config))
}
```

```{r example-register_all_to_config-1, eval=FALSE}
#' \dontrun{
# Usually run this one inside the current project
# Note: running this will write "dev/config_fusen.yaml" in your working directory
register_all_to_config()
#' }
```

<!-- Use eval=FALSE because inflate cannot work inside a Rmd vignette -->

```{r example-register_all_to_config-2, eval=FALSE}
# Or you can try on the reproducible example
dummypackage <- tempfile("register")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage, {
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )
  out_path <- register_all_to_config(dummypackage)

  # Look at the output
  yaml::read_yaml(out_path)
})
```

```{r tests-register_all_to_config}
dummypackage <- tempfile("register")
dir.create(dummypackage)
dir.create(file.path(dummypackage, "fusentest"))
dummypackage_fixed <- file.path(dummypackage, "fusentest")
# unlink(dummypackage, recursive = TRUE)
# {fusen} steps
fill_description(pkg = dummypackage_fixed, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage_fixed, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage_fixed, {
  suppressMessages(
    inflate(
      pkg = dummypackage_fixed, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )
})
# Add a not registered file to the package
cat("# test R file\n", file = file.path(dummypackage_fixed, "R", "to_keep.R"))


test_that("register_all_to_config can be run twice", {
  expect_true(inherits(register_all_to_config, "function"))

  usethis::with_project(dummypackage_fixed, {
    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )
    expect_equal(out_path, file.path("dev", "config_fusen.yaml"))

    # What happens if everything is already registered? ----
    expect_message(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = "There is no file to register"
    )

    expect_equal(out_path, file.path("dev", "config_fusen.yaml"))

    # Add a new file to register from a new flat file ----
    add_flat_template(template = "add", flat_name = "new_one", open = FALSE)
    # Without vignette first
    suppressMessages(
      inflate(
        pkg = dummypackage_fixed,
        flat_file = "dev/flat_new_one.Rmd", vignette_name = NA,
        check = FALSE, open_vignette = FALSE
      )
    )

    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )

    # With vignette then
    suppressMessages(
      inflate(
        pkg = dummypackage_fixed,
        flat_file = "dev/flat_new_one.Rmd",
        vignette_name = "new_one",
        check = FALSE, open_vignette = FALSE
      )
    )

    expect_error(
      out_path <- register_all_to_config(dummypackage_fixed),
      regexp = NA
    )
  })

  # yaml::read_yaml(out_path)
})

test_that("config file is correctly built after half register", {
  out_actual <- yaml::read_yaml(file.path(dummypackage_fixed, "dev", "config_fusen.yaml"))
  # To update
  # file.copy(file.path(dummypackage_fixed, "dev", "config_fusen.yaml"), here::here("tests/testthat/config_fusen_register.yaml"), overwrite = TRUE)
  if (file.exists("config_fusen_register.yaml")) {
    out_expected <- yaml::read_yaml("config_fusen_register.yaml")
  } else {
    # during dev in root directory
    out_expected <- yaml::read_yaml(here::here("tests/testthat/config_fusen_register.yaml"))
  }

  expect_equal(out_actual, out_expected)
})

unlink(dummypackage, recursive = TRUE)
```


### Protect existing R, tests and vignettes files

`df_to_config()` allows to add your own list of files that you want to `keep` in your package, despite not being created with a flat file.  
This is important if you started to develop without {fusen}, and start using a flat file from now on, so that {fusen} does not delete your existing files.

```{r function-df_to_config, filename="register_config_file"}
#' Add a tibble of files and types to add to the 'fusen' config file along with inflate parameters
#'
#' @param df_files A data.frame with 'type' and 'path' columns
#' or a csv file path as issued from `[check_not_registered_files()]`
#' or nothing (and it will take the csv file in "dev/")
#' @param flat_file_path Character. Usually set to `"keep"` for users. You can use the name of the origin flat file but this is more of an internal use, as inflating the flat file should have the same result.
#' @param state Character. Whether if the flat file is `active` or `deprecated`.
#' @param force Logical. Whether to force writing the configuration file even is some files do not exist.
#' @param clean Logical. Delete list associated to a specific flat file before updating the whole list. Default is set to TRUE during `inflate()` of a specific flat file, as the list should only contain files created during the inflate. This could be set to FALSE with a direct use of `df_to_config()` too.
#' @param inflate_parameters list of parameters passed through a call to `inflate()`

#' @importFrom stats setNames
#' @importFrom utils read.csv
#' @importFrom cli cli_alert_warning cli_alert_info
#'
#' @return Config file path.
#' Side effect: create a yaml config file.
#' 
#' @seealso
#'   [check_not_registered_files()] for the list of files not already associated with a flat file in the config file,
#'   [register_all_to_config()] for automatically registering all files already present in the project
#'   
#' @export
#'
#'
df_to_config <- function(df_files,
                         flat_file_path = "keep",
                         state = c("active", "deprecated"),
                         force = FALSE,
                         clean = TRUE,
                         inflate_parameters = NULL) {
  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")
  state <- match.arg(state, several.ok = FALSE)

  # User entry verifications
  if (missing(df_files)) {
    df_files <- file.path(dirname(config_file), "config_not_registered.csv")
  }

  if (!is.data.frame(df_files) && file.exists(df_files)) {
    df_files <- read.csv(df_files, stringsAsFactors = FALSE)
  } else if (!is.data.frame(df_files) && !file.exists(df_files)) {
    stop("'", df_files, "' does not exist. You can run `check_not_registered_files()` before.")
  }

  # Then if is.data.frame(df_files)
  if (!all(c("type", "path") %in% names(df_files))) {
    stop("df_files should contains two columns named: 'type' and 'path'")
  }



  if (!"origin" %in% names(df_files)) {
    df_files[["origin"]] <- flat_file_path
  } else {
    # check origin exists
    df_files_origin <- df_files[["origin"]]
    df_files_origin <- df_files_origin[df_files_origin != "keep"]
    all_exists <- file.exists(df_files_origin)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'origin' in df_files do not exist:",
        paste(
          paste0(
            "row ", which(!all_exists), ": ",
            df_files[["origin"]][!all_exists]
          ),
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli_alert_warning(
          paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  }

  if (!all(grepl("^R$|^r$|^test$|^tests$|^vignette$|^vignettes$", df_files[["type"]]))) {
    stop("Only types 'R', 'test' or 'vignette' are allowed")
  }
  all_exists <- file.exists(df_files[["path"]])
  if (!all(all_exists)) {
    msg <- paste(
      "Some 'path' in df_files do not exist:",
      paste(
        paste0(
          "row ", which(!all_exists), "- ",
          df_files[["type"]][!all_exists], ": ",
          df_files[["path"]][!all_exists]
        ),
        collapse = ", "
      )
    )

    if (isTRUE(force)) {
      cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  if (!is.null(inflate_parameters) & flat_file_path == "keep") {
    stop("The purpose of using \"keep\" is to store files created without inflate(). Therefore it is not allowed to provide inflate_parameters")
  }

  # Remove common part between config_file and all path
  # to get relative paths to project

  # TODO - When path does not exists, normalizePath does not correctly
  # use path.expand.
  # All path should exists. It is tested above.
  if (!isTRUE(force) || isTRUE(all(file.exists(df_files$path)))) {
    df_files$path <- gsub(
      paste0(normalize_path_winslash("."), "/"),
      "",
      normalize_path_winslash(df_files$path, mustWork = TRUE),
      fixed = TRUE
    )
  }

  # All origin path should exist, if not "keep"
  if (!isTRUE(force) || isTRUE(all(file.exists(df_files$origin[df_files$origin != "keep"])))) {
    df_files$origin[df_files$origin != "keep"] <- gsub(
      paste0(normalize_path_winslash("."), "/"),
      "",
      normalize_path_winslash(df_files$origin[df_files$origin != "keep"], mustWork = TRUE),
      fixed = TRUE
    )
  } else if (isFALSE(all(file.exists(df_files$origin[df_files$origin != "keep"])))) {
    warning(
      "Please open a bug on {fusen} package with this complete message:\n",
      "There is an error in the df_to_config process.\n",
      "Files origin do not exist but will be registered as is in the config file:\n",
      paste(df_files$origin[!file.exists(df_files$origin[df_files$origin != "keep"])],
        collapse = ", "
      )
    )
  }

  if (any(duplicated(df_files$path))) {
    msg <- paste("Some paths appear multiple times in df_files. Please remove duplicated rows: ", paste(unique(df_files$path[duplicated(df_files$path)]), collapse = ", "))

    if (isTRUE(force)) {
      cli_alert_warning(
        paste(msg, "\nHowever, you forced to write it in the yaml file with `force = TRUE`.")
      )
    } else {
      stop(msg)
    }
  }

  if (file.exists(config_file)) {
    complete_yaml <- read_yaml(config_file)

    yaml_paths <- get_list_paths(complete_yaml)
    yaml_paths <- yaml_paths[!grepl("inflate\\.", names(yaml_paths))]
    all_exists <- file.exists(yaml_paths)
    if (!all(all_exists)) {
      msg <- paste(
        "Some 'path' in config_file do not exist:",
        paste(
          yaml_paths[!all_exists],
          collapse = ", "
        )
      )
      if (isTRUE(force)) {
        cli_alert_warning(
          paste(msg, "However, you forced to write it in the yaml file with `force = TRUE`.")
        )
      } else {
        stop(msg)
      }
    }
  } else {
    complete_yaml <- list()
  }

  each_flat_file_path <- unique(df_files[["origin"]])
  if (length(state) != length(each_flat_file_path)) {
    state <- rep(state, length.out = length(each_flat_file_path))
  }
  all_groups_list <- lapply(
    seq_along(each_flat_file_path),
    function(x) {
      update_one_group_yaml(
        df_files, complete_yaml,
        each_flat_file_path[x],
        state = state[x],
        clean = clean,
        inflate_parameters = inflate_parameters
      )
    }
  ) %>%
    setNames(basename(each_flat_file_path))

  all_modified <- names(complete_yaml)[names(complete_yaml) %in% names(all_groups_list)]

  if (length(all_modified) != 0) {
    cli_alert_info(
      paste0(
        "Some files group already existed and were overwritten: ",
        paste(all_modified, collapse = ", ")
      )
    )
    complete_yaml[all_modified] <- NULL
  }

  # Combine with complete_yaml
  complete_yaml <- c(complete_yaml, all_groups_list)
  # order according to name without path so that flat_2 is after flat.Rmd
  complete_yaml <- complete_yaml[order(
    sub("(?<!^|[.]|/)[.][^.]+$", "", names(complete_yaml), perl = TRUE)
  )]

  # Get duplicated paths after update
  yaml_paths <- unlist(complete_yaml)
  # Except info on state
  yaml_paths <- yaml_paths[!grepl("[.]state$", names(yaml_paths))]
  yaml_paths <- yaml_paths[!grepl("inflate\\.", names(yaml_paths))]

  if (any(duplicated(yaml_paths))) {
    which_file <- files_list_to_vector(
      lapply(complete_yaml, files_list_to_vector)
    )

    if (isTRUE(force)) {
      cli_alert_warning("Some paths appear multiple times in the config file. The yaml was forced with `force = TRUE`. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"))
    } else {
      stop("Some paths would appear multiple times in the future config file. The yaml has not been created. Please verify the source of these scripts in the existing yaml file or in the df_files provided:\n", paste(which_file[duplicated(yaml_paths)], collapse = ",\n"), "\nOr use `force = TRUE`")
    }
  }

  write_yaml_verbatim(complete_yaml, file = config_file)

  return(config_file)
}


#' Make sure yaml returns true/false as is, and not "yes/no"
#' @importFrom yaml write_yaml read_yaml
#' @noRd
write_yaml_verbatim <- function(x, file) {
  write_yaml(x,
    file = file,
    handlers = list(
      logical = function(x) {
        result <- ifelse(x, "true", "false")
        class(result) <- "verbatim"
        return(result)
      }
    )
  )
}

#' Extract name of file along with type to inform the user
#' @param list_of_files A named list of files
#' @noRd
files_list_to_vector <- function(list_of_files) {
  lapply(seq_along(list_of_files), function(x) {
    if (length(list_of_files[[x]]) != 0) {
      paste(names(list_of_files[x]), list_of_files[[x]], sep = ": ")
    }
  }) %>% unlist()
}

#' Update one group in the complete yaml as list
#' @param complete_yaml The list as output of config_yaml file
#' @param flat_file_path The group to update
#' @param state Character. See `df_to_config()`.
#' @param clean Logical. See `df_to_config()`.
#' @param inflate_parameters See `df_to_config()`.
#' @importFrom cli cli_alert_warning cli_alert_success
#' @noRd
update_one_group_yaml <- function(df_files,
                                  complete_yaml,
                                  flat_file_path,
                                  state = c("active", "deprecated"),
                                  clean = TRUE,
                                  inflate_parameters = NULL) {
  state <- match.arg(state, several.ok = FALSE)
  all_keep_before <- complete_yaml[[basename(flat_file_path)]]

  # Only files from df_files will be listed
  df_files_filtered <- df_files[df_files[["origin"]] == flat_file_path, ]

  # All already in the list will be deleted except if clean is FALSE
  if (isTRUE(clean)) {
    this_group_list <- list(
      path = flat_file_path,
      state = state,
      R = c(df_files_filtered[["path"]][
        grepl("^R$|^r$", df_files_filtered[["type"]])
      ]),
      tests = c(df_files_filtered[["path"]][
        grepl("^test$|^tests$", df_files_filtered[["type"]])
      ]),
      vignettes = c(df_files_filtered[["path"]][
        grepl("^vignette$|^vignettes$", df_files_filtered[["type"]])
      ])
    )
  } else {
    this_group_list <- list(
      path = flat_file_path,
      state = state,
      R = c(
        # new ones
        df_files_filtered[["path"]][
          grepl("^R$|^r$", df_files_filtered[["type"]])
        ],
        # previous ones
        unlist(all_keep_before[["R"]])
      ),
      tests = c(
        # new ones
        df_files_filtered[["path"]][
          grepl("^test$|^tests$", df_files_filtered[["type"]])
        ],
        # previous ones
        unlist(all_keep_before[["tests"]])
      ),
      vignettes = c(
        # new ones
        df_files_filtered[["path"]][grepl("^vignette$|^vignettes$", df_files_filtered[["type"]])],
        # previous ones
        unlist(all_keep_before[["vignettes"]])
      )
    )
  }

  if (!is.null(inflate_parameters)) this_group_list <- c(this_group_list, list(inflate = inflate_parameters))

  # Those removed
  those_removed <- setdiff(
    all_keep_before,
    this_group_list
  )
  those_removed_vec <- files_list_to_vector(those_removed)
  those_added <- setdiff(
    this_group_list,
    all_keep_before
  )
  those_added_vec <- files_list_to_vector(those_added)

  if (!is.null(those_removed_vec) || length(those_removed_vec) != 0) {
    silent <- lapply(paste(those_removed_vec, "was removed from the config file"), cli_alert_warning)
  }
  if (!is.null(those_added_vec) || length(those_added_vec) != 0) {
    silent <- lapply(paste(those_added_vec, "was added to the config file"), cli_alert_success)
  }

  return(this_group_list)
}
```

```{r examples-df_to_config, eval=FALSE}
# Add your own list of files to "keep",
# if they are not in any flat file.
# Otherwise, they may be deleted with your next `inflate()`
my_files_to_protect <- tibble::tribble(
  ~type, ~path,
  "R", "R/zaza.R",
  "R", "R/zozo.R",
  "test", "tests/testthat/test-zaza.R",
  "vignette", "vignettes/my-zaza-vignette.Rmd"
)

#' \dontrun{
# This code writes in the current user working directory
df_to_config(my_files_to_protect)
#' }

#' \dontrun{
# This code writes in the current user working directory

# Provide a list of `inflate()` parameters if you wish them
# to be added in the dev/config_fusen.yaml file
# This is usually for {fusen} internal use during `inflate()`.

# This example proposes to write all output parameters
# of a specific flat file in the config file:
# files inflated and inflate parameters
fake_flat_file <- "dev/flat_minimal.Rmd"

files_created_from_fake_flat <- structure(
  list(
    type = c("R", "test", "vignette"),
    path = c(
      "R", "my_fun.R",
      "tests/testthat", "test-my_fun.R",
      "vignettes/minimal.Rmd"
    )
  ),
  row.names = c(NA, -3L),
  class = c("tbl_df", "tbl", "data.frame")
)

# This code writes in the current user working directory
config_file <- df_to_config(
  df_files = files_created_from_fake_flat,
  flat_file_path = fake_flat_file,
  clean = TRUE,
  state = "active",
  force = TRUE,
  inflate_parameters = list(
    flat_file = fake_flat_file,
    vignette_name = "My new vignette",
    open_vignette = FALSE,
    check = FALSE,
    document = TRUE,
    overwrite = "yes"
  )
)
#' }
```

```{r tests-df_to_config}
# Test df_to_config with custom config file path ----
config_file_path <- tempfile(fileext = ".yaml")

test_that("df_to_config fails when appropriate", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    all_files <- tibble::tribble(
      ~type, ~files,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files),
      "df_files should contains two columns named: 'type' and 'path'"
    )

    all_files <- tibble::tribble(
      ~type, ~path,
      "R", "zaza.R",
      "R", "zozo.R",
      "test", "test-zaza.R"
    )

    expect_error(
      df_to_config(all_files),
      "Some 'path' in df_files do not exist: row 1- R: zaza.R, row 2- R: zozo.R, row 3- test: test-zaza.R"
    )

    expect_error(
      config_file_out <- df_to_config(all_files, force = TRUE),
      regexp = NA
    )

    expect_equal(config_file_out, config_file_path)
    all_keep <- yaml::read_yaml(config_file_out)
    expect_equal(names(all_keep), "keep")
    expect_equal(names(all_keep$keep), c("path", "state", "R", "tests", "vignettes"))
    expect_equal(all_keep$keep$path, c("keep"))
    expect_equal(all_keep$keep$state, c("active"))
    expect_equal(all_keep$keep$R, c("zaza.R", "zozo.R"))
    expect_equal(all_keep$keep$tests, c("test-zaza.R"))
    expect_equal(all_keep$keep$vignettes, list())
  })
})
file.remove(config_file_path)

# Create files, even empty
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R", "toto.Rmd")))

test_that("df_to_config works", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      # Use full path

      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R"
      )

      expect_message(config_file_out <- df_to_config(all_files))
    })

    expect_equal(config_file_out, config_file_path)
    all_keep <- yaml::read_yaml(config_file_out)
    expect_equal(names(all_keep), "keep")
    expect_equal(names(all_keep$keep), c("path", "state", "R", "tests", "vignettes"))
    expect_equal(all_keep$keep$path, c("keep"))
    expect_equal(all_keep$keep$state, c("active"))
    expect_equal(all_keep$keep$R, c("zaza.R", "zozo.R"))
    expect_equal(all_keep$keep$tests, c("test-zaza.R"))
    expect_equal(all_keep$keep$vignettes, list())
  })
})

# Second pass
all_files <- tibble::tribble(
  ~type, ~path,
  "r", "tata.R",
  "R", "toto.R",
  "tests", "test-tata.R",
  "vignettes", "tata_vignette.Rmd"
)

file.create(file.path(dir_tmp, c("tata.R", "toto.R", "test-tata.R", "tata_vignette.Rmd")))

test_that("df_to_config works after 2nd run", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      expect_message(
        config_file <- df_to_config(all_files),
        regexp = "Some files group already existed and were overwritten: keep"
      ) # "keep" is default
    })
  })
})

unlink(dir_tmp, recursive = TRUE)
file.remove(config_file_path)

# Create files, even empty ----
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R")))
dir.create(file.path(dir_tmp, "vignettes"))
file.create(file.path(dir_tmp, "vignettes", "my-vignette.Rmd"))

test_that("df_to_config works with files having no content", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    withr::with_dir(dir_tmp, {
      # Use relative path
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R",
        "vignette", file.path("vignettes", "my-vignette.Rmd")
      )

      expect_message(config_file_out <- df_to_config(all_files))
    })

    expect_equal(config_file_out, config_file_path)
    all_keep <- yaml::read_yaml(config_file_out)
    expect_equal(names(all_keep), "keep")
    expect_equal(names(all_keep$keep), c("path", "state", "R", "tests", "vignettes"))
    expect_equal(all_keep$keep$path, c("keep"))
    expect_equal(all_keep$keep$state, c("active"))
    # Relative path
    expect_equal(all_keep$keep$R, c("zaza.R", "zozo.R"))
    expect_equal(all_keep$keep$tests, c("test-zaza.R"))
    expect_equal(all_keep$keep$vignettes, c("vignettes/my-vignette.Rmd"))
  })
})

# Remove one file to see if it is detected ----
file.remove(file.path(dir_tmp, c("zaza.R")))
test_that("df_to_config works with files having no content", {
  withr::with_options(list(fusen.config_file = config_file_path), {
    withr::with_dir(dir_tmp, {
      # Use relative path
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R",
        "vignette", file.path("vignettes", "my-vignette.Rmd")
      )

      expect_error(config_file_out <- df_to_config(all_files),
        regexp = "zaza.R"
      )
    })
  })
})

unlink(dir_tmp, recursive = TRUE)
file.remove(config_file_path)

# Test df_to_config with inflate parameters and flat_file_path = "keep"
config_file_path <- tempfile(fileext = ".yaml")
dir_tmp <- tempfile()
dir.create(dir_tmp)
file.create(file.path(dir_tmp, c("zaza.R", "zozo.R", "test-zaza.R")))

test_that("df_to_config does not work with inflate_parameters and flat_file_path = \"keep\"", {
  withr::with_dir(dir_tmp, {
    withr::with_options(list(fusen.config_file = config_file_path), {
      all_files <- tibble::tribble(
        ~type, ~path,
        "R", "zaza.R",
        "R", "zozo.R",
        "test", "test-zaza.R"
      )

      expect_error(
        df_to_config(all_files,
          inflate_parameters = list(
            flat_file = "dev/my_flat.Rmd",
            vignette_name = "My new vignette",
            open_vignette = FALSE,
            check = FALSE,
            document = TRUE,
            overwrite = "yes"
          )
        )
      )
    })
  })
})

unlink(dir_tmp, recursive = TRUE)

# df to config with inflate_parameters
# unlink(dummypackage, recursive = TRUE)
dummypackage <- tempfile("dftoconfig")
dir.create(dummypackage)
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- (add_minimal_package(pkg = dummypackage, overwrite = TRUE, open = FALSE))
# let's create a flat file
flat_file <- dev_file[grepl("flat_", dev_file)]

dir.create(file.path(dummypackage, "R"))
file.create(file.path(dummypackage, "R", "my_fun.R"))

dir.create(file.path(dummypackage, "tests"))
dir.create(file.path(dummypackage, "tests/testthat"))
file.create(file.path(dummypackage, "tests/testthat", "test-my_fun.R"))

dir.create(file.path(dummypackage, "vignettes"))
file.create(file.path(dummypackage, "vignettes", "minimal.Rmd"))

test_that("df_to_config works with inflate parameters", {
  usethis::with_project(dummypackage, {
    all_files <- structure(list(
      type = c("R", "test", "vignette"),
      path = c(
        file.path(dummypackage, "R", "my_fun.R"),
        file.path(dummypackage, "tests/testthat", "test-my_fun.R"),
        "vignettes/minimal.Rmd"
      )
    ), row.names = c(NA, -3L), class = c("tbl_df", "tbl", "data.frame"))

    relative_flat_file <- "dev/flat_minimal.Rmd"

    config_file <- df_to_config(
      df_files = all_files,
      flat_file_path = relative_flat_file,
      clean = TRUE,
      state = "active",
      force = TRUE,
      inflate_parameters = list(
        flat_file = "dev/flat_minimal.Rmd",
        vignette_name = "My new vignette",
        open_vignette = FALSE,
        check = FALSE,
        document = TRUE,
        overwrite = "yes"
      )
    )

    config_file_content <- yaml::read_yaml(config_file)

    expect_equal(
      config_file_content[[basename(flat_file)]][["inflate"]],
      list(
        flat_file = "dev/flat_minimal.Rmd",
        vignette_name = "My new vignette",
        open_vignette = FALSE,
        check = FALSE,
        document = TRUE,
        overwrite = "yes"
      )
    )
  })
})
unlink(dummypackage, recursive = TRUE)

# Verify df_to_config was run during ìnflate()
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

test_that("inflate parameters are put into config_fusen.yaml", {
  # Inflate once
  usethis::with_project(dummypackage, {
    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started", check = FALSE,
        open_vignette = FALSE,
        extra_param = "toto"
      )
    )

    config_yml <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["vignette_name"]],
      "Get started"
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["check"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["open_vignette"]]
    )

    expect_true(
      config_yml[[basename(flat_file)]][["inflate"]][["document"]]
    )

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["overwrite"]],
      "ask"
    )


    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["extra_param"]],
      "toto"
    )

    # Let's inflate a second time with different parameters

    suppressMessages(
      inflate(
        pkg = dummypackage, flat_file = flat_file,
        vignette_name = "Get started again", check = FALSE,
        open_vignette = FALSE, overwrite = "yes",
        extra_param = "tutu", document = FALSE
      )
    )

    config_yml <- yaml::read_yaml(file.path(dummypackage, "dev/config_fusen.yaml"))

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["vignette_name"]],
      "Get started again"
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["check"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["open_vignette"]]
    )

    expect_false(
      config_yml[[basename(flat_file)]][["inflate"]][["document"]]
    )

    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["overwrite"]],
      "yes"
    )


    expect_equal(
      config_yml[[basename(flat_file)]][["inflate"]][["extra_param"]],
      "tutu"
    )
  })
})

unlink(dummypackage, recursive = TRUE)
# rstudioapi::navigateToFile(config_file)
```

## List files that are not registered in config

{fusen} now registers all files created during `inflate()`. 
This allows to clean the packages directories in case some functions do not exist anymore and were renamed.  
However, this also requires to register all existing files if you started your package without {fusen} or with an earlier version of {fusen}.  
`check_not_registered_files()` shows files that are not already registered in the yaml config file. The output is consistent with what is needed for the internal function `df_to_config()` to register them if wanted.  
Note that `check_not_registered_files()` will try to guess the source flat template, if you used {fusen} >= 0.4 before.

```{r function-check_not_registered_files, filename="register_config_file"}
#' Show in a table files that are not already registered in the yaml config file
#'
#' If user start their package without 'fusen' or with version < 0.4, they need to create the config file, with already existing functions.
#'
#' @param path Path to package to check for not registered files
#' @param guess Logical. Guess if the file was inflated by a specific flat file
#' @param to_csv Logical. Whether to store along the config file, the outputs in a csv for the user to clean it manually
#' @return Path to csv file if `to_csv` is TRUE. `dput()` of the dataframe otherwise.
#' @importFrom utils write.csv
#' 
#' @seealso
#'   [df_to_config()] to manually register all files detected by `check_not_registered_files()`,
#'   [register_all_to_config()] for automatically registering all files already present in the project,
#'   [inflate_all()] to inflate every flat files according to the configuration file.
#'
#' @export
check_not_registered_files <- function(path = ".", guess = TRUE, to_csv = TRUE) {
  path <- normalizePath(path, winslash = "/")

  all_r <- list.files(file.path(path, "R"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_test <- list.files(file.path(path, "tests", "testthat"), pattern = "[.]R$|[.]r$", full.names = TRUE)
  all_vignette <- list.files(file.path(path, "vignettes"), pattern = "[.]Rmd$|[.]rmd$", full.names = TRUE)

  res <- data.frame(
    type = c(
      rep("R", length(all_r)),
      rep("test", length(all_test)),
      rep("vignette", length(all_vignette))
    ),
    path = c(
      all_r, all_test, all_vignette
    ),
    stringsAsFactors = FALSE
  )

  if (nrow(res) == 0) {
    message("There are no files in the package. Did you inflate it once?")
    return(NULL)
  }

  config_file <- getOption("fusen.config_file", default = "dev/config_fusen.yaml")

  if (file.exists(config_file)) {
    # Read config file, and remove those already there
    config_list <- yaml::read_yaml(config_file)
    config_list_path <- normalizePath(get_list_paths(config_list), mustWork = FALSE, winslash = "/")
    res_existing <- res[res$path %in% config_list_path, ]
    res_new <- res[!res$path %in% config_list_path, ]
  } else {
    res_existing <- res[FALSE, ]
    res_new <- res
  }

  if (nrow(res_new) == 0) {
    cli::cli_alert_info("There are no unregistered files")
    return(NULL)
  }

  # Guess those not in config_file
  # All files without path, are changed for "keep"
  if (isTRUE(guess)) {
    # List all files
    res_new$origin <- unlist(lapply(res_new$path, guess_flat_origin))
  } else {
    res_new$origin <- "keep"
  }

  # TODO go back to relative path
  res_new$path <- gsub(paste0(getwd(), "/"), "", normalize_path_winslash(res_new$path, mustWork = TRUE))

  # config_file may not exist already
  csv_file <- file.path(
    gsub(paste0(getwd(), "/"), "", dirname(normalize_path_winslash(config_file, mustWork = FALSE))), "config_not_registered.csv"
  )

  # Save for manual modification
  if (isTRUE(to_csv)) {
    write.csv(res_new, csv_file, row.names = FALSE)
    cli::cli_alert_info(paste(
      "There are unregistered files in your package.",
      "This means that some files are not listed in the 'fusen' config file.", 
      "\n- Either they were manually created, thus not issued from an inflate.", 
      "Hence, you may want to run `register_all_to_config()`",
      "\n- Or they are issued from a previous inflate and you changed the name of the output. Hence, you will want to manually delete these files.", 
      "\n Have a look at the csv that lists them and you can decide what to do: probably a combination of manually deleting files, and then run `register_all_to_config()`.",
      "The csv file is there:", csv_file,
      "\n After the process, see if there is a 'keep' section in your 'fusen' config file that lists all files not linked to any flat file."
    ))

    return(csv_file)
  } else {
    # return a `dput()` to allow to add to `df_to_config()`
    # dput()
    # return(dput(res_new, file = nullfile()))
    return(res_new)
  }
}

#' Guess flat file of origin of a script
#'
#' @param path Path of the script to test
#' @noRd
guess_flat_origin <- function(path) {
  lines <- readLines(path)

  guess_path <- sub(
    ".* from\\s*(/){0,1}(.+[.].{1}md).*", "\\2",
    lines[grep("(G|g)enerated by \\{fusen\\} from", lines)][1]
  )

  guess_path <- normalizePath(guess_path, mustWork = FALSE, winslash = "/")
  if (file.exists(guess_path)) {
    guess_path <- gsub(paste0(getwd(), "/"), "", normalizePath(guess_path, mustWork = FALSE, winslash = "/"))
    return(guess_path)
  } else {
    return("No existing source path found. Write 'keep', the full path to the flat file source, or delete this line.")
  }
}

#' Get all paths from a config list, except some
#' @param config_list List as read from config.yaml file
#' @noRd
get_list_paths <- function(config_list) {
  unlist(lapply(config_list, function(x) {
    if (x$path == "keep") x$path <- NULL
    x$state <- NULL
    x
  }))
}
```

```{r example-check_not_registered_files, eval=FALSE}
#' \dontrun{
# Run this on the current package in development
out_csv <- check_not_registered_files()
out_csv
#' }
```

<!-- Use eval=FALSE because inflate cannot work inside a Rmd vignette -->

```{r example2-check_not_registered_files, eval=FALSE}
# Or you can try on the reproducible example
dummypackage <- tempfile("clean")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]
# Inflate once
usethis::with_project(dummypackage, {
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  # Add a not registered file to the package
  cat("# test R file\n", file = file.path(dummypackage, "R", "to_keep.R"))

  # Use the fonction to check the list of files
  out_csv <- check_not_registered_files(dummypackage)
  out_csv
  # Open the csv to modify manually the list of files in the csv created
  # Indeed, the "to_keep.R" file will be registered as
  # "No existing source path found."
  # Manually change this line with "keep"
  content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
  # Here I change the line to simulate what you manually did above
  content_csv[content_csv[["path"]] == "R/to_keep.R", "origin"] <- "keep"
  write.csv(content_csv, out_csv)
  out_config <- df_to_config(
    df_files = out_csv
  )
  out_config
  # Open the out_config file to see what's going on
  yaml::read_yaml(out_config)
})
unlink(dummypackage, recursive = TRUE)
```


```{r tests-check_not_registered_files}
dummypackage <- tempfile("registered")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- suppressMessages(add_flat_template(pkg = dummypackage, overwrite = TRUE, open = FALSE))
flat_file <- dev_file[grepl("flat_", dev_file)]

usethis::with_project(dummypackage, {

  test_that("check_not_registered_files returns message if empty", {
    expect_true(inherits(check_not_registered_files, "function"))

    # debugonce(check_not_registered_files)
    expect_message(check_not_registered_files(), "There are no files in the package")
  })

  # Inflate once
  suppressMessages(
    inflate(
      pkg = dummypackage, flat_file = flat_file,
      vignette_name = "Get started", check = FALSE,
      open_vignette = FALSE
    )
  )

  test_that("guess_flat_origin works", {
    guessed_path <- guess_flat_origin(file.path(dummypackage, "R", "my_median.R"))
    # Relative path
    expect_equal(guessed_path, file.path("dev", "flat_full.Rmd"))

    guessed_path <- guess_flat_origin(file.path(dummypackage, "dev", "0-dev_history.Rmd"))
    expect_true(grepl("No existing source path found", guessed_path))
  })

  test_that("check_not_registered_files works", {
    # All files were registered during inflate
    expect_true(file.exists(file.path(dummypackage, "dev", "config_fusen.yaml")))
    expect_message(out_csv <- check_not_registered_files(),
      regexp = "There are no unregistered files"
    )

    # Delete config file to check if al sub-functions work
    file.remove(file.path(dummypackage, "dev", "config_fusen.yaml"))
    expect_message(out_csv <- check_not_registered_files(),
      regexp = "There are unregistered files in your package"
    )

    content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
    expect_true(all(names(content_csv) %in% c("type", "path", "origin")))
    expect_equal(content_csv[["type"]], c("R", "R", "test", "test", "vignette"))
    # Relative path
    expect_equal(
      content_csv[["path"]],
      c(
        "R/my_median.R",
        "R/my_other_median.R",
        "tests/testthat/test-my_median.R",
        "tests/testthat/test-my_other_median.R",
        "vignettes/get-started.Rmd"
      )
    )
  })

  test_that("guess_flat_origin output works with df_to_config", {
    out_csv <- "dev/config_not_registered.csv"
    # Include it in df_to_config()

    out_config <- df_to_config(
      df_files = out_csv
    )
    out_config_content <- yaml::read_yaml(out_config)
    expect_true(names(out_config_content) == "flat_full.Rmd")
    expect_equal(
      names(out_config_content[["flat_full.Rmd"]]),
      c("path", "state", "R", "tests", "vignettes")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["R"]],
      c("R/my_median.R", "R/my_other_median.R")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["tests"]],
      c("tests/testthat/test-my_median.R", "tests/testthat/test-my_other_median.R")
    )
    expect_equal(
      out_config_content[["flat_full.Rmd"]][["vignettes"]],
      c("vignettes/get-started.Rmd")
    )

    # rstudioapi::navigateToFile(out_config)
  })

  # Test add a R file manually and include in "keep" after `check_not_registered_files()`
  cat("# test R file\n", file = file.path(dummypackage, "R", "to_keep.R"))

  test_that("check_not_registered_files can help manually fill config", {
    expect_message(out_csv <- check_not_registered_files(), "There are unregistered files in your package")
    content_csv <- read.csv(out_csv, stringsAsFactors = FALSE)
    expect_true(
      grepl(
        "No existing source path found",
        content_csv[grepl("to_keep.R", content_csv[, "path"]), "origin"]
      )
    )

    # Add in the yaml file with `df_to_config()`
    keep_to_add_to_config <- content_csv[grepl("to_keep.R", content_csv[, "path"]), ]
    keep_to_add_to_config$origin <- "keep"

    out_config <- df_to_config(keep_to_add_to_config)
    # rstudioapi::navigateToFile(out_config)
    out_config_content <- yaml::read_yaml(out_config)
    expect_equal(out_config_content$keep$R, "R/to_keep.R")

    expect_message(
      out_csv <- check_not_registered_files(),
      "There are no unregistered files"
    )
    expect_true(is.null(out_csv))

    # Add same file in the yaml file with `df_to_config()` using different origin (existing one, but duplicate R file) ----

    keep_to_add_to_config$origin <- "dev/flat_full.Rmd"

    expect_error(
      df_to_config(keep_to_add_to_config),
      "Some paths would appear multiple times in the future config file."
    )

    # Add same file in the yaml file with `df_to_config()` using different origin (not existing) ----

    keep_to_add_to_config$origin <- "dev/flat_dont_exists.Rmd"

    expect_error(
      df_to_config(keep_to_add_to_config),
      "Some 'origin' in df_files do not exist: row 1: dev/flat_dont_exists.Rmd"
    )
  })
})
```


```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_register_config_file.Rmd", vignette_name = "Register files in config", check = FALSE, overwrite = TRUE, open_vignette = FALSE)
# rstudioapi::navigateToFile("dev/dev_history.R", line = 105)
```
