---
title: "How to use fusen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use fusen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fusen)
```

# How to use {fusen}

- Create a new directory / new project with
  - RStudio template: File > New Project > New directory > Package using {fusen}
  - Command line: `create_fusen("path/to/new/project")`
- Open the "dev/dev_history.Rmd" template
- Run the content of the first `development` chunk with `library(testthat)` inside
- Modify and run the content of the chunk named `description`
- Follow the `"dev/dev_history.Rmd"` template to write your documentation and build your functions and test your examples.  
  - Chunk named `function` gets the code of a function
  - Chunk named `example` gets the code for examples of using the function. This will be used for function `@examples` and will be kept for the vignette
  - Chunk named `tests` gets the code for unit testing
  - Chunk named `development` gets the code for development purposes, usually only used once like {usethis} functions
- Inflate the template to transform it as a package with functions, unit tests and the current Rmd transformed as a vignette. And check.
- Build your {pkgdown} site to verify everything is at the right place

> Create multiple `"dev_history_xxx.Rmd"` files with `fusen::add_dev_history()` if needed


## Limitations

- One title / one chunk is for one function
- `examples` and `tests` chunks need to be placed after the associated `function` chunk
- You can add sub-functions in the `function` chunk to store them in the same R file, but they won't have `@examples`. Only the first function of the chunk will be able to get examples.
- As for any Rmarkdown file, chunk names need to be unique. Thus, you can use `examples-1`, `examples-2`, ...
- _Do not forget to regularly clear your Workspace to avoid functions hidden by global environment_

## Short names

- Chunk short names are possible:
  - `function` can be named `fun-` or `fun_` or `fun-my_function_name`
  - `example` can be named `ex-` or `ex_` or `ex-my_function_name`
  - `tests` can be named `test-` or `test-my_function_name`
  - `development` can be named `dev-` or `dev_` or `dev-my_function_name`

- Short "dev_history" templates names are possible thanks to fuzzy match

## Use `\dontrun{}`

You can use `\dontrun{}` in an example chunk as follows:

```{r example-dontrun, echo=TRUE, eval=FALSE}
#' \dontrun{
an_example <- 1 + 1
an_example
#' }

#' OR

#' \dontrun{
#' an_example <- 1 + 1
#' an_example
#' }
```


# Add a new dev_history.Rmd template in "dev" directory

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# Add an additional dev template
add_dev_history(pkg = dummypackage, name = "add")

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# Fill your package Description

```{r example-2}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = paste("Use Rmarkdown First method to build your package.", 
                        "Start your package with documentation.", 
                        "Everything can be set from a Rmarkdown file in your project."),
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", 
             role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# There can be development actions

These will be included in the `dev/dev_history.R` file of your package, but won't be direct part of it.

Name the following chunk with `{r development-1, eval=FALSE}`

```

# Run but keep eval=FALSE to avoid infinite loop

usethis::use_mit_license("Sébastien Rochette")

# Execute in the console directly

fusen::inflate(rmd = "dev/dev_history.Rmd")
```



# Inflate your package from dev Rmd template

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

After that, you can:

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
- Build your documentation using `pkgdown::build()` for vignette and examples checks


```{r example-3, eval = FALSE}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_dev_history(pkg = dummypackage, overwrite = TRUE)
inflate(pkg = dummypackage, rmd = dev_file, name = "Exploration of my Data", check = FALSE)

# Explore directory of the package
# browseURL(dummypackage)

# Try pkgdown build
# pkgdown::build_site(dummypackage)
# usethis::use_build_ignore("docs")
# usethis::use_git_ignore("docs")
# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# Create a new package from command line directly, using a pre-defined template

- Build a package from Rmd template in a temporary directory
  + _This is for testing purposes_

```{r, eval=FALSE}
# Create a new project
dummypackage <- tempfile(pattern = "dummy")

# {fusen} steps
create_fusen(dummypackage, open = FALSE)
# Description
fusen::fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))

# From inside the package
usethis::with_project(dummypackage, {
  # Define License with use_*_license()
  usethis::use_mit_license("Sébastien Rochette")
  
  # You may need to execute inflate() in the console directly
  fusen::inflate(pkg = dummypackage, rmd = file.path(dummypackage, "dev", "dev_history.Rmd"),
                 name = "Get started")
})
```
