---
title: "How to use fusen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use fusen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fusen)
```

# How to use {fusen}

- Create a new directory / new project
- Add the Rmarkdown template with `fusen::add_dev_history()`
- Follow the `"dev/dev_history.Rmd"` template to write your documentation and build your functions and test your examples.  
  - Chunk named `function` gets the code of a function
  - Chunk named `example` gets the code for examples of using the function. This will be used for function `@examples` and will be kept for the vignette
  - Chunk named `tests` gets the code for unit testing
  - Chunk named `development` gets the code for development purposes, usually only used once like {usethis} functions
- Inflate the template to transform it as a package with functions, unit tests and the current Rmd transformed as a vignette. And check.
- Build your {pkgdown} site to verify everything is at the right place

> Create multiple `"dev_history_xxx.Rmd"` files with `fusen::add_dev_history()` if needed


## Limitations

- One title / one chunk is for one function
- `examples` and `tests` chunks need to be placed after the associated `function` chunk
- You can add sub-functions in the `function` chunk to store them in the same R file, but they won't have `@examples`. Only the first function of the chunk will be able to get examples.
- As for any Rmd file, chunk names need to be unique. Thus, you can use `examples-1`, `examples-2`, ...
- _Do not forget to regularly clear your Workspace to avoid functions hidden by global environment_

<!--

# A chunk for package description

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
-->


# Add a new dev_history.Rmd template in "dev" directory

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# Add
add_dev_history(pkg = dummypackage)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# Fill your package Description

```{r example-2}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = paste("Use Rmd First method to build your package.", 
                        "Start your package with documentation.", 
                        "Everything can be set from a Rmd file in your project."),
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", 
             role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# There can be development actions

These will be included in the `dev/dev_history.R` file of your package, but won't be direct part of it.

Name the following chunk with `{r development-1, eval=FALSE}`

```

# Run but keep eval=FALSE to avoid infinite loop

usethis::use_mit_license("Sébastien Rochette")

# Execute in the console directly

fusen::inflate(rmd = "dev/dev_history.Rmd")
```



# Inflate your package from dev Rmd template

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

After that, you can:

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
- Build your documentation using `pkgdown::build()` for vignette and examples verifications


```{r example-3, eval = FALSE}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_dev_history(pkg = dummypackage, overwrite = TRUE)
inflate(pkg = dummypackage, rmd = dev_file, name = "Exploration of my Data", check = FALSE)

# Explore directory of the package
# browseURL(dummypackage)

# Try pkgdown build
# pkgdown::build_site(dummypackage)
# usethis::use_build_ignore("docs")
# usethis::use_git_ignore("docs")
# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

