---
title: "How to use fusen"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a-How to use fusen}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fusen)
```

# How to use {fusen}

- Create a new directory / new project with
  - RStudio template: File > New Project > New directory > Package using {fusen} 
  - Choose the template `teaching` to start  
  - *Or command line: `create_fusen("path/to/new/project", template = "teaching")`*
- Open the "dev/flat_teaching" Rmd to start setting up the package
- Run the content of the first `development` chunk with `library(testthat)` inside
- Modify and run the content of the chunk named `description` asking to describe your package and license it
  + *For the first time, you can let the code as is, this is already the content for a working package*
- Follow the `"dev/flat_teaching.Rmd"` template to write your documentation and build your functions and test your examples.  
  - Chunk named `function` gets the code of a function
  - Chunk named `example` gets the code for examples of using the function. This will be used for function `@examples` and will be kept for the vignette
  - Chunk named `tests` gets the code for unit testing
  - Chunk named `development` gets the code for development purposes, usually only used once like {usethis} functions
- Inflate the flat template to transform it as an inflated package with functions, unit tests and the current Rmd template transformed as a vignette. And check.
- Build your {pkgdown} site to verify everything is at the right place

> Create multiple `"flat_xxx.Rmd"` files with `fusen::add_flat_template(template = "add")` if needed


## Limitations

- One title / one chunk is for one function
- `examples` and `tests` chunks need to be placed after the associated `function` chunk
- You can add sub-functions in the `function` chunk to store them in the same R file, but they won't have `@examples`. Only the first function of the chunk will be able to get examples.
- As for any Rmarkdown file, chunk names need to be unique. Thus, you better use `examples-myfunction`, `examples-myotherfunction`, ...
- _Do not forget to regularly clear your Workspace to avoid functions hidden by global environment_

## Short names

- Chunk short names are possible:
  - `function` can be named `fun-` or `fun_` or `fun-my_function_name`
  - `example` can be named `ex-` or `ex_` or `ex-my_function_name`
  - `tests` can be named `test-` or `test-my_function_name`
  - `development` can be named `dev-` or `dev_` or `dev-my_function_name`

- Short "flat" templates names are possible thanks to fuzzy match like `add_flat_template("add")` for template `additionnal`

## Use `\dontrun{}`

You can use `\dontrun{}` in an example chunk as follows:

```{r example-dontrun, echo=TRUE, eval=FALSE}
#' \dontrun{
an_example <- 1 + 1
an_example
#' }

#' OR

#' \dontrun{
#' an_example <- 1 + 1
#' an_example
#' }
```


# Add a new flat_template.Rmd template in "dev" directory

```{r example}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# Add an additional dev template
add_flat_template(template = "add", pkg = dummypackage)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# Fill your package Description

```{r example-2}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = paste("Use Rmarkdown First method to build your package.", 
                        "Start your package with documentation.", 
                        "Everything can be set from a Rmarkdown file in your project."),
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", 
             role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# There can be development actions

These are only included in the flat template file, their content will not be part of the package anywhere else.

Name the following chunk with `{r development-1, eval=FALSE}`

```
# Run but keep eval=FALSE to avoid infinite loop

usethis::use_mit_license("Sébastien Rochette")

# Execute in the console directly

fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package from dev Rmd template

You're one inflate from flat paper to box.
Build your package from the flat Rmd template using the `inflate()` command below.

After that, you can:

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
- Build your documentation using `pkgdown::build()` for vignette and examples checks

_This code creates a package in a temporary directory. You will most probably be inside your project when ready to inflate, hence there will be no need to specify the directory of the package. This code is here as a reproducible example for you to test._
```{r example-3, eval = FALSE}
# Create a new project
tmpdir <- tempdir()
dummypackage <- file.path(tmpdir, "dummypackage")
dir.create(dummypackage)

# {fusen} steps
fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))
dev_file <- add_flat_template(template = "teaching",
                              pkg = dummypackage, overwrite = TRUE)
inflate(pkg = dummypackage, rmd = dev_file, name = "Exploration of my Data", check = FALSE)

# Explore directory of the package
browseURL(dummypackage)

# Delete dummy package
unlink(dummypackage, recursive = TRUE)
```

# Create a new package from command line directly, using a pre-defined template

- Build a package from Rmd template in a temporary directory
  + _This is for testing purposes_

```{r, eval=FALSE}
# Create a new project
dummypackage <- tempfile(pattern = "dummy")

# {fusen} steps
dev_file <- create_fusen(dummypackage, template = "teaching", open = FALSE)
# Description
fusen::fill_description(pkg = dummypackage, fields = list(Title = "Dummy Package"))

# From inside the package
usethis::with_project(dummypackage, {
  # Define License with use_*_license()
  usethis::use_mit_license("Sébastien Rochette")
  
  # You may need to execute inflate() in the console directly
  fusen::inflate(pkg = dummypackage, rmd = dev_file,
                 name = "Get started")
})
```
