---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
```{r description}
fill_description(
  pkg = dummypackage,
  fields = list(
    Title = "Build A Package From Rmarkdown file",
    Description = "Use Rmd First method to build your package. Start your package with documentation. Everything can be set from a Rmd file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
```

# Calculate the median of a vector

```{r function}
#' My median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
#' # Do not fill if you have an example chunk following this function
my_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  stats::median(x, na.rm = na.rm)
}
```

```{r examples}
my_median(1:12)
```

```{r tests}
test_that("my_median works properly and show error if needed", {
  expect_true(my_median(1:12) == 6.5)
  expect_error(my_median("text"))
})
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development}
# fusen::inflate() # Run but keep commented to avoid infinite loop
usethis::use_mit_license("Sébastien Rochette")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
