---
title: "flat_template.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- 
Run this 'development' chunk

Store every call to library() that you need to run chunks line by line, as in a classical Rmd for analysis
-->

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Fill and run the content of this chunk, before anything else. 

Note: when you will use other flat templates, this part will be in a separate file. Do not be surprised!
--> 

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Learn how to build A Package From Rmarkdown file",
    Description = "A Set of tools to understand packages structure. Use Rmarkdown First method to build a package from a defined template. Start your package with documentation. Everything can be set from a Rmarkdown file in your project.",
    `Authors@R` = c(
      person("Sebastien", "Rochette", email = "sebastien@thinkr.fr", role = c("aut", "cre")),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Sébastien Rochette")
```

# Calculate the median of a vector

This is the first tools of our wonderful package. 
You can calculate the median of a numeric vector using function `my_median()`.  

- Note that this will first verify that the vector is numeric, otherwise it stops with a meaningful message.

<!-- 
This first section shows:

- the three parts necessary for a package: 'function', 'examples' and 'tests'.  
  + Note that the three following chunks have names accordingly.
- the use of {roxygen2} skeleton to document a function
  + Use of `#' @importFrom` to list dependencies
  
-->

```{r function-my_median}
#' My median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#' @importFrom stats median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  median(x, na.rm = na.rm)
}
```

<!--
Here is an example on how to use the function.
This should be a reproducible and working example
-->

```{r examples-my_median}
my_median(1:12)
```

<!--
Here are some unit tests to verify the function works as expected.
-->

```{r tests-my_median}
test_that("my_median works properly and show error if needed", {
  expect_equal(my_median(1:12), 6.5)
  expect_error(my_median("text"))
})
```

# Calculate again the median of a vector
## Use sub-functions in the same chunk

Here is the second wonderful function of our package: `my_other_median()`.
This looks like the first one for sure, but when we teach, it is better to repeat things.

```{r function-my_other_median}
#' My Other median
#'
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#'
#' @return
#' Median of vector x
#' @export
#'
#' @examples
my_other_median <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {stop("x should be numeric")}
  sub_median(x, na.rm = na.rm)
}

#' Core of the median not exported
#' @param x Vector of Numeric values
#' @inheritParams stats::median
#' @importFrom stats median
#' @noRd
sub_median <- function(x, na.rm = TRUE) {
  median(x, na.rm)
}
```

```{r examples-my_other_median}
my_other_median(1:12)
```

```{r tests-my_other_median}
test_that("my_median works properly and show error if needed", {
  expect_true(my_other_median(1:12) == 6.5)
  expect_error(my_other_median("text"))
})
```

That's it ! This the end of the documented story of our package. All components are there.

<!-- 
# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()` 
-->


```{r development-inflate, eval=FALSE}
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_template.Rmd")
```

<!-- 
- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory 
-->
